% !TEX encoding = UTF-8 Unicode

\newglossaryentry{bitg}{name=built-in test,
text=built-in test,
description={The technique of designing circuits with additional logic which can be used to test proper operation of the primary (functional) logic.
}}

\newglossaryentry{biteg}{name=built-in test equipment,
text=built-in test equipment,
description={Any device permanently mounted in the prime equipment and used for the express purpose of testing the prime equipment, either independently or in association with external test equipment.
}}



\newglossaryentry{common hand tool}{name=common hand tool,
description={A tool found in common usage or applicable to a variety of operations or to a single operation on a variety of material. Screwdrivers, hammers, and wrenches are examples of common hand tools.
}}

\newglossaryentry{common part}{name=common part,
description={A part or component which is generic because (a) equivalent parts are available from more than one manufacturer and (b) it is not designed or intended for exclusive use in or by a single system or piece of equipment.
}}

\newglossaryentry{common tool}{name=common tool,
description={A tool, routinely found in the tool supply of maintenance organizations for a similar class of system or equipment, which is generic because it is available from more than one manufacturer, and is not designed or intended for exclusive use on or with a single system or piece of equipment.
}}

\newglossaryentry{critical task}{name=critical task,
description={%
A task requiring human performance which, if not accomplished in accordance with system requirements, will most likely have adverse effects on cost, system reliability, efficiency, effectiveness, or safety. Critical performance is usually part of a single line or flow in the operation or maintenance cycle of the system. A task is also considered critical whenever equipment design characteristics demand human performance which approaches the limits of human capabilities (e.g., human performance functions and tasks are too demanding, information presented to personnel is inadequate to meet human performance requirements, appropriate information displayed is not perceived, or controls provided cannot be effectively operated) and thereby significantly contributes to the occurrence of one or more of the following conditions, but not necessarily limited thereto:%
\begin{enumerate}
\item Jeopardized performance of a mission
\item Degradation of mission effectiveness or completion from inaccurate performance; e.g., human entry or response error predicted required system performance
\item Delay of a mission beyond acceptable time limits; e.g., human time to react will not meet required system reaction time
\item Exceeding predicted times for maintenance personnel to complete maintenance tasks
\item Degradation of system equipment below reliability requirements; i.e., mean time between failures (MTBF) is reduced
\item The damaging of system equipment, resulting either in a return to a maintenance facility for major repair, or in unacceptable costs, spare requirements, or system downtime
\item Injury or illness to personnel
\end{enumerate}%
}}

\newglossaryentry{depot level maintenance}{name=depot level maintenance,
description={Maintenance performed on materiel requiring major overhaul or a complete rebuilding of parts, assemblies, subassemblies, and end items, including the manufacture of parts, modification, testing, and reclamation, as required. Supports organizational and intermediate maintenance activities by more extensive shop facilities and personnel of higher technical skill than normally available at the lower maintenance levels.
}}



\newglossaryentry{feedback}{name=feedback,
description={Product response (e.g., visual, aural, or tactile) which indicates the extent to which the operator's desired effect was accomplished. Feedback can be either intrinsic or extrinsic. Intrinsic feedback (feel) is that which the individual senses directly from the operation of the control devices (e.g., clicks, detents, resistance, response ratios, stops, control displacement ). Extrinsic feedback is that which is sensed from an external source that indicates the consequences of the control action (e.g., aural tones, display changes, indicator lights).
}}

\newglossaryentry{field maintenance}{name=field maintenance,
description={That maintenance authorized and performed by designated maintenance activities in direct support of using organizations. It is normally limited to replacement of unserviceable parts, subassemblies, or assemblies.
}}


\newglossaryentry{gross kinematics}{name=gross kinematics,
description={A term to describe the general motion of a component or a component chain relative to an initial reference frame to a sufficiently coarse degree of accuracy.
}}


\newglossaryentry{iptg}{name=integrated product team,
text=integrated product team,
description={Team composed of representatives from appropriate functional disciplines working together to build successful programs, identify and resolve issues, and make sound and timely recommendations to facilitate decision-making.
}}

\newglossaryentry{intermediate level maintenance}{name=intermediate level maintenance,
description={Maintenance that is normally the responsibility of, and performed by, designated maintenance activities for direct support of using organizations. Its phases normally consist of calibrating, repairing, or replacing damaged or unserviceable parts, components, or assemblies; modification of material, emergency manufacturing of unavailable parts; and providing technical assistance to using organizations. Intermediate maintenance is normally accomplished by the using commands in fixed or mobile shops.
}}


\newglossaryentry{primary controls}{name=primary controls,
description={The most important and frequently used devices designed to control equipment and systems.
}}

\newglossaryentry{qualitative information}{name=qualitative information,
description={Information presented by a display in a manner which permits the
display user to assess the information without requiring attention to an exact numerical quantity.
}}

\newglossaryentry{quantitative information}{name=quantitative information,
description={Information presented by a display in a manner which permits the display user to observe or extract a numerical value associated with the information. Quantitative information may be displayed in either digital or analog form.
}}

\newglossaryentry{repairable item}{name=repairable item,
description={An item of a durable nature that has been determined by the application of engineering, economic, and other factors to be the type of item feasible for restoration to a serviceable condition through regular repair procedures.
}}

\newglossaryentry{rigid-body kinematics}{name=rigid-body kinematics,
description={The  dynamics of one or more idealized components relative to each other and to an initial reference frame where each component is considered non-deformable. The reconstruction of a component's location-history requires measurements sufficient to unambiguously determine to an acceptable level of precision, the component's location with respect to its initial frame.
}}

\newglossaryentry{state-of-the-art}{name=state-of-the-art,
description={The highest level of scientific and technical knowledge existing at the time of contract award.
}}

\newglossaryentry{subassembly}{name=subassembly,
description={Two or more units which form a portion of an assembly or a unit replaceable as a whole, but having a part or parts which are individually replaceable.
}}

\newglossaryentry{subsystem}{name=subsystem,
description={A combination of sets, groups, etc., which performs an operational function within a system and is a major subdivision of the system.
}}

\newglossaryentry{support equipment}{name=support equipment,
text=support equipment,
description={All equipment (mobile or fixed) required to support the Operation and Maintenance (O&M) of a materiel system. This includes associated multi-use support items, ground-handling and maintenance equipment, tools, meteorology and calibration equipment, and manual/automatic test equipment. It includes the acquisition of Logistics Support (LS) for the support equipment itself. One of the traditional LS elements.
}}







%\newglossaryentry{pear}{name=pear,
%description={an oddly shaped fruit}}
%
%\newglossaryentry{apple}{name=apple,
%description={firm, round fruit},
%see=[see also]{pear}}
%
%\newglossaryentry{banana}{name=banana,
%description={a yellow fruit with an even odder shape than
%a \gls{pear}}}
%
%\newglossaryentry{fruit}{name=fruit,
%description={sweet, fleshy product of plant containing seed}}
