% !TEX encoding = UTF-8 Unicode


%:A

\newglossaryentry{ieee.analogToDigitalConverter1}{name=analog-to-digital converter,
description={A device that converts a signal that is a function of a continuous variable into a representative number sequence.\protect \maybeCite{IEEE-100-2000}
}}

\newglossaryentry{ieee.analogToDigitalConverter2}{name=analog-to-digital converter,
description={A circuit whose input is information in analog form and whose output is the same information in digital form.\protect \maybeCite{IEEE-100-2000}
}}

\newglossaryentry{ieee.analogToDigitalConverter3}{name=analog-to-digital converter,
description={Provides the means of obtaining a digital number representation of a specific analog voltage value.\protect \maybeCite{IEEE-100-2000}
}}

\newglossaryentry{ieee.analogToDigitalConverter4}{name=analog-to-digital converter,
description={A device whose input is information in analog form and whose output is the same information in digital form.\protect \maybeCite{IEEE-100-2000}
}}

\newglossaryentry{ieee.analogToDigitalConverter5}{name=analog-to-digital converter,
description={An electronic device used to convert the amplitude of a voltage pulse from analog to digital format.\protect \maybeCite{IEEE-100-2000}
}}

\newglossaryentry{ieee.analogToDigitalConverter6}{name={analog-to-digital converter},
description={A device that provides the means to obtain a digital number representation from a specific analog value.\protect \maybeCite{IEEE-100-2000}
}}

\newglossaryentry{ieee.analogToDigitalConverter7}{name=analog-to-digital converter,
description={A circuit whose input is information in analog form and whose output is the same information in digital form.\protect \maybeCite{IEEE-100-2000}
}}

\newglossaryentry{ieee.analogToDigitalConverter8}{name={analog-to-digital converter},
description={A device or a group of devices that converts an analog quantity or analog position input signal into some type of numerical output signal or code. The input signal is either the measure and or a signal derived from it.\protect \maybeCite{IEEE-100-2000}
}}


%:B

%:C

%:D

%:E

%:F

%:G

%:H

%:I

%:J

%:K

%:L

%:M

%:N

%:O

%:P

%:Q

%:R

%:S

%:T

%:U

%:V

%:W

%:X

%:Y

%:Z
