% !TEX encoding = UTF-8 Unicode


%% A

\newglossaryentry{gov.mil.mil_std.1798B.analysis}{name=analysis,
description={Analysis is the diagnostic effort that illustrates contractual requirements have been achieved. This effort may include solution of equations, performance of simulations, evaluation and interpretation of charts and reduced data, and comparisons of analytical predictions versus test data. The normal reduction of data generated during ground and flight tests is not included. This effort is usually performed by the contractor. \maybeCite{MIL-STD-1798B}
}}


%% D

\newglossaryentry{gov.mil.mil_std.1798B.damageTolerance}{name=damage tolerance,
description={Damage tolerance is the attribute of a structure that permits it to retain its required residual strength for a period of unrepaired usage after the structure has sustained specific levels of fatigue, corrosion, accidental, and/or discrete source damage. \maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.demonstration}{name=demonstration,
description={Demonstration is an engineering effort performed to show contractual requirements have been met. Compliance or noncompliance is determined by observation only. Fit and function checks may be accomplished as demonstrations. \maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.DeRatingOfElectricalEquipment}{name=de-rating of electrical equipment,
description={De-rating is the process of operating an electrical component well inside its normal operating limits to reduce the rate at which the component deteriorates. This is done to enhance the component’s useful life. Example: If a diode is specified to be able to operate at \SI{10}{\volt} and \SI{5}{\ampere}, and it is placed into operation where it only sees \SI{10}{\volt} and \SI{3}{\ampere}, it is said to have been de-rated for that application. \maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.designLoadsEnvironmentSpectrum}{name=design loads\slash\hspace{0pt}environment spectrum,
description={The design loads/environment spectrum is the spectrum of internal and external loads and environments (chemical, thermal, etc.) used in the design of mechanical equipment and is representative of the spectrum that the equipment is expected to encounter within the design service life. \maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.designServiceLife}{name=design service life,
description={The design service life is the period of time (e.g., years, flight cycles, operating hours, landings, etc.) established at design, during which the mechanical equipment is expected to maintain its integrity when operated to the design loads/environment/usage spectrum. \maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.durability}{name=durability,
description={Durability is the ability of the system or component to resist deterioration, wear, cracking, corrosion, thermal degradation, and the effect of foreign object damage, for a specified period of time. \maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.durabilityCriticalComponent}{name=durability-critical component,
description={A durability-critical component is a component whose failure may entail costly maintenance and/or part repair and replacement which, if not performed, would significantly degrade performance and operational readiness. These components are not safety- or mission-critical, but may have a major economic impact on the system.
 \maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.durabilityNoncriticalComponent}{name=durability-noncritical component,
description={A durability-noncritical component is one whose failure would result in a minor economic impact on the system but would require maintenance and/or repair or replacement to ensure continued performance. These components do not usually require special attention during production and could be maintained on either a corrective- or preventive-maintenance basis. \maybeCite{MIL-STD-1798B}
}}

%% E

\newglossaryentry{gov.mil.mil_std.1798B.economicLife}{name=economic life,
description={Economic life is the operational service period during which it is judged to be more economically advantageous to repair than replace a component, based on an evaluation of data developed during system development. \maybeCite{MIL-STD-1798B}
}}

%% I

\newglossaryentry{gov.mil.mil_std.1798B.nondestructiveInspection}{name=nondestructive inspection (NDI),
text=nondestructive inspection,
description={Nondestructive inspection is an inspection process or technique that reveals conditions at or beneath the external surface of a part or material without adversely affecting the material or part being inspected.  \maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.improbableOccurrence}{name=improbable occurrence,
description={An improbable occurrence is defined as a risk of failure shown to be less than \num{1d-7} events per flying hour (FH). \maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.integrity}{name=integrity,
description={Integrity is comprised of the essential characteristics of systems and equipment which allows specified performance, safety, durability, reliability, and supportability to be achieved under specified operational conditions over a defined service lifetime. \maybeCite{MIL-STD-1798B}
}}

%% L

\newglossaryentry{gov.mil.mil_std.1798B.leakBeforeBurst}{name=leak before burst,
description={A through crack in a fluid container will leak fluid before burst by demonstrating tolerance of a through thickness crack two times (2$\times$) the wall thickness, or a size agreed upon with the Procuring Service, when subject to limit loading conditions. \maybeCite{MIL-STD-1798B}
}}


%% M

\newglossaryentry{gov.mil.mil_std.1798B.maintenanceFreeOperatingPeriod}{name=maintenance-free operating period,
description={This phase is that segment of the required operational service life during which no preventive maintenance is required to ensure performance and operational readiness. The results of durability testing and analysis are used to determine the maintenance-free operating period. \maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.missionCriticalComponent}{name=mission-critical component,
description={A mission-critical component is a component whose failure would: (a) prohibit the execution of a critical mission, (b) significantly reduce the operational mission capability, or (c) significantly increase the system vulnerability during a critical mission. \maybeCite{MIL-STD-1798B}
}}


%% O

\newglossaryentry{gov.mil.mil_std.1798B.otherExpendableComponents}{name=other/expendable components,
description={Other/expendable components includes all components of a system not classified as safety- critical, mission-critical, durability-critical, or durability-noncritical. The failure of these components could be handled during routine maintenance and would not impact the mission, safety, or operational readiness. \maybeCite{MIL-STD-1798B}
}}


%% P

\newglossaryentry{gov.mil.mil_std.1798B.probabilityOfDetection}{name=probability of detection (POD),
text=probability of detection,
description={A POD is a statistical measurement of the likelihood, with a specified confidence level, of finding a flaw of a defined size using a specific inspection technique. (Reference MIL-HDBK-1823.) \maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.proofTesting}{name=proof testing,
description={A test is performed on each production component that can effectively demonstrate that the part is damage tolerant. The proof test must be supported by analysis. \maybeCite{MIL-STD-1798B}
}}


%% R

\newglossaryentry{gov.mil.mil_std.1798B.requiredOperationalServiceLife}{name=required operational service life,
description={The required operational service life is that operational life specified for the specific system, subsystem, or component---usually in terms of service or operation time. \maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.redundancy}{name=redundancy,
description={Redundancy in design incorporates dual/multiple components or duplicates function to provide operational capability (without degradation) upon failure of a single component or function. Failure of a single component or function must be detectable (i.e., system is both fail operational and fail evident). Detectability may be through the Prognostic Health Management (PHM) system or at depot inspection. Redundancy also may describe a component that has redundant features. \maybeCite{MIL-STD-1798B}
}}


%% S

\newglossaryentry{gov.mil.mil_std.1798B.safeLife}{name=safe-life,
description={Safe-life of a component is that number of events such as flights, landings, or operating hours, during which there is a low probability that the (strength will degrade below its design ultimate value due to fatigue cracking.) \maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.safetyCriticalComponent}{name=safety-critical component,
description={A safety-critical component is a component whose failure would cause loss of the air vehicle, injury to personnel, or extensive damage to critical equipment/structures which could adversely affect safety of flight or personnel. \maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.similarityLegacySystems}{name=Similarity (legacy systems),
description={Similarity is when significant, successful operational experience on hardware of actual or similar design and usage has occurred. Similarity is appropriate for mature designs susceptible to damage when other design verification approaches are not feasible/appropriate. Consider the following to establish similarity:
\begin{enumerate}
	\item materials and processing;
	\item design configuration and usage;
	\item operating environment considerations including cycle temperatures and pressures,
speeds, torques, and flows;
	\item legacy component hours or cyclic history, including number of parts produced, number and type of safety-critical or mission-critical events, total number of fleet hours, and high- time component.
\end{enumerate}
\maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.slowDamageGrowthStructure}{name=slow damage growth structure,
description={Slow damage growth structure is structure in which damage is not allowed to attain the critical size required for unstable rapid damage propagation. Safety is assured through slow damage growth for specified periods of usage depending upon the degree of inspectability. The strength of slow damage growth structure with damage present is not degraded below a specified limit for the period of unrepaired service usage. \maybeCite{MIL-STD-1798B}
}}

%% T

\newglossaryentry{gov.mil.mil_std.1798B.test}{name=test,
description={Test is an empirical effort performed to prove contractual requirements have been met. Documented procedures, instrumentation, and known environmental conditions are normally applicable. Compliance or noncompliance is determined by observation, where practical, and evaluation of collected data. Most ground and flight empirical efforts associated with this procurement and acquisition qualify as tests. This effort is usually performed by the contractor. \maybeCite{MIL-STD-1798B}
}}


%% U

\newglossaryentry{gov.mil.mil_std.1798B.upRating}{name=up-rating,
description={Up-rating is the process of operating an electrical component outside/beyond the manufacturer recommended operating range. This is usually done to minimize design cost or weight or prevent obsolescence. It may have detrimental impacts on component useful life and requires careful analysis of its application. Example: If the manufacturer specs a diode to operate at \SI{10}{\volt} and \SI{5}{\ampere} and it is used in an environment of \SI{13}{\volt} and \SI{7}{\ampere}, it is said to have been up- rated for that application. \maybeCite{MIL-STD-1798B}
}}

\newglossaryentry{gov.mil.mil_std.1798B.usage}{name=usage,
description={Usage is defined as the operational parameters critical to function, performance, and service-life of the system and equipment (e.g., missions, duty cycles, loading, environments, etc.). \maybeCite{MIL-STD-1798B}
}}
