% !TEX encoding = UTF-8 Unicode

% Joint Chiefs of Staff. Dod dictionary of military and associated terms. Technical report, US Department of Defense, July 2019.



%:A

\newglossaryentry{gov.mil.acceptability}{
name={acceptability},
description={The plan review criterion for assessing whether the contemplated course of action is proportional, worth the cost, consistent with the law of war, and is militarily and politically supportable. \glsseeformat[See also]{gov.mil.adequacy,gov.mil.feasibility}{}\glsadd{gov.mil.adequacy}\glsadd{gov.mil.feasibility} (JP 5-0)}
}

\newglossaryentry{gov.mil.access}{
name={access},
description={In counterintelligence and intelligence use, a. a way or means of approach to identify a target; or b. exploitable proximity to or ability to approach an individual, facility, or information that enables target to carry out the intended mission. (JP 2-01.2)}
}

\newglossaryentry{gov.mil.accompanying_supplies}{
name={accompanying supplies},
description={Unit supplies that deploy with forces. (JP 4-01.5)}
}

\newglossaryentry{gov.mil.accountability}{
name={accountability},
description={The obligation imposed by law or lawful order or regulation on an officer or other person for keeping accurate record of property, documents, or funds. (JP 1)}
}

\newglossaryentry{gov.mil.acoustic_intelligence}{
name={acoustic intelligence},
description={Intelligence derived from the collection and processing of acoustic
phenomena. Also called ACINT. (JP 2-0)}
}
\newacronym{gov.mil.acint}{ACINT}{acoustic intelligence}

\newglossaryentry{gov.mil.acquisition_and_cross_servicing_agreement}{
name={acquisition and cross-servicing agreement},
description={Agreement, negotiated on a bilateral basis with countries or international organizations, that allow United States forces to exchange most common types of support, including food, fuel, transportation, ammunition, and equipment. Also called ACSA. \glsseeformat[See also]{gov.mil.cross_servicing}{}\glsadd{gov.mil.cross_servicing} (JP 5-0)}
}
\newacronym{gov.mil.acsa}{ACSA}{acquisition and cross-servicing agreement}

\newglossaryentry{gov.mil.action_phase}{
name={action phase},
description={In amphibious operations, the period of time between the arrival of the landing forces of the amphibious force in the operational area and the accomplishment of their mission. \glsseeformat[See also]{gov.mil.amphibious_force,gov.mil.amphibious_operation,gov.mil.landing_force,gov.mil.mission}{}\glsadd{gov.mil.amphibious_force}\glsadd{gov.mil.amphibious_operation}\glsadd{gov.mil.landing_force}\glsadd{gov.mil.mission} (JP 3-02)}
}

\newglossaryentry{gov.mil.activation}{
name={activation},
description={Order to active duty (other than for training) in the federal service. \glsseeformat[See also]{gov.mil.active_duty,gov.mil.federal_service}{}\glsadd{gov.mil.active_duty}\glsadd{gov.mil.federal_service} (JP 4-05)}
}

\newglossaryentry{gov.mil.active_defense}{
name={active defense},
description={The employment of limited offensive action and counterattacks to deny a contested area or position to the enemy. See also passive defense. \glsseeformat[See also]{gov.mil.passive_defense}{}\glsadd{gov.mil.passive_defense} (JP 3-60)}
}

\newglossaryentry{gov.mil.active_duty}{
name={active duty},
description={Full-time duty in the active military service of the United States, including active duty or full-time training duty in the Reserve Component. See also active duty for training; inactive duty training. \glsseeformat[See also]{gov.mil.active_duty_for_training,gov.mil.inactive_duty_training}{}\glsadd{gov.mil.active_duty_for_training}\glsadd{gov.mil.inactive_duty_training} (JP 4-05)}
}

\newglossaryentry{gov.mil.active_duty_for_training}{
name={active duty for training},
description={A tour of active duty that is used for training members of the Reserve Component to provide trained units and qualified persons to fill the needs of the Armed Forces of the United States in time of war or national emergency and such other times as the national security requires. (JP 4-05)}
}

\newglossaryentry{gov.mil.active_guard_and_reserve}{
name={Active Guard and Reserve},
description={National Guard and Reserve members who are on voluntary active duty providing full-time support to National Guard, Reserve, and Active Component organizations for the purpose of organizing, administering, recruiting, instructing, or training the Reserve Components. (CJCSM 3150.13)}
}

\newglossaryentry{gov.mil.activity}{
name={activity},
description={1. A unit, organization, or installation performing a function or mission. 2. A function, mission, action, or collection of actions. (JP 3-0)}
}

\newglossaryentry{gov.mil.activity_based_intelligence}{
name={activity-based intelligence},
description={An analytic method applied to structured data from multiple sources, to discover objects, relationships, or behaviors by resolving significant activity. Also called ABI. (JP 2-03)}
}
\newacronym{gov.mil.abi}{ABI}{activity-based intelligence}

\newglossaryentry{gov.mil.act_of_mercy}{
name={act of mercy},
description={In personnel recovery, assistance rendered to evaders by an individual or elements of the local population who sympathize or empathize with the evaders’ cause or plight.  \glsseeformat[See also]{gov.mil.evader,gov.mil.evasion,gov.mil.recovery,gov.mil.recovery_operations}{}\glsadd{gov.mil.evader}\glsadd{gov.mil.evasion}\glsadd{gov.mil.recovery}\glsadd{gov.mil.recovery_operations} (JP 3-50)}
}

\newglossaryentry{gov.mil.acute_radiation_dose}{
name={acute radiation dose},
description={Total ionizing radiation dose received at one time and over a period so short that biological recovery cannot occur. (JP 3-11)}
}

\newglossaryentry{gov.mil.acute_radiation_syndrome}{
name={acute radiation syndrome},
description={An acute illness caused by irradiation of the body by a high dose of penetrating radiation in a very short period of time. Also called ARS. (JP 3-11)}
}
\newacronym{gov.mil.ars}{ARS}{acute radiation syndrome}

\newglossaryentry{gov.mil.adaptive_planning_and_execution}{
name={Adaptive Planning and Execution},
description={A Department of Defense enterprise of joint policies, processes, procedures, and reporting structures, supported by communications and information technology, that is used by the joint planning and execution community to monitor, plan, and execute mobilization, deployment, employment, sustainment, redeployment, and demobilization activities associated with joint operations. Also called APEX. (JP 5-0)}
}
\newacronym{gov.mil.apex}{APEX}{Adaptive Planning and Execution}

\newglossaryentry{gov.mil.adequacy}{
name={adequacy},
description={The plan review criterion for assessing whether the scope and concept of planned operations can accomplish the assigned mission and comply with the planning guidance provided. \glsseeformat[See also]{gov.mil.acceptability,gov.mil.feasibility}{}\glsadd{gov.mil.acceptability}\glsadd{gov.mil.feasibility} (JP 5-0)}
}

\newglossaryentry{gov.mil.administrative_contracting_officer}{
name={administrative contracting officer},
description={Contracting officer whose primary duties involve contract administration. Also called ACO. \glsseeformat[See also]{gov.mil.contracting_officer,gov.mil.procuring_contracting_officer}{}.\glsadd{gov.mil.contracting_officer}\glsadd{gov.mil.procuring_contracting_officer} (JP 4-10)}
}
\newacronym{gov.mil.aconoff}{ACO}{administrative contracting officer}

\newglossaryentry{gov.mil.administrative_control}{
name={administrative control},
description={Direction or exercise of authority over subordinate or other organizations in respect to administration and support. Also called ADCON. (JP 1)}
}
\newacronym{gov.mil.adcon}{ADCON}{administrative control}

\newglossaryentry{gov.mil.administrative_loading}{
name={administrative loading},
description={A loading method that gives primary consideration to achieving maximum utilization of troop and cargo space without regard to tactical considerations. Also called commercial loading. (JP 3-02)}
}

\newglossaryentry{gov.mil.advanced_force_operations}{
name={advanced force operations},
description={Operations conducted to refine the location of specific, identified targets and further develop the operational environment for near-term missions. Also called AFO. (JP 3-05)}
}
\newacronym{gov.mil.afo}{AFO}{advanced force operations}

\newglossaryentry{gov.mil.advance_guard}{
name={advance guard},
description={Detachment sent ahead of the main force to ensure its uninterrupted advance; to protect the main body against surprise; to facilitate the advance by removing obstacles and repairing roads and bridges; and to cover the deployment of the main body if it is committed to action. (JP 3-07.2)}
}

\newglossaryentry{gov.mil.adversary}{
name={adversary},
description={A party acknowledged as potentially hostile to a friendly party and against which the use of force may be envisaged. (JP 3-0)}
}

\newglossaryentry{gov.mil.adversary_template}{
name={adversary template},
description={A model based on an adversary’s known or postulated preferred methods of operation illustrating the disposition and activity of adversary forces and assets conducting a particular operation unconstrained by the impact of the operational environment. (JP 2-01.3)}
}

\newglossaryentry{gov.mil.aerial_port}{
name={aerial port},
description={An airfield that has been designated for the sustained air movement of personnel and materiel, as well as an authorized port for entrance into or departure from the country where located. \glsseeformat[See also]{gov.mil.port_of_debarkation,gov.mil.port_of_embarkation}{}.\glsadd{gov.mil.port_of_debarkation}\glsadd{gov.mil.port_of_embarkation} (JP 3-17)}
}

\newglossaryentry{gov.mil.aeromedical_evacuation}{
name={aeromedical evacuation},
description={The movement of patients under medical supervision to and between medical treatment facilities by air transportation. Also called AE. (JP 4-02)}
}
\newacronym{gov.mil.aevac}{AE}{aeromedical evacuation}

\newglossaryentry{gov.mil.aeromedical_evacuation_control_team}{
name={aeromedical evacuation control team},
description={A core team assigned to a component-numbered Air Force air operations center air mobility division that provides operational planning, scheduling, and execution of theater aeromedical evacuation missions and positioning of aeromedical evacuation ground forces. Also called AECT. \glsseeformat[See also]{gov.mil.aeromedical_evacuation,gov.mil.air_mobility_division}{}.\glsadd{gov.mil.aeromedical_evacuation}\glsadd{gov.mil.air_mobility_division} (JP 3-17)}
}
\newacronym{gov.mil.aect}{AECT}{aeromedical evacuation control team}

\newglossaryentry{gov.mil.aerospace_defense}{
name={aerospace defense},
description={Defensive measures designed to destroy or nullify attacking enemy aircraft and missiles and also negate hostile space systems. \glsseeformat[See also]{gov.mil.air_defense}{}.\glsadd{gov.mil.air_defense} (JP 3-27)}
}
% gov.mil.space_defense missing

\newglossaryentry{gov.mil.afloat_pre_positioning_force}{
name={afloat pre-positioning force},
description={Shipping maintained in full operational status to afloat pre- position military equipment and supplies in support of combatant commanders’ operation plans, consisting of the three maritime pre-positioning ships squadrons, the Army’s afloat pre-positioning stocks-3 ships, and the Defense Logistics Agency, and the Air Force ships. Also called APF. \glsseeformat[See also]{gov.mil.maritime_pre_positioning_ships}{}.\glsadd{gov.mil.maritime_pre_positioning_ships} (JP 4-01.2)}
}
\newacronym{gov.mil.apf}{APF}{afloat pre-positioning force}

\newglossaryentry{gov.mil.afloat_pre_positioning_operations}{
name={afloat pre-positioning operations},
description={Pre-positioning of ships, preloaded with equipment and supplies that provides for an alternative to land-based programs. \glsseeformat[See also]{gov.mil.operation}{}.\glsadd{gov.mil.operation} (JP 4-01.6)}
}

\newglossaryentry{gov.mil.agency}{
name={agency},
description={In intelligence usage, an organization or individual that collects and/or processes information. Also called collection agency. \glsseeformat[See also]{gov.mil.agent,gov.mil.intelligence_process,gov.mil.source}{}.\glsadd{gov.mil.agent}\glsadd{gov.mil.intelligence_process}\glsadd{gov.mil.source} (JP 2-01)}
}

\newglossaryentry{gov.mil.agent}{
name={agent},
description={In intelligence usage, one who is authorized or instructed to obtain or to assist in obtaining information for intelligence or counterintelligence purposes. (JP 2-01.2)}
}


\newglossaryentry{gov.mil.aimpoint}{
name={aimpoint},
description={1. A point associated with a target and assigned for a specific weapon impact. 2. A prominent radar-significant feature used to assist an aircrew in navigating and delivering their weapons. \glsseeformat[See also]{gov.mil.desired_point_of_impact}{}.\glsadd{gov.mil.desired_point_of_impact} (JP 3-60)}
}

\newglossaryentry{gov.mil.air_and_missile_defense}{
name={air and missile defense},
description={Direct [active and passive] defensive actions taken to destroy, nullify, or reduce the effectiveness of hostile air and ballistic missile threats against friendly forces and assets. Also called AMD. (JP 3-01)}
}
\newacronym{gov.mil.amdef}{AMD}{air and missile defense}

\newglossaryentry{gov.mil.air_apportionment}{
name={air apportionment},
description={The determination and assignment of the total expected effort by percentage and/or by priority that should be devoted to the various air operations for a given period of time. (JP 3-0)}
}

\newglossaryentry{gov.mil.air_assault}{
name={air assault},
description={The movement of friendly assault forces by rotary-wing or tiltrotor aircraft to engage and destroy enemy forces or to seize and hold key terrain. \glsseeformat[See also]{gov.mil.assault}{}. \glsadd{gov.mil.assault}(JP 3-18)}
}

\newglossaryentry{gov.mil.air_assault_force}{
name={air assault force},
description={A force composed primarily of ground and rotary-wing air units organized, equipped, and trained for air assault operations. (JP 3-18)}
}

\newglossaryentry{gov.mil.air_assault_operation}{
name={air assault operation},
description={An operation in which assault forces, using the mobility of rotary- wing or tiltrotor aircraft and the total integration of available fires, maneuver under the control of a ground or air maneuver commander to engage enemy forces or to seize and hold key terrain. (JP 3-18)}
}

\newglossaryentry{gov.mil.airborne}{
name={airborne},
description={1. In relation to personnel, troops especially trained to effect, following transport by air, an assault debarkation, either by parachuting or touchdown. 2. In relation to equipment, pieces of equipment that have been especially designed for use by airborne troops during or after an assault debarkation, as well as some aeronautical equipment used to accomplish a particular mission. 3. When applied to materiel, items that form an integral part of the aircraft. 4. The state of an aircraft, from the instant it becomes entirely sustained by air until it ceases to be so sustained. (JP 3-17)}
}

\newglossaryentry{gov.mil.airborne_alert}{
name={airborne alert},
description={A state of aircraft readiness wherein combat-equipped aircraft are airborne and ready for immediate action to reduce reaction time and to increase survivability. \glsseeformat[See also]{gov.mil.combat_air_patrol,gov.mil.ground_alert}{}. \glsadd{gov.mil.combat_air_patrol}\glsadd{gov.mil.ground_alert}(JP 3-01)}
}

\newglossaryentry{gov.mil.airborne_assault}{
name={airborne assault},
description={The use of airborne forces to parachute into an objective area to attack and eliminate armed resistance and secure designated objectives. (JP 3-18)}
}

\newglossaryentry{gov.mil.airborne_early_warning}{
name={airborne early warning},
description={The detection of enemy air or surface units by radar or other equipment carried in an airborne vehicle, and the transmitting of a warning to friendly units. Also called AEW. (JP 3-52)}
}
\newacronym{gov.mil.aew}{AEW}{airborne early warning}

\newglossaryentry{gov.mil.airborne_mission_coordinator}{
name={airborne mission coordinator},
description={The designated individual that serves as an airborne extension of the component commander or supported commander responsible for the personnel recovery mission. Also called AMC. \glsseeformat[See also]{gov.mil.combat_search_and_rescue,gov.mil.personnel_recovery_coordination_cell}{}. \glsadd{gov.mil.combat_search_and_rescue}\glsadd{gov.mil.personnel_recovery_coordination_cell}(JP 3-50)}
}
\newacronym{gov.mil.amcoor}{AMC}{airborne mission coordinator}

\newglossaryentry{gov.mil.airborne_operation}{
name={airborne operation},
description={An operation involving the air movement into an objective area of combat forces and their logistic support for execution of a tactical, operational, or strategic mission. \glsseeformat[See also]{gov.mil.assault,gov.mil.assault_phase}{}. \glsadd{gov.mil.assault}\glsadd{gov.mil.assault_phase}(JP 3-18)}
}

\newglossaryentry{gov.mil.air_corridor}{
name={air corridor},
description={A restricted air route of travel specified for use by friendly aircraft and established for the purpose of preventing friendly aircraft from being fired on by friendly forces. (JP 3-52)}
}

\newglossaryentry{gov.mil.aircraft_carrier}{
name={aircraft carrier},
description={A warship designed to support and operate aircraft, engage in attacks on targets afloat or ashore, and engage in sustained operations in support of other forces. Also called CV or CVN. (JP 3-32)}
}
\newacronym{gov.mil.cv}{CV}{aircraft carrier}
\newacronym{gov.mil.cvn}{CVN}{aircraft carrier}

\newglossaryentry{gov.mil.air_defense}{
name={air defense},
description={Defensive measures designed to destroy attacking enemy aircraft or aerodynamic missiles, or to nullify or reduce the effectiveness of such attack. Also called AD. \glsseeformat[See also]{gov.mil.aerospace_defense}{}.\glsadd{gov.mil.aerospace_defense} (JP 3-01)}
}
\newacronym{gov.mil.adef}{AD}{air defense}

\newglossaryentry{gov.mil.air_defense_area}{
name={air defense area},
description={1. overseas --- A specifically defined airspace for which air defense must be planned and provided. 2. United States --- Airspace of defined dimensions designated by the appropriate agency within which the ready control of airborne vehicles is required in the interest of national security during an air defense emergency. (JP 3-01)}
}

\newglossaryentry{gov.mil.air_defense_artillery}{
name={air defense artillery},
description={Weapons and equipment for actively combating air targets from the ground. Also called ADA. (JP 3-01)}
}
\newacronym{gov.mil.ada}{ADA}{air defense artillery}

\newglossaryentry{gov.mil.air_defense_identification_zone}{
name={air defense identification zone},
description={Airspace of defined dimensions within which the ready identification, location, and control of airborne vehicles are required. Also called ADIZ. (JP 3-52)}
}
\newacronym{gov.mil.adiz}{ADIZ}{air defense identification zone}

\newglossaryentry{gov.mil.air_defense_region}{
name={air defense region},
description={A geographical subdivision of an air defense area. (JP 3-01)}
}

\newglossaryentry{gov.mil.air_defense_sector}{
name={air defense sector},
description={A geographical subdivision of an air defense region. (JP 3-01)}
}

\newglossaryentry{gov.mil.air_defense_warning_condition}{
name={air defense warning condition},
description={An air defense warning given in the form of a color code corresponding to the degree of air raid probability with yellow standing for when an attack by hostile aircraft or missiles is probable; red for when an attack by hostile aircraft or missiles is imminent or is in progress; and white for when an attack by hostile aircraft or missiles is improbable. Also called ADWC. (JP 3-01)}
}
\newacronym{gov.mil.adwc}{ADWC}{air defense warning condition}

\newglossaryentry{gov.mil.air_domain}{
name={air domain},
description={The atmosphere, beginning at the Earth’s surface, extending to the altitude where its effects upon operations become negligible. (JP 3-30)}
}

\newglossaryentry{gov.mil.airdrop}{
name={airdrop},
description={The unloading of personnel or materiel from aircraft in flight. \glsseeformat[See also]{gov.mil.air_movement,gov.mil.free_drop,gov.mil.free_fall,gov.mil.high_velocity_drop,gov.mil.low_velocity_drop}{}. \glsadd{gov.mil.air_movement}\glsadd{gov.mil.free_drop}\glsadd{gov.mil.free_fall}\glsadd{gov.mil.high_velocity_drop}\glsadd{gov.mil.low_velocity_drop}(JP 3-17)}
}

\newglossaryentry{gov.mil.air_expeditionary_task_force}{
name={air expeditionary task force},
description={A deployed numbered air force or command echelon immediately subordinate to a numbered air force provided as the United States Air Force component command committed to a joint operation. Also called AETF. (JP 3-30)}
}
\newacronym{gov.mil.aetf}{AETF}{air expeditionary task force}

\newglossaryentry{gov.mil.airfield}{
name={airfield},
description={An area prepared for the accommodation (including any buildings, installations, and equipment), landing, and takeoff of aircraft. \glsseeformat[See also]{gov.mil.departure_airfield,gov.mil.landing_area,gov.mil.landing_site}{}. \glsadd{gov.mil.departure_airfield}\glsadd{gov.mil.landing_area}\glsadd{gov.mil.landing_site}(JP 3-17)}
}

\newglossaryentry{gov.mil.air_force_special_operations_air_component}{
name={Air Force special operations air component},
description={The Air Force component of a joint special operations force, normally composed of a special operations wing, special operations group, or squadron, and element of an Air Force special tactics personnel. Also called AFSOAC. (JP 3-05)}
}
\newacronym{gov.mil.afsoac}{AFSOAC}{Air Force special operations air component}

\newglossaryentry{gov.mil.air_force_special_operations_air_detachment}{
name={Air Force special operations air detachment},
description={A squadron-size headquarters that could be a composite organization composed of different Air Force special operations assets, normally subordinate to an Air Force special operations air component, joint special operations air component, joint special operations task force, or a joint task force. Also called AFSOAD. (JP 3-05)}
}
\newacronym{gov.mil.afsoad}{AFSOAD}{Air Force special operations air detachment}

\newglossaryentry{gov.mil.air_force_special_operations_forces}{
name={Air Force special operations forces},
description={Those Active and Reserve Component Air Force forces designated by the Secretary of Defense that are specifically organized, trained, and equipped to conduct and support special operations. Also called AFSOF. (JP 3-05)}
}
\newacronym{gov.mil.afsof}{AFSOF}{Air Force special operations forces}

\newglossaryentry{gov.mil.airhead}{
name={airhead},
description={A lodgment that, when seized and held, ensures the continuous air landing of troops and materiel and provides the maneuver space necessary for projected operations. \glsseeformat[See also]{gov.mil.airhead}{}. \glsadd{gov.mil.airhead}(JP 3-18}
}

\newglossaryentry{gov.mil.airhead_line}{
name={airhead line},
description={A line denoting the limits of the objective area for an airborne assault. \glsseeformat[See also]{gov.mil.airhead,gov.mil.assault_phase,gov.mil.objective_area}{}. \glsadd{gov.mil.airhead}\glsadd{gov.mil.assault_phase}\glsadd{gov.mil.objective_area}(JP 3-18)}
}

\newglossaryentry{gov.mil.air_interdiction}{
name={air interdiction},
description={Air operations conducted to divert, disrupt, delay, or destroy the enemy’s military surface capabilities before it can be brought to bear effectively against friendly forces, or to otherwise achieve objectives that are conducted at such distances from friendly forces that detailed integration of each air mission with the fire and movement of friendly forces is not required. Also called AI. (JP 3-03)}
}
\newacronym{gov.mil.ainter}{AI}{air interdiction}

\newglossaryentry{gov.mil.airland}{
name={airland},
description={Move by air and disembark, or unload, after the aircraft has landed or while an aircraft is hovering. \glsseeformat[See also]{gov.mil.air_movement}{}. \glsadd{gov.mil.air_movement}(JP 3-17)}
}

\newglossaryentry{gov.mil.airland_operation}{
name={airland operation},
description={An operation involving movement by air with a designated destination for further ground deployment of units and personnel and/or further ground distribution of supplies. \glsseeformat[See also]{gov.mil.airland}{}. \glsadd{gov.mil.airland}(JP 3-17)}
}

\newglossaryentry{gov.mil.air_liaison_officer}{
name={air liaison officer},
description={The senior tactical air control party member attached to a ground unit who functions as the primary advisor to the ground commander on air power. Also called ALO. (JP 3-09.3)}
}
\newacronym{gov.mil.alo}{ALO}{air liaison officer}

\newglossaryentry{gov.mil.airlift_capability}{
name={airlift capability},
description={The total capacity expressed in terms of number of passengers and/or weight/cubic displacement of cargo that can be carried at any one time to a given destination by available airlift. \glsseeformat[See also]{gov.mil.airlift_requirement}{}. \glsadd{gov.mil.airlift_requirement}(JP 3-17)}
}

\newglossaryentry{gov.mil.airlift_control_team}{
name={airlift control team},
description={A core team within the joint air operations center with intratheater airlift functional expertise to plan, coordinate, manage, and execute intratheater airlift operations in support of the joint force air component commander. Also called ALCT. \glsseeformat[See also]{gov.mil.air_operations_center,gov.mil.air_mobility_division,gov.mil.intratheater_airlift}{}. \glsadd{gov.mil.air_operations_center}\glsadd{gov.mil.air_mobility_division}\glsadd{gov.mil.intratheater_airlift}(JP 3-17)}
}
\newacronym{gov.mil.alct}{ALCT}{airlift control team}

\newglossaryentry{gov.mil.airlift_mission_commander}{
name={airlift mission commander},
description={A commander designated when airlift aircraft are participating in airlift operations specified in the implementing directive. \glsseeformat[See also]{gov.mil.joint_force_air_component_commander}{}. \glsadd{gov.mil.joint_force_air_component_commander}(JP 3-17)}
}

\newglossaryentry{gov.mil.airlift_requirement}{
name={airlift requirement},
description={The total number of passengers and/or weight/cubic displacement of cargo required to be carried by air for a specific task. \glsseeformat[See also]{gov.mil.airlift_capability}{}. (JP 3-17)}
}

\newglossaryentry{gov.mil.air_mobility}{
name={air mobility},
description={The rapid movement of personnel, materiel, and forces to and from or within a theater by air.\glsseeformat[See also]{gov.mil.air_refueling}{}. (JP 3-17)}
}

\newglossaryentry{gov.mil.air_mobility_command}{
name={Air Mobility Command},
description={The Air Force component command of the United States Transportation Command. Also called AMC. (JP 3-17)}
}
\newacronym{gov.mil.amc}{AMC}{Air Mobility Command}

\newglossaryentry{gov.mil.air_mobility_control_team}{
name={air mobility control team},
description={A core team within the joint air operations center that directs or redirects air mobility forces in response to requirements changes, higher priorities, or immediate execution requirements. Also called AMCT. \glsseeformat[See also]{gov.mil.air_operations_center,gov.mil.air_mobility,gov.mil.air_mobility_division}{}. \glsadd{gov.mil.air_operations_center}\glsadd{gov.mil.air_mobility}\glsadd{gov.mil.air_mobility_division}(JP 3-17)}
}
\newacronym{gov.mil.amct}{AMCT}{air mobility control team}

\newglossaryentry{gov.mil.air_mobility_division}{
name={air mobility division},
description={Located in the joint air operations center to plan, coordinate, task, and execute the air mobility mission consisting of the air mobility control team, airlift control team, air refueling control team, and aeromedical evacuation control team. Also called AMD. \glsseeformat[See also]{gov.mil.air_mobility,gov.mil.joint_air_operations_center}{}.\glsadd{gov.mil.air_mobility}\glsadd{gov.mil.joint_air_operations_center} (JP 3-17)}
}
\newacronym{gov.mil.amdiv}{AMD}{air mobility division}

\newglossaryentry{gov.mil.air_mobility_liaison_officer}{
name={air mobility liaison officer},
description={A rated United States Air Force mobility air forces officer selected, trained, and equipped to assess, train, advise, and assist with mobility air forces and ground force integration for air movement and sustainment. Also called AMLO. (JP 3-17)}
}
\newacronym{gov.mil.amlo}{AMLO}{air mobility liaison officer}

\newglossaryentry{gov.mil.air_movement}{
name={air movement},
description={Air transport of units, personnel, supplies, and equipment, including airdrops and air landings. \glsseeformat[See also]{gov.mil.airdrop,gov.mil.airland}{}. \glsadd{gov.mil.airdrop}\glsadd{gov.mil.airland}(JP 3-17)}
}

\newglossaryentry{gov.mil.air_operations_center}{
name={air operations center},
description={The senior agency of the Air Force component commander that provides command and control of Air Force air and space operations and coordinates with other components and Services. Also called AOC. (JP 3-30)}
}
\newacronym{gov.mil.aoc}{AOC}{air operations center}

\newglossaryentry{gov.mil.air_refueling}{
name={air refueling},
description={The refueling of an aircraft in flight by another aircraft. Also called AR. (JP 3-17)}
}
\newacronym{gov.mil.ar}{AR}{air refueling}

\newglossaryentry{gov.mil.air_refueling_control_team}{
name={air refueling control team},
description={A core team within the joint air operations center that coordinates aerial refueling to support combat air operations or to support a strategic airbridge. Also called ARCT. \glsseeformat[See also]{gov.mil.air_operations_center,gov.mil.air_mobility_division,gov.mil.air_refueling}{}. \glsadd{gov.mil.air_operations_center}\glsadd{gov.mil.air_mobility_division}\glsadd{gov.mil.air_refueling}(JP 3-17)}
}
\newacronym{gov.mil.arct}{ARCT}{air refueling control team}

\newglossaryentry{gov.mil.air_route}{
name={air route},
description={The navigable airspace between two points, identified to the extent necessary for the application of flight rules. (JP 3-52)}
}

\newglossaryentry{gov.mil.air_sovereignty}{
name={air sovereignty},
description={A nation’s inherent right to exercise absolute control and authority over the airspace above its territory. (JP 3-27)}
}

\newglossaryentry{gov.mil.airspace_control}{
name={airspace control},
description={Capabilities and procedures used to increase operational effectiveness by promoting the safe, efficient, and flexible use of airspace. (JP 3-52)}
}

\newglossaryentry{gov.mil.airspace_control_area}{
name={airspace control area},
description={Airspace that is laterally defined by the boundaries of the operational area and may be subdivided into sectors. (JP 3-01)}
}

\newglossaryentry{gov.mil.airspace_control_authority}{
name={airspace control authority},
description={The commander designated to assume overall responsibility for the operation of the airspace control system in the airspace control area. Also called ACA. \glsseeformat[See also]{gov.mil.airspace_control,gov.mil.airspace_control_area,gov.mil.airspace_control_system,gov.mil.control,gov.mil.operation}{}. \glsadd{gov.mil.airspace_control}\glsadd{gov.mil.airspace_control_area}\glsadd{gov.mil.airspace_control_system}\glsadd{gov.mil.control}\glsadd{gov.mil.operation}(JP 3-52)}
}
\newacronym{gov.mil.acauth}{ACA}{airspace control authority}

\newglossaryentry{gov.mil.airspace_control_order}{
name={airspace control order},
description={ An order implementing the airspace control plan that provides the details of the approved requests for airspace coordinating measures. Also called ACO. (JP 3-52)}
}
\newacronym{gov.mil.acontord}{ACO}{airspace control order}

\newglossaryentry{gov.mil.airspace_control_plan}{
name={airspace control plan},
description={The document approved by the joint force commander that provides specific planning guidance and procedures for the airspace control system for the joint force operational area. Also called ACP. \glsseeformat[See also]{gov.mil.airspace_control_system,gov.mil.joint_force_commander}{}. \glsadd{gov.mil.airspace_control_system}\glsadd{gov.mil.joint_force_commander}(JP 3-52)}
}
\newacronym{gov.mil.acp}{ACP}{airspace control plan}

\newglossaryentry{gov.mil.airspace_control_procedures}{
name={airspace control procedures},
description={Rules, mechanisms, and directions that facilitate the control and use of airspace of specified dimensions. \glsseeformat[See also]{gov.mil.airspace_control_authority,gov.mil.airspace_control_order,gov.mil.airspace_control_plan}{}. \glsadd{gov.mil.airspace_control_authority}\glsadd{gov.mil.airspace_control_order}\glsadd{gov.mil.airspace_control_plan}(JP 3-52)}
}

\newglossaryentry{gov.mil.airspace_control_system}{
name={airspace control system},
description={An arrangement of those organizations, personnel, policies, procedures, and facilities required to perform airspace control functions. Also called ACS. (JP 3-52)}
}
\newacronym{gov.mil.acs}{ACS}{airspace control system}

\newglossaryentry{gov.mil.airspace_coordinating_measures}{
name={airspace coordinating measures},
description={Measures employed to facilitate the efficient use of airspace to accomplish missions and simultaneously provide safeguards for friendly forces. Also called ACMs. \glsseeformat[See also]{gov.mil.airspace_control_area,gov.mil.airspace_coordination_area,gov.mil.high_density_airspace_control_zone,gov.mil.weapon_engagement_zone}{}. \glsadd{gov.mil.airspace_control_area}\glsadd{gov.mil.airspace_coordination_area}\glsadd{gov.mil.high_density_airspace_control_zone}\glsadd{gov.mil.weapon_engagement_zone}(JP 3-52)}
}
\newacronym{gov.mil.acms}{ACMs}{airspace coordinating measures}

\newglossaryentry{gov.mil.airspace_coordination_area}{
name={airspace coordination area},
description={A three-dimensional block of airspace in a target area, established by the appropriate commander, in which friendly aircraft are reasonably safe from friendly surface fires. Also called ACA. (JP 3-09.3)}
}
\newacronym{gov.mil.aca}{ACA}{airspace coordination area}

\newglossaryentry{gov.mil.airspace_management}{
name={airspace management},
description={The coordination, integration, and regulation of the use of airspace of defined dimensions. (JP 3-52)}
}

\newglossaryentry{gov.mil.air_superiority}{
name={air superiority},
description={That degree of control of the air by one force that permits the conduct of its operations at a given time and place without prohibitive interference from air and missile threats. (JP 3-01)}
}

\newglossaryentry{gov.mil.air_support_control_section}{
name={air support control section},
description={In amphibious operations, the section of the Navy tactical air control center designated to coordinate, control, and integrate all direct-support aircraft and assault-support operations. Also called ASCS. (JP 3-02)}
}
\newacronym{gov.mil.ascs}{ASCS}{air support control section}

\newglossaryentry{gov.mil.air_support_operations_center}{
name={air support operations center},
description={The principal air control agency of the theater air control system responsible for the direction and control of air operations directly supporting the ground combat element. Also called ASOC. \glsseeformat[See also]{gov.mil.close_air_support,gov.mil.operation,gov.mil.navy_tactical_air_control_center}{}. \glsadd{gov.mil.close_air_support}\glsadd{gov.mil.operation}\glsadd{gov.mil.navy_tactical_air_control_center}(JP 3-09.3)}
}
\newacronym{gov.mil.asoc}{ASOC}{air support operations center}

\newglossaryentry{gov.mil.air_support_request}{
name={air support request},
description={A means to request preplanned and immediate close air support, air interdiction, air reconnaissance, surveillance, escort, helicopter airlift, and other aircraft missions. Also called AIRSUPREQ. (JP 3-30)}
}
\newacronym{gov.mil.airsupreq}{AIRSUPREQ}{air support request}

\newglossaryentry{gov.mil.air_supremacy}{
name={air supremacy},
description={That degree of control of the air wherein the opposing force is incapable of effective interference within the operational area using air and missile threats. (JP 3-01)}
}

\newglossaryentry{gov.mil.air_tasking_order}{
name={air tasking order},
description={A method used to task and disseminate to components, subordinate units, and command and control agencies projected sorties, capabilities, and/or forces to targets and specific missions. Also called ATO. (JP 3-30)}
}
\newacronym{gov.mil.ato}{ATO}{air tasking order}

\newglossaryentry{gov.mil.air_terminal}{
name={air terminal},
description={A facility on an airfield that functions as an air transportation hub and accommodates the loading and unloading of airlift aircraft and the in-transit processing of traffic. (JP 3-17)}
}

\newglossaryentry{gov.mil.air_traffic_control_section}{
name={air traffic control section},
description={In amphibious operations, the section of the Navy tactical air control center designed to provide initial safe passage, radar control, and surveillance for close air support aircraft in the operational area. Also called ATCS. (JP 3-02)}
}
\newacronym{gov.mil.atcs}{ATCS}{air traffic control section}

\newglossaryentry{gov.mil.alert_order}{
name={alert order},
description={1. A planning directive normally associated with a crisis, issued by the Chairman of the Joint Chiefs of Staff, on behalf of the President or Secretary of Defense, that provides essential planning guidance and directs the development, adaptation, or refinement of a plan/order after the directing authority approves a military course of action. 2. A planning directive that provides essential planning guidance, directs the initiation of planning after the directing authority approves a military course of action, but does not authorize execution. Also called ALERTORD. \glsseeformat[See also]{gov.mil.course_of_action}{}. \glsadd{gov.mil.course_of_action}(JP 5-0)}
}
\newacronym{gov.mil.alertord}{ALERTORD}{alert order}

\newglossaryentry{gov.mil.alliance}{
name={alliance},
description={The relationship that results from a formal agreement between two or more nations for broad, long-term objectives that further the common interests of the members. \glsseeformat[See also]{gov.mil.multinational}{}. \glsadd{gov.mil.multinational}(JP 3-0)}
}

\newglossaryentry{gov.mil.allied_system_for_geospatial_intelligence}{
name={Allied System for Geospatial Intelligence},
description={A partnership between five nations (United States and allied partners Australia, Canada, New Zealand, and the United Kingdom) to advance the geospatial intelligence mission with a common analytic environment to provide a common geospatial intelligence picture. Also called ASG. (JP 2-03)}
}
\newacronym{gov.mil.asg}{ASG}{Allied System for Geospatial Intelligence}

\newglossaryentry{gov.mil.allocation}{
name={allocation},
description={1. Distribution of limited forces and resources for employment among competing requirements. 2. The temporary transfer of forces to meet the operational demand of combatant commanders, including rotational requirements and requests for capabilities or forces (unit or individual) in response to crisis or emergent contingencies. \glsseeformat[See also]{gov.mil.apportionment}{}. \glsadd{gov.mil.apportionment}(JP 5-0)}
}

\newglossaryentry{gov.mil.allocation_request}{
name={allocation request},
description={A daily message that provides an estimate of the total air effort, identifies any excess and joint force general support aircraft sorties, and identifies unfilled air requirements for preplanned missions. Also called ALLOREQ. (JP 3-30)}
}
\newacronym{gov.mil.alloreq}{ALLOREQ}{allocation request}

\newglossaryentry{gov.mil.allowable_cabin_load}{
name={allowable cabin load},
description={The maximum payload that can be carried on an individual sortie. Also called ACL. (JP 3-17)}
}
\newacronym{gov.mil.acl}{ACL}{allowable cabin load}

\newglossaryentry{gov.mil.all_source_intelligence}{
name={all-source intelligence},
description={1. Intelligence products and/or organizations and activities that incorporate all sources of information in the production of finished intelligence. 2. In intelligence collection, a phrase that indicates that in the satisfaction of intelligence requirements, all collection, processing, exploitation, and reporting systems and resources are identified for possible use and those most capable are tasked. \glsseeformat[See also]{gov.mil.intelligence}{}. (JP 2-0)}
}

\newglossaryentry{gov.mil.amphibian}{
name={amphibian},
description={A small craft, propelled by propellers and wheels or by air cushions for the purpose of moving on both land and water. (JP 4-01.6)}
}

\newglossaryentry{gov.mil.amphibious_advance_force}{
name={amphibious advance force},
description={A temporary support force assigned to the amphibious force that conducts shaping operations in the amphibious objective area or operational area prior to the arrival of the amphibious force. (JP 3-02)}
}

\newglossaryentry{gov.mil.amphibious_air_traffic_control_center }{
name={amphibious air traffic control center},
description={The centralized air traffic control agency on an amphibious warfare ship responsible for operational control of aircraft departing from and recovering on the ship and tactical control of airborne helicopters in support of amphibious assaults. Also called AATCC. (JP 3-02)}
}
\newacronym{gov.mil.aatcc}{AATCC}{amphibious air traffic control center}

\newglossaryentry{gov.mil.amphibious_assault}{
name={amphibious assault},
description={A type of amphibious operation that involves establishing a force on a hostile or potentially hostile shore. \glsseeformat[See also]{gov.mil.assault,gov.mil.assault_phase}{}. \glsadd{gov.mil.assault}\glsadd{gov.mil.assault_phase}(JP 3-02)}
}

\newglossaryentry{gov.mil.amphibious_assault_vehicle_launching_area}{
name={amphibious assault vehicle launching area},
description={An area, in the vicinity of and to seaward of the line of departure, to which landing ships proceed and launch amphibious assault vehicles. (JP 3-02)}
}

\newglossaryentry{gov.mil.amphibious_breaching}{
name={amphibious breaching},
description={The conduct of a deliberate breaching operation specifically planned to overcome antilanding defenses to conduct amphibious operations. (JP 3-02)}
}

\newglossaryentry{gov.mil.amphibious_bulk_liquid_transfer_system}{
name={amphibious bulk liquid transfer system},
description={Hose-reel system providing capability to deliver fuel and/or water from ship to shore. Also called ABLTS. (JP 4-01.6)}
}
\newacronym{gov.mil.ablts}{ABLTS}{amphibious bulk liquid transfer system}

\newglossaryentry{gov.mil.amphibious_construction_battalion}{
name={amphibious construction battalion},
description={A permanently commissioned naval unit, subordinate to the commander, naval beach group, designed to provide an administrative unit from which personnel and equipment are formed in tactical elements and made available to appropriate commanders to operate causeways, transfer barges, warping tugs, and assault bulk fuel systems and to meet salvage requirements of the naval beach party. Also called PHIBCB. (JP 3-02)}
}
\newacronym{gov.mil.phibcb}{PHIBCB}{amphibious construction battalion}

\newglossaryentry{gov.mil.amphibious_defense_zone}{
name={amphibious defense zone},
description={The area encompassing the amphibious objective area and the adjoining airspace required by accompanying naval forces for the purpose of air defense. Also called an ADZ. (JP 3-02)}
}
\newacronym{gov.mil.adz}{ADZ}{amphibious defense zone}

\newglossaryentry{gov.mil.amphibious_demonstration}{
name={amphibious demonstration},
description={A type of amphibious operation conducted for the purpose of deceiving the enemy by a show of force with the expectation of deluding the enemy into following an unfavorable course of action. (JP 3-02)}
}

\newglossaryentry{gov.mil.amphibious_force}{
name={amphibious force},
description={An amphibious task force and a landing force together with other forces that are trained, organized, and equipped for amphibious operations. Also called AF.  \glsseeformat[See also]{gov.mil.amphibious_operation,gov.mil.amphibious_task_force,gov.mil.landing_force}{}\glsadd{gov.mil.amphibious_operation}\glsadd{gov.mil.amphibious_task_force}\glsadd{gov.mil.landing_force}. (JP 3-02)}
}
\newacronym{gov.mil.af}{AF}{amphibious force}

\newglossaryentry{gov.mil.amphibious_objective_area}{
name={amphibious objective area},
description={A geographical area of sufficient size for conducting necessary sea, air, and land operations and within which is located the objective(s) to be secured by the amphibious force. Also called AOA. \glsseeformat[See also]{gov.mil.amphibious_force,gov.mil.mission}{}. \glsadd{gov.mil.amphibious_force}\glsadd{gov.mil.mission}(JP 3-02)}
}
\newacronym{gov.mil.aoa}{AOA}{amphibious objective area}

\newglossaryentry{gov.mil.amphibious_operation}{
name={amphibious operation},
description={A military operation launched from the sea by an amphibious force to conduct landing force operations within the littorals. Also called PHIBOP. \glsseeformat[See also]{gov.mil.amphibious_force,gov.mil.landing_force,gov.mil.mission,gov.mil.operation}{}. \glsadd{gov.mil.amphibious_force}\glsadd{gov.mil.landing_force}\glsadd{gov.mil.mission}\glsadd{gov.mil.operation}(JP 3-02)}
}
\newacronym{gov.mil.phibop}{PHIBOP}{amphibious operation}

\newglossaryentry{gov.mil.amphibious_raid}{
name={amphibious raid},
description={A type of amphibious operation involving swift incursion into, or temporary occupation of, an objective area followed by a planned withdrawal. \glsseeformat[See also]{gov.mil.amphibious_operation}{}. \glsadd{gov.mil.amphibious_operation}(JP 3-02)}
}

\newglossaryentry{gov.mil.amphibious_ready_group}{
name={amphibious ready group},
description={A Navy task organization formed to conduct amphibious operations, commanded by an amphibious squadron commander. Also called ARG. (JP 3-02)}
}
\newacronym{gov.mil.arg}{ARG}{amphibious ready group}

\newglossaryentry{gov.mil.amphibious_squadron}{
name={amphibious squadron},
description={A tactical and administrative organization composed of amphibious warfare ships used to transport troops and their equipment for an amphibious operation. Also called PHIBRON. (JP 3-02)}
}
\newacronym{gov.mil.phibron}{PHIBRON}{amphibious squadron}

\newglossaryentry{gov.mil.amphibious_task_force}{
name={amphibious task force},
description={A Navy task organization formed to conduct amphibious operations. Also called ATF. \glsseeformat[See also]{gov.mil.amphibious_force,gov.mil.amphibious_operation,gov.mil.landing_force}{}.\glsadd{gov.mil.amphibious_force}\glsadd{gov.mil.amphibious_operation}\glsadd{gov.mil.landing_force} (JP 3-02)}
}
\newacronym{gov.mil.atf}{ATF}{amphibious task force}

\newglossaryentry{gov.mil.amphibious_vehicle}{
name={amphibious vehicle},
description={A wheeled or tracked vehicle capable of operating on both land and water. \glsseeformat[See also]{gov.mil.landing_craft}{}. \glsadd{gov.mil.landing_craft}(JP 3-02)}
}

\newglossaryentry{gov.mil.amphibious_vehicle_availability_table}{
name={amphibious vehicle availability table},
description={A tabulation of the type and number of amphibious vehicles available primarily for assault landings and for support of other elements of the operation. (JP 3-02)}
}

\newglossaryentry{gov.mil.amphibious_vehicle_employment_plan}{
name={amphibious vehicle employment plan},
description={A plan showing, in tabular form, the planned employment of amphibious vehicles during landing operations, to include initial movement to the beach. (JP 3-02)}
}

\newglossaryentry{gov.mil.amphibious_warfare_ship}{
name={amphibious warfare ship},
description={A combatant ship having organic capability to embark, land, and support landing forces in amphibious operations and which has characteristics enabling long-duration operations on the high seas. (JP 3-02)}
}

\newglossaryentry{gov.mil.amphibious_withdrawal}{
name={amphibious withdrawal},
description={A type of amphibious operation involving the extraction of forces by sea in ships or craft from a hostile or potentially hostile shore. \glsseeformat[See also]{gov.mil.amphibious_operation}{}. \glsadd{gov.mil.amphibious_operation}(JP 3-02)}
}

\newglossaryentry{gov.mil.analysis_and_production}{
name={analysis and production},
description={ In intelligence usage, the conversion of processed information into intelligence through the integration, evaluation, analysis, and interpretation of all source data and the preparation of intelligence products in support of known or anticipated user requirements. \glsseeformat[See also]{gov.mil.intelligence_process}{}. (JP 2-01)}
}

\newglossaryentry{gov.mil.antiaccess}{
name={antiaccess},
description={Action, activity, or capability, usually long-range, designed to prevent an advancing enemy force from entering an operational area. Also called A2. (JP 3-0)}
}
\newacronym{gov.mil.atwo}{A2}{antiaccess}

\newglossaryentry{gov.mil.antideficiency_act_violations}{
name={Antideficiency Act violations},
description={The incurring of obligations or the making of expenditure (outlays) in violation of appropriation law as to purpose, time, and amounts as specified in the defense appropriation or appropriations of funds. (JP 3-80)}
}

\newglossaryentry{gov.mil.antiradiation missile}{
name={antiradiation missile},
description={A missile which homes passively on a radiation source. Also called ARM. \glsseeformat[See also]{gov.mil.guided_missile}{}. \glsadd{gov.mil.guided_missile}(JP 3-01)}
}
\newacronym{gov.mil.arm}{ARM}{antiradiation missile}

\newglossaryentry{gov.mil.antisubmarine_warfare}{
name={antisubmarine warfare},
description={Operations conducted with the intention of denying the enemy the effective use of submarines. Also called ASW. (JP 3-32)}
}
\newacronym{gov.mil.asw}{ASW}{antisubmarine warfare}

\newglossaryentry{gov.mil.antiterrorism}{
name={antiterrorism},
description={Defensive measures used to reduce the vulnerability of individuals and property to terrorist acts, to include rapid containment by local military and civilian forces. Also called AT. \glsseeformat[See also]{gov.mil.counterterrorism,gov.mil.terrorism}{}. \glsadd{gov.mil.counterterrorism}\glsadd{gov.mil.terrorism}(JP 3-07.2)}
}
\newacronym{gov.mil.at}{AT}{antiterrorism}

\newglossaryentry{gov.mil.anti_vehicle_land_mine}{
name={anti-vehicle land mine},
description={A mine designed to immobilize or destroy a vehicle. Also called AVL. (JP 3-15)}
}
\newacronym{gov.mil.avl}{AVL}{anti-vehicle land mine}

\newglossaryentry{gov.mil.application}{
name={application},
description={1. The system or problem to which a computer is applied. 2. In the intelligence context, the direct extraction and tailoring of information from an existing foundation of intelligence and near real time reporting. (JP 2-0)}
}

\newglossaryentry{gov.mil.apportionment}{
name={apportionment},
description={The quantities of force capabilities and resources provided for planning purposes only, but not necessarily an identification of the actual forces that may be allocated for use when a plan transitions to execution. \glsseeformat[See also]{gov.mil.allocation}{}. \glsadd{gov.mil.allocation}(JP 5-0)}
}

\newglossaryentry{gov.mil.approach_schedule}{
name={approach schedule},
description={In amphibious operations, a schedule that indicates, for each scheduled wave, the time of departure from the rendezvous area, from the line of departure and from other control points, and the time of arrival at the beach. (JP 3-02)}
}

\newglossaryentry{gov.mil.apron}{
name={apron},
description={A defined area on an airfield intended to accommodate aircraft for purposes of loading or unloading passengers or cargo, refueling, parking, or maintenance. (JP 3-34)}
}

\newglossaryentry{gov.mil.area_air_defense_commander}{
name={area air defense commander},
description={The component commander with the preponderance of air defense capability and the required command, control, and communications capabilities who is assigned by the joint force commander to plan and execute integrated air defense operations. Also called AADC. (JP 3-01)}
}
\newacronym{gov.mil.aadc}{AADC}{area air defense commander}

\newglossaryentry{gov.mil.area_damage_control}{
name={area damage control},
description={Measures taken before, during, and/or after a hostile action or natural or manmade disasters to reduce the probability of damage and minimize its effects. Also called ADC. (JP 3-10)}
}
\newacronym{gov.mil.adc}{ADC}{area damage control}

\newglossaryentry{gov.mil.area_denial}{
name={area denial},
description={Action, activity, or capability, usually short-range, designed to limit an enemy force’s freedom of action within an operational area. Also called AD. (JP 3-0)}
}
\newacronym{gov.mil.ad}{AD}{area denial}

\newglossaryentry{gov.mil.area_of_influence}{
name={area of influence},
description={A geographical area wherein a commander is directly capable of influencing operations by maneuver or fire support systems normally under the commander’s command or control. (JP 3-0)}
}

\newglossaryentry{gov.mil.area_of_interest}{
name={area of interest},
description={That area of concern to the commander, including the area of influence, areas adjacent thereto, and extending into enemy territory. Also called AOI. \glsseeformat[See also]{gov.mil.area_of_influence}{}. \glsadd{gov.mil.area_of_influence}(JP 3-0)}
}
\newacronym{gov.mil.aoi}{AOI}{area of interest}

\newglossaryentry{gov.mil.area_of_operations}{
name={area of operations},
description={An operational area defined by a commander for land and maritime forces that should be large enough to accomplish their missions and protect their forces. Also called AO. \glsseeformat[See also]{gov.mil.area_of_responsibility,gov.mil.joint_operations_area,gov.mil.joint_special_operations_area}{}. \glsadd{gov.mil.area_of_responsibility}\glsadd{gov.mil.joint_operations_area}\glsadd{gov.mil.joint_special_operations_area}(JP 3-0)}
}
\newacronym{gov.mil.ao}{AO}{area of operations}

\newglossaryentry{gov.mil.area_of_responsibility}{
name={area of responsibility},
description={The geographical area associated with a combatant command within which a geographic combatant commander has authority to plan and conduct operations. Also called AOR. \glsseeformat[See also]{gov.mil.combatant_command}{}. \glsadd{gov.mil.combatant_command}(JP 1)}
}
\newacronym{gov.mil.aor}{AOR}{area of responsibility}

\newglossaryentry{gov.mil.area_search}{
name={area search},
description={Visual reconnaissance of limited or defined areas. (JP 3-50)}
}

\newglossaryentry{gov.mil.armed_forces_of_the_united_states}{
name={Armed Forces of the United States},
description={A term used to denote collectively all components of the Army, Marine Corps, Navy, Air Force, and Coast Guard (when mobilized under Title 10, United States Code, to augment the Navy). \glsseeformat[See also]{gov.mil.united_states_armed_forces}{}. (JP 1)}
}

\newglossaryentry{gov.mil.arming}{
name={arming},
description={As applied to explosives, weapons, and ammunition, the changing from a safe condition to a state of readiness for initiation. (JP 3-15)}
}

\newglossaryentry{gov.mil.army_air_ground_system}{
name={Army air-ground system},
description={The Army system which provides for interface between Army and tactical air support agencies of other Services in the planning, evaluating, processing, and coordinating of air support requirements and operations. Also called AAGS. (JP 3-09.3)}
}
\newacronym{gov.mil.aags}{AAGS}{Army air-ground system}

\newglossaryentry{gov.mil.army_corps}{
name={Army corps},
description={An intermediate headquarters between divisions and the theater army consisting of two or more divisions together with supporting brigades. (JP 3-31)}
}

\newglossaryentry{gov.mil.army_service_component_command}{
name={Army Service component command},
description={Command responsible for recommendations to the joint force commander on the allocation and employment of Army forces within a combatant command. Also called ASCC. (JP 3-31)}
}
\newacronym{gov.mil.ascc}{ASCC}{Army Service component command}

\newglossaryentry{gov.mil.army_special_operations_forces}{
name={Army special operations forces},
description={Those Active and Reserve Component Army forces designated by the Secretary of Defense that are specifically organized, trained, and equipped to conduct and support special operations. Also called ARSOF. (JP 3-05)}
}
\newacronym{gov.mil.arsof}{ARSOF}{Army special operations forces}

\newglossaryentry{gov.mil.army_support_area}{
name={Army support area},
description={The specific support area for a theater Army that is outside of a division or corps’s operational area established primarily for the positioning, employment, and protection of theater support units; and where the majority of the sustaining operations occur. (JP 3-31)}
}

\newglossaryentry{gov.mil.arrival_zone}{
name={arrival zone},
description={In counterdrug operations, the area in or adjacent to the United States where smuggling concludes and domestic distribution begins (by air, an airstrip; by sea, an offload point on land or transfer to small boats). \glsseeformat[See also]{gov.mil.transit_zone}{}. \glsadd{gov.mil.transit_zone}(JP 3-07.4)}
}

\newglossaryentry{gov.mil.ascent_phase}{
name={ascent phase},
description={That portion of the flight of a ballistic missile or space vehicle that begins after powered flight and ends just prior to apogee. (JP 3-01)}
}

\newglossaryentry{gov.mil.assault}{
name={assault},
description={1. In an amphibious operation, the period of time between the arrival of the major assault forces of the amphibious task force in the objective area and the accomplishment of the amphibious task force mission. (JP 3-02) 2. To make a short, violent, but well-ordered attack against a local objective, such as a gun emplacement, a fort, or a machine gun nest. (JP 3-18) 3. A phase of an airborne operation beginning with delivery by air of the assault echelon of the force into the objective area and extending through attack of assault objectives and consolidation of the initial airhead. \glsseeformat[See also]{gov.mil.assault_phase}{}. \glsadd{gov.mil.assault_phase}(JP 3-18)}
}

\newglossaryentry{gov.mil.assault_breaching}{
name={assault breaching},
description={A part of amphibious breaching in support of an amphibious assault involving a fire support mission using precision-guided munitions to neutralize mines and obstacles in the surf zone and on the beach. (JP 3-02)}
}

\newglossaryentry{gov.mil.assault_craft_unit}{
name={assault craft unit},
description={A permanently commissioned naval organization, subordinate to the commander, naval beach group, that contains landing craft and crews necessary to provide lighterage required in an amphibious operation. Also called ACU. (JP 3-02)}
}
\newacronym{gov.mil.acu}{ACU}{assault craft unit}

\newglossaryentry{gov.mil.assault_echelon}{
name={assault echelon},
description={In amphibious operations, the element of a force comprised of tailored units and aircraft assigned to conduct the initial assault on the operational area. Also called AE. \glsseeformat[See also]{gov.mil.amphibious_operation}{}. \glsadd{gov.mil.amphibious_operation}(JP 3-02)}
}
\newacronym{gov.mil.aech}{AE}{assault echelon}

\newglossaryentry{gov.mil.assault_follow_on_echelon }{
name={assault follow-on echelon},
description={ In amphibious operations, that echelon of the assault troops, vehicles, aircraft, equipment, and supplies that, though not needed to initiate the assault, is required to support and sustain the assault. Also called AFOE. (JP 3-02)}
}
\newacronym{gov.mil.afoe}{AFOE}{assault follow-on echelon}

\newglossaryentry{gov.mil.assault_phase}{
name={assault phase},
description={In an airborne operation, a phase beginning with delivery by air of the assault echelon of the force into the objective area and extending through attack of assault objectives and consolidation of the initial airhead. \glsseeformat[See also]{gov.mil.assault}{}. \glsadd{gov.mil.assault}(JP 3-18)}
}

\newglossaryentry{gov.mil.assault_schedule}{
name={assault schedule},
description={In amphibious operations, a schedule that provides the formation, composition, and timing of waves landing over the beach. (JP 3-02)}
}

\newglossaryentry{gov.mil.assessment}{
name={assessment},
description={1. A continuous process that measures the overall effectiveness of employing capabilities during military operations. 2. Determination of the progress toward accomplishing a task, creating a condition, or achieving an objective. 3. Analysis of the security, effectiveness, and potential of an existing or planned intelligence activity. 4. Judgment of the motives, qualifications, and characteristics of present or prospective employees or “agents.” (JP 3-0)}
}

\newglossaryentry{gov.mil.assessment_agent}{
name={assessment agent},
description={The organization responsible for conducting an assessment of an approved joint publication. Also called AA. (CJCSM 5120.01)}
}
\newacronym{gov.mil.aagent}{AA}{assessment agent}

\newglossaryentry{gov.mil.asset_validation}{
name={asset validation},
description={In intelligence use, the process used to determine the asset authenticity, reliability, utility, suitability, and degree of control the case officer or others have. (JP 2-01.2)}
}

\newglossaryentry{gov.mil.asset_visibility}{
name={asset visibility},
description={Provides users with information on the location, movement, status and identity of units, personnel, equipment, and supplies. Also called AV. (JP 3-35)}
}
\newacronym{gov.mil.av}{AV}{asset visibility}

\newglossaryentry{gov.mil.assign}{
name={assign},
description={1. To place units or personnel in an organization where such placement is relatively permanent, and/or where such organization controls and administers the units or personnel for the primary function, or greater portion of the functions, of the unit or personnel. 2. To detail individuals to specific duties or functions where such duties or functions are primary and/or relatively permanent. \glsseeformat[See also]{gov.mil.attach}{}.\glsadd{gov.mil.attach} (JP 3-0)}
}

\newglossaryentry{gov.mil.assumption}{
name={assumption},
description={A specific supposition of the operational environment that is assumed to be true, in the absence of positive proof, essential for the continuation of planning. (JP 5-0)}
}

\newglossaryentry{gov.mil.atmospheric_environment}{
name={atmospheric environment},
description={The envelope of air surrounding the Earth, including its interfaces and interactions with the Earth’s solid or liquid surface. (JP 3-59)}
}

\newglossaryentry{gov.mil.attach}{
name={attach},
description={1. The placement of units or personnel in an organization where such placement is relatively temporary. 2. The detailing of individuals to specific functions where such functions are secondary or relatively temporary. \glsseeformat[See also]{gov.mil.assign}{}. (JP 3-0)}
}

\newglossaryentry{gov.mil.attack_group}{
name={attack group},
description={A subordinate task organization of the Navy forces of an amphibious task force composed of amphibious warfare ships and supporting naval units designated to transport, protect, land, and initially support a landing group. (JP 3-02)}
}

\newglossaryentry{gov.mil.attack_heading}{
name={attack heading},
description={1. The interceptor heading during the attack phase that will achieve the desired track-crossing angle. 2. The assigned magnetic compass heading to be flown by aircraft during the delivery phase of an air strike. (JP 3-09.3)}
}

\newglossaryentry{gov.mil.attack_position}{
name={attack position},
description={The last position occupied by the assault echelon before crossing the line of departure. (JP 3-09.3)}
}

\newglossaryentry{gov.mil.audience}{
name={audience},
description={In public affairs, a broadly-defined group that contains stakeholders and/or publics relevant to military operations. (JP 3-61)}
}

\newglossaryentry{gov.mil.authentication}{
name={authentication},
description={1. A security measure designed to protect a communications system against acceptance of a fraudulent transmission or simulation by establishing the validity of a transmission, message, or originator. 2. A means of identifying individuals and verifying their eligibility to receive specific categories of information. 3. Evidence by proper signature or seal that a document is genuine and official. 4. In personnel recovery missions, the process whereby the identity of an isolated person is confirmed. \glsseeformat[See also]{gov.mil.evader,gov.mil.evasion,gov.mil.recovery_operations,gov.mil.security}{}. \glsadd{gov.mil.evader}\glsadd{gov.mil.evasion}\glsadd{gov.mil.recovery_operations}\glsadd{gov.mil.security}(JP 3-50)}
}

\newglossaryentry{gov.mil.authorized_departure}{
name={authorized departure},
description={A procedure, short of ordered departure, by which mission employees or dependents or both, are permitted to leave post in advance of normal rotation when the national interests or imminent threat to life require it. (JP 3-68)}
}

\newglossaryentry{gov.mil.automated_repatriation_reporting_system}{
name={Automated Repatriation Reporting System},
description={A Defense Manpower Data Center system used to track the status of noncombatant evacuees after they have arrived in an initial safe haven in the United States. (JP 3-68)}
}

\newglossaryentry{gov.mil.automatic_identification_technology}{
name={automatic identification technology},
description={A suite of technologies enabling the automatic capture of data, thereby enhancing the ability to identify, track, document, and control assets (e.g., materiel), deploying and redeploying forces, equipment, personnel, and sustainment cargo. Also called AIT. (JP 4-09)}
}
\newacronym{gov.mil.ait}{AIT}{automatic identification technology}

\newglossaryentry{gov.mil.autonomous_operation}{
name={autonomous operation},
description={ In air defense, the mode of operation assumed by a unit after it has lost all communications with higher echelons forcing the unit commander to assume full responsibility for control of weapons and engagement of hostile targets. (JP 3-01)}
}

\newglossaryentry{gov.mil.avenue_of_approach}{
name={avenue of approach},
description={An air or ground route of an attacking force of a given size leading to its objective or to key terrain in its path. Also called AA. (JP 2-01.3)}
}
\newacronym{gov.mil.aapproach}{AA}{avenue of approach}

\newglossaryentry{gov.mil.aviation medicine}{
name={aviation medicine},
description={The special field of medicine that is related to the biological and psychological problems of flight. (JP 4-02)}
}







%:B


\newglossaryentry{gov.mil.backfill}{
name={backfill},
description={Reserve Component units and individuals recalled to replace deploying active units and/or individuals in the continental United States and outside the continental United States. \glsseeformat[See also]{gov.mil.reserve_component}{}. \glsadd{gov.mil.reserve_component}(JP 4-05)}
}

\newglossaryentry{gov.mil.bale_cubic_capacity}{
name={bale cubic capacity},
description={The space available for cargo measured in cubic feet to the inside of the cargo battens, on the frames, and to the underside of the beams. (JP 4-01.2)}
}

\newglossaryentry{gov.mil.ballistic_missile}{
name={ballistic missile},
description={Any missile that does not rely upon aerodynamic surfaces to produce lift and consequently follows a ballistic trajectory when thrust is terminated. Also called BM. \glsseeformat[See also]{gov.mil.guided_missile}{}. \glsadd{gov.mil.guided_missile}(JP 3-01)}
}
\newacronym{gov.mil.bm}{BM}{ballistic missile}


\newglossaryentry{gov.mil.barrier}{
name={barrier},
description={A coordinated series of natural or man-made obstacles designed or employed to channel, direct, restrict, delay, or stop the movement of an opposing force and to impose additional losses in personnel, time, and equipment on the opposing force. (JP 3-15)}
}

\newglossaryentry{gov.mil.barrier_combat_air_patrol}{
name={barrier combat air patrol},
description={One or more divisions or elements of fighter aircraft employed between a force and an objective area as a barrier across the probable direction of enemy attack. \glsseeformat[See also]{gov.mil.combat_air_patrol}{}. \glsadd{gov.mil.combat_air_patrol}(JP 3-01)}
}

\newglossaryentry{gov.mil.barrier_obstacle_and_mine_warfare_plan}{
name={barrier, obstacle, and mine warfare plan},
description={A comprehensive, coordinated plan that includes responsibilities; general location of unspecified and specific barriers, obstacles, and minefields; special instructions; limitations; coordination; and completion times; and may designate locations of obstacle zones or belts. (JP 3-15)}
}

\newglossaryentry{gov.mil.base}{
name={base},
description={1. A locality from which operations are projected or supported. 2. An area or locality containing installations which provide logistics or other support. 3. Home airfield or home carrier. \glsseeformat[See also]{gov.mil.facility}{}. \glsadd{gov.mil.facility}(JP 4-0)}
}

\newglossaryentry{gov.mil.base_boundary}{
name={base boundary},
description={A line that delineates the surface area of a base for the purpose of facilitating coordination and deconfliction of operations between adjacent units, formations, or areas. (JP 3-10)}
}

\newglossaryentry{gov.mil.base_cluster}{
name={base cluster},
description={A collection of bases, geographically grouped for mutual protection and ease of command and control. (JP 3-10)}
}

\newglossaryentry{gov.mil.base_cluster_operations_center}{
name={base cluster operations center},
description={A command and control facility that serves as the base cluster commander’s focal point for defense and security of the base cluster. Also called BCOC. (JP 3-10)}
}
\newacronym{gov.mil.bcoc}{BCOC}{base cluster operations center}

\newglossaryentry{gov.mil.base_defense}{
name={base defense},
description={The local military measures, both normal and emergency, required to nullify or reduce the effectiveness of enemy attacks on, or sabotage of, a base to ensure the maximum capacity of its facilities is available to United States forces. (JP3-10)}
}

\newglossaryentry{gov.mil.base_defense_operations_center}{
name={base defense operations center},
description={A command and control facility established by the base commander to serve as the focal point for base security and defense. Also called BDOC. (JP 3-10)}
}
\newacronym{gov.mil.bdoc}{BDOC}{base defense operations center}

\newglossaryentry{gov.mil.base_defense_zone}{
name={base defense zone},
description={An air defense zone established around an air base and limited to the engagement envelope of short-range air defense weapons systems defending that base. Also called BDZ. (JP 3-52)}
}
\newacronym{gov.mil.bdz}{BDZ}{base defense zone}

\newglossaryentry{gov.mil.base_development}{
name={base development},
description={The acquisition, development, expansion, improvement, construction and/or replacement of the facilities and resources of a location to support forces. (JP 3-34)}
}

\newglossaryentry{gov.mil.baseline_costs}{
name={baseline costs},
description={The continuing annual costs of military operations funded by the operations and maintenance and military personnel appropriations. (JP 3-80)}
}

\newglossaryentry{gov.mil.base_operating_support}{
name={base operating support},
description={Directly assisting, maintaining, supplying, and distributing support of forces at the operating location. Also called BOS. (JP 4-0)}
}
\newacronym{gov.mil.bos}{BOS}{base operating support}

\newglossaryentry{gov.mil.base_operating_support_integrator}{
name={base operating support-integrator},
description={The designated Service component or joint task force commander assigned to synchronize all sustainment functions for a contingency base. Also called BOS-I. (JP 4-0)}
}
\newacronym{gov.mil.bos_i}{BOS-I}{base operating support-integrator}

\newglossaryentry{gov.mil.base_plan}{
name={base plan},
description={A type of operation plan that describes the concept of operations, major forces, sustainment concept, and anticipated timelines for completing the mission without annexes or time-phased force and deployment data. Also called BPLAN. (JP 5-0)}
}
\newacronym{gov.mil.bplan}{BPLAN}{base plan}

\newglossaryentry{gov.mil.base_support_installation}{
name={base support installation},
description={A Department of Defense Service or agency installation within the United States and its territories tasked to serve as a base for military forces engaged in either homeland defense or conducting defense support of civil authorities. Also called BSI. (JP 3-28)}
}
\newacronym{gov.mil.bsi}{BSI}{base support installation}

\newglossaryentry{gov.mil.basic_encyclopedia}{
name={basic encyclopedia},
description={A compilation of identified installations and physical areas of potential significance as objectives for attack. Also called BE. (JP 2-01)}
}
\newacronym{gov.mil.be}{BE}{basic encyclopedia}

\newglossaryentry{gov.mil.basic_load}{
name={basic load},
description={The quantity of supplies required to be on hand within, and moved by a unit or formation, expressed according to the wartime organization of the unit or formation and maintained at the prescribed levels. (JP 4-09)}
}

\newglossaryentry{gov.mil.battalion_landing_team}{
name={battalion landing team},
description={1. In an amphibious operation, an infantry battalion normally reinforced by necessary combat and service elements. 2. The basic unit for planning an assault landing. Also called BLT. (JP 3-02)}
}
\newacronym{gov.mil.blt}{BLT}{battalion landing team}

\newglossaryentry{gov.mil.battle_damage_assessment}{
name={battle damage assessment},
description={The estimate of damage composed of physical and functional damage assessment, as well as target system assessment, resulting from the application of lethal or nonlethal military force. Also called BDA. \glsseeformat[See also]{gov.mil.combat_assessment}{}. \glsadd{gov.mil.combat_assessment}(JP 3-0)}
}
\newacronym{gov.mil.bda}{BDA}{battle damage assessment}

\newglossaryentry{gov.mil.battle_damage_repair}{
name={battle damage repair},
description={Essential repair, which may be improvised, carried out rapidly in a hostile environment in order to return damaged or disabled equipment to temporary service. Also called BDR. (JP 4-09)}
}
\newacronym{gov.mil.bdr}{BDR}{battle damage repair}

\newglossaryentry{gov.mil.battlefield_coordination_detachment}{
name={battlefield coordination detachment},
description={An Army liaison located in the air operations center that provides selected operational functions between the Army forces and the air component commander. Also called BCD. \glsseeformat[See also]{gov.mil.air_operations_center}{}. \glsadd{gov.mil.air_operations_center}(JP 3-03)}
}
\newacronym{gov.mil.bcd}{BCD}{battlefield coordination detachment}

\newglossaryentry{gov.mil.battle_injury}{
name={battle injury},
description={Damage or harm sustained by personnel during or as a result of battle conditions. Also called BI. (JP 4-02)}
}
\newacronym{gov.mil.bi}{BI}{battle injury}

\newglossaryentry{gov.mil.battle_management}{
name={battle management},
description={The management of activities within the operational environment based on the commands, direction, and guidance given by appropriate authority. (JP 3-01)}
}

\newglossaryentry{gov.mil.battle_rhythm}{
name={battle rhythm},
description={A deliberate, daily schedule of command, staff, and unit activities intended to maximize use of time and synchronize staff actions. (JP 3-33)}
}

\newglossaryentry{gov.mil.beach}{
name={beach},
description={1. The area extending from the shoreline inland to a marked change in physiographic form or material or to the line of permanent vegetation (coastline). 2. In amphibious operations, that portion of the shoreline designated for landing of a tactical organization. (JP 3-02)}
}

\newglossaryentry{gov.mil.beach_group}{
name={beach group},
description={\glsseeformat[See]{gov.mil.shore_party}{}\glsadd{gov.mil.shore_party} (JP 3-02)}
}

\newglossaryentry{gov.mil.beachhead}{
name={beachhead},
description={A designated area on a hostile or potentially hostile shore that, when seized and held, ensures the continuous landing of troops and materiel and provides maneuver space requisite for subsequent projected operations ashore. (JP 3-02)}
}

\newglossaryentry{gov.mil.beachmaster_unit}{
name={beachmaster unit},
description={A commissioned naval unit of the naval beach group designed to provide to the shore party a Navy component known as a beach party, which is capable of supporting the amphibious landing of one division (reinforced). Also called BMU. \glsseeformat[See also]{gov.mil.beach_party,gov.mil.naval_beach_group,gov.mil.shore_party}{}. \glsadd{gov.mil.beach_party}\glsadd{gov.mil.naval_beach_group}\glsadd{gov.mil.shore_party}(JP 4-01.6)}
}
\newacronym{gov.mil.bmu}{BMU}{beachmaster unit}

\newglossaryentry{gov.mil.beach_party}{
name={beach party},
description={The Navy component of the landing force support party under the tactical control of the landing force support party commander. \glsseeformat[See also]{gov.mil.beachmaster_unit,gov.mil.shore_party}{}. \glsadd{gov.mil.beachmaster_unit}\glsadd{gov.mil.shore_party}(JP 3-02)}
}

\newglossaryentry{gov.mil.beach_support_area}{
name={beach support area},
description={In amphibious operations, the area to the rear of a landing force, or elements thereof, that contains the facilities for the unloading of troops and materiel and the support of the forces ashore. Also called BSA. (JP 3-02)}
}
\newacronym{gov.mil.bsa}{BSA}{beach support area}

\newglossaryentry{gov.mil.begin_morning_civil_twilight}{
name={begin morning civil twilight},
description={The period of time at which the sun is halfway between beginning morning and nautical twilight and sunrise, when there is enough light to see objects clearly with the unaided eye. Also called BMCT. (JP 2-01.3)}
}
\newacronym{gov.mil.bmct}{BMCT}{begin morning civil twilight}

\newglossaryentry{gov.mil.begin_morning_nautical_twilight}{
name={begin morning nautical twilight},
description={The start of that period where, in good conditions and in the absence of other illumination, the sun is 12 degrees below the eastern horizon and enough light is available to identify the general outlines of ground objects and conduct limited military operations. Also called BMNT. (JP 3-09.3)}
}
\newacronym{gov.mil.bmnt}{BMNT}{begin morning nautical twilight}

\newglossaryentry{gov.mil.biological_agent}{
name={biological agent},
description={A microorganism (or a toxin derived from it) that causes disease in personnel, plants, or animals or causes the deterioration of materiel. See also chemical agent. (JP 3-11)}
}

\newglossaryentry{gov.mil.biological_hazard}{
name={biological hazard},
description={An organism, or substance derived from an organism, that poses a threat to human or animal health. (JP 3-11)}
}

\newglossaryentry{gov.mil.biometrics}{
name={biometrics},
description={The process of recognizing an individual based on measurable anatomical, physiological, and behavioral characteristics. (JP 2-0)}
}

\newglossaryentry{gov.mil.biometrics_enabled_intelligence}{
name={biometrics-enabled intelligence},
description={The intelligence derived from the processing of biologic identity data and other all-source for information concerning persons of interest. Also called BEI. (JP 2-0)}
}
\newacronym{gov.mil.bei}{BEI}{biometrics-enabled intelligence}


\newglossaryentry{gov.mil.biosurveillance}{
name={biosurveillance},
description={The process to gather, integrate, interpret, and communicate essential information related to all-hazards, threats, or disease activity affecting human, animal, or plant health to achieve early detection and warning, contribute to overall situational awareness of the health aspects of an incident, and to enable better decision making at all levels. (JP 4-02)}
}

\newglossaryentry{gov.mil.blister_agent}{
name={blister agent},
description={A chemical agent that injures the eyes and lungs, and burns or blisters the skin. Also called vesicant agent. (JP 3-11)}
}

\newglossaryentry{gov.mil.blood agent}{
name={blood agent},
description={A chemical compound, including the cyanide group, that affects bodily functions by preventing the normal utilization of oxygen by body tissues. (JP 3-11)}
}

\newglossaryentry{gov.mil.blood_chit}{
name={blood chit},
description={A small sheet of material depicting an American flag and a statement in several languages to the effect that anyone assisting the bearer to safety will be rewarded. \glsseeformat[See also]{gov.mil.evasion_aid}{}. \glsadd{gov.mil.evasion_aid}(JP 3-50)}
}

\newglossaryentry{gov.mil.board}{
name={board},
description={An organized group of individuals within a headquarters, appointed and tasked by the commander (or other authority), that meets with the purpose of gaining guidance or decision. (JP 3-33)}
}

\newglossaryentry{gov.mil.boat_group}{
name={boat group},
description={A lane for amphibious assault landing craft, which extends from the line of departure to the beach. (JP 3-02)}
}

\newglossaryentry{gov.mil.boat_space}{
name={boat space},
description={The space and weight factor used in planning for one person with individual equipment to determine overall ship-to-shore movement requirements for boats, landing craft, and amphibious vehicles. (JP 3-02)}
}

\newglossaryentry{gov.mil.bona_fides}{
name={bona fides},
description={1. In personnel recovery, the use of verbal or visual communication by individuals who are unknown to one another, to establish their authenticity, sincerity, honesty, and truthfulness. \glsseeformat[See also]{gov.mil.evasion,gov.mil.recovery,gov.mil.recovery_operations}{}. \glsadd{gov.mil.evasion}\glsadd{gov.mil.recovery}\glsadd{gov.mil.recovery_operations}(JP 3-50) 2. The lack of fraud or deceit: a determination that a person is who he/she says he/she is. (JP 2-01.2)}
}

\newglossaryentry{gov.mil.boost_phase}{
name={boost phase},
description={That portion of the flight of a ballistic missile or space vehicle during which the booster and sustainer engines operate. \glsseeformat[See also]{gov.mil.midcourse_phase,gov.mil.terminal phase}{}. \glsadd{gov.mil.midcourse_phase}\glsadd{gov.mil.terminal}(JP 3-01)}
}

\newglossaryentry{gov.mil.bottom_mine}{
name={bottom mine},
description={A mine with negative buoyancy that remains on the seabed. \glsseeformat[See also]{gov.mil.mine}{}. \glsadd{gov.mil.mine}(JP 3-15)}
}

\newglossaryentry{gov.mil.boundary}{
name={boundary},
description={A line that delineates surface areas for the purpose of facilitating coordination and deconfliction of operations between adjacent units, formations, or areas. (JP 3-0)}
}

\newglossaryentry{gov.mil.branch}{
name={branch},
description={1. A subdivision of any organization. 2. A geographically separate unit of an activity, which performs all or part of the primary functions of the parent activity on a smaller scale. 3. An arm or service of the Army. 4. The contingency options built into the base plan used for changing the mission, orientation, or direction of movement of a force to aid success of the operation based on anticipated events, opportunities, or disruptions caused by enemy actions and reactions. \glsseeformat[See also]{gov.mil.sequel}{}. \glsadd{gov.mil.sequel}(JP 5-0)}
}

\newglossaryentry{gov.mil.breakbulk_ship}{
name={breakbulk ship},
description={A ship with conventional holds for stowage of breakbulk cargo and a limited number of containers, below or above deck, and equipped with cargo-handling gear. (JP 4-09)}
}

\newglossaryentry{gov.mil.brevity_code}{
name={brevity code},
description={A code word, which provides no security, that serves the sole purpose of shortening of messages rather than the concealment of their content. (JP 3-09.3)}
}

\newglossaryentry{gov.mil.brigade_combat_team}{
name={brigade combat team},
description={A combined arms team that forms the basic building block of the Army’s tactical formations. Also called BCT. (JP 3-31)}
}
\newacronym{gov.mil.bct}{BCT}{brigade combat team}

\newglossaryentry{gov.mil.broken_stowage}{
name={broken stowage},
description={The space lost in the holds of a vessel because of the contour of the ship, dunnage, ladders, stanchions, and the shape of the cargo. (JP 3-02)}
}

\newglossaryentry{gov.mil.broken_stowage_factor}{
name={broken stowage factor},
description={A factor applied to the available space for embarkation, due to the loss between boxes, between vehicles, around stanchions, and over cargo, that will vary depending on the type and size of vehicles, type and size of general cargo, training and experience of loading personnel, type of loading, method of stowage, and configuration of compartments. (JP 3-02)}
}

\newglossaryentry{gov.mil.buddy_aid}{
name={buddy aid},
description={Acute medical care (first aid) provided by a nonmedical Service member to another person. (JP 4-02)}
}

\newglossaryentry{gov.mil.buffer_zone}{
name={buffer zone},
description={1. A defined area controlled by a peace operations force from which disputing or belligerent forces have been excluded. Also called area of separation in some United Nations operations. Also called BZ. \glsseeformat[See also]{gov.mil.line_of_demarcation,gov.mil.peace_operations}{}. \glsadd{gov.mil.line_of_demarcation}\glsadd{gov.mil.peace_operations}(JP 3-07.3) 2. A designated area used for safety in military operations. (JP 3-01)}
}
\newacronym{gov.mil.bz}{BZ}{buffer zone}

\newglossaryentry{gov.mil.building_system}{
name={building system},
description={A structure assembled from manufactured components designed to provide a specific building configuration. (JP 3-34)}
}

\newglossaryentry{gov.mil.bulk_cargo}{
name={bulk cargo},
description={That which is generally shipped in volume where the transportation conveyance is the only external container; such as liquids, ore, or grain. (JP 4-01.5)}
}

\newglossaryentry{gov.mil.bulk_petroleum_product}{
name={bulk petroleum product},
description={A liquid petroleum product transported by various means and stored in tanks or containers having an individual fill capacity greater than 208 liters. (JP 4-03)}
}

\newglossaryentry{gov.mil.bulk_storage}{
name={bulk storage},
description={1. Storage in a warehouse of supplies and equipment in large quantities, usually in original containers, as distinguished from bin storage. 2. Storage of liquids, such as petroleum products in tanks, as distinguished from drum or packaged storage. (JP 4-03)}
}




















%:!!!!!!!!!!!!!!









%:C


\newglossaryentry{gov.mil.classification}{
name={classification},
description={The determination that official information requires, in the interests of national security, a specific degree of protection against unauthorized disclosure, coupled with a designation signifying that such a determination has been made. (JP 2-01.2)}
}

\newglossaryentry{gov.mil.classified_information}{
name={classified information},
description={Official information that has been determined to require, in the interests of national security, protection against unauthorized disclosure and which has been so designated. (JP 2-01.2)}
}






\newglossaryentry{gov.mil.clearance_decontamination}{
name={clearance decontamination},
description={The final level of decontamination that provides the decontamination of equipment and personnel to a level that allows unrestricted transportation, maintenance, employment, and disposal. (JP 3-11)}
}

\newglossaryentry{gov.mil.clearing_operation}{
name={clearing operation},
description={An operation designed to clear or neutralize all mines and obstacles from a route or area. (JP 3-15)}
}

\newglossaryentry{gov.mil.climate_change}{
name={climate change},
description={Variations in average weather conditions that persist over multiple decades or longer that encompass increases and decreases in temperature, shifts in precipitation, and changing risk of certain types of severe weather events. (DODD 4715.21)}
}

\newglossaryentry{gov.mil.close_air_support}{
name={close air support},
description={Air action by aircraft against hostile targets that are in close proximity to friendly forces and that require detailed integration of each air mission with the fire and movement of those forces. Also called CAS. \glsseeformat[See also]{gov.mil.air_interdiction}{}. \glsadd{gov.mil.air_interdiction}(JP 3- 09.3}
}
\newacronym{gov.mil.cas}{CAS}{close air support}

\newglossaryentry{gov.mil.close_range_ballistic_missile}{
name={close-range ballistic missile},
description={A land-based ballistic missile with a range capability up to 300 nautical miles. Also called CRBM. (JP 3-01)}
}
\newacronym{gov.mil.crbm}{CRBM}{close-range ballistic missile}



\newglossaryentry{gov.mil.collection}{
name={collection},
description={In intelligence usage, the acquisition of information and the provision of this information to processing elements. \glsseeformat[See also]{gov.mil.intelligence_process}{}.\glsadd{gov.mil.intelligence_process} (JP 2-01)}
}

\newglossaryentry{gov.mil.collection_agency}{
name={collection agency},
description={Any individual, organization, or unit that has access to sources of information and the capability of collecting information from them. \glsseeformat[See also]{gov.mil.agency}{}.\glsadd{gov.mil.agency} (JP 2-01)}
}








\newglossaryentry{gov.mil.combatant_command_support_agent}{
name={combatant command support agent},
description={The Secretary of a Military Department to whom the Secretary of Defense or the Deputy Secretary of Defense has assigned administrative and logistical support of the headquarters of a combatant command, United States Element, North American Aerospace Defense Command, or subordinate unified command. The nature and scope of the combatant command support agent responsibilities, functions, and authorities shall be prescribed at the time of assignment or in keeping with existing agreements and practices, and they shall remain in effect until the Secretary of Defense or the Deputy Secretary of Defense revokes, supersedes, or modifies them. (DODD 5100.03)}
}

\newglossaryentry{gov.mil.combat_assessment}{
name={combat assessment},
description={The determination of the overall effectiveness of force employment during military operations. Also called CA. \glsseeformat[See also]{gov.mil.battle_damage_assessment,gov.mil.munitions_effectiveness_assessment,gov.mil.reattack_recommendation}{}. \glsadd{gov.mil.battle_damage_assessment}\glsadd{gov.mil.munitions_effectiveness_assessment}\glsadd{gov.mil.reattack_recommendation}(JP 3-60)}
}
\newacronym{gov.mil.ca}{CA}{combat assessment}










\newglossaryentry{gov.mil.combat_air_patrol}{
name={combat air patrol},
description={An aircraft patrol provided over an objective area, the force protected, the critical area of a combat zone, or in an air defense area, for the purpose of intercepting and destroying hostile aircraft before they reach their targets. Also called CAP. \glsseeformat[See also]{gov.mil.airborne_alert,gov.mil.barrier_combat_air_patrol,gov.mil.rescue_combat_air_patrol}{}. \glsadd{gov.mil.airborne_alert}\glsadd{gov.mil.barrier_combat_air_patrol}\glsadd{gov.mil.rescue_combat_air_patrol}(JP 3-01)}
}
\newacronym{gov.mil.cap}{CAP}{combat air patrol}

\newglossaryentry{gov.mil.combat_and_operational_stress}{
name={combat and operational stress},
description={The expected and predictable emotional, intellectual, physical, and/or behavioral reactions of an individual who has been exposed to stressful events in military operations. (JP 4-02)}
}

\newglossaryentry{gov.mil.combat_and_operational_stress_control}{
name={combat and operational stress control},
description={Programs developed and actions taken by military leadership to prevent, identify, and manage adverse combat and operational stress reactions in units; optimize mission performance; conserve fighting strength; prevent or minimize adverse effects of combat and operational stress on members’ physical, psychological, intellectual, and social health; and to return the unit or Service member to duty expeditiously. Also called COSC. (JP 4-02)}
}
\newacronym{gov.mil.cosc}{COSC}{combat and operational stress control}

\newglossaryentry{gov.mil.combatant_command}{
name={combatant command},
description={A unified or specified command with a broad continuing mission under a single commander established and so designated by the President, through the Secretary of Defense and with the advice and assistance of the Chairman of the Joint Chiefs of Staff. Also called CCMD. \glsseeformat[See also]{gov.mil.specified_combatant_command,gov.mil.unified_command}{}. \glsadd{gov.mil.specified_combatant_command}\glsadd{gov.mil.unified_command}(JP 1)}
}
\newacronym{gov.mil.ccmd}{CCMD}{combatant command}

\newglossaryentry{gov.mil.combatant_command_chaplain}{
name={combatant command chaplain},
description={The senior chaplain assigned to the staff of, or designated by, the combatant commander to provide advice on religion, ethical, and moral issues and morale of assigned personnel and to coordinate religious ministries within the combatant commander’s area of responsibility. (JP 3-0)}
}

\newglossaryentry{gov.mil.combatant_command_command_authority}{
name={combatant command (command authority)},
description={Nontransferable command authority, which cannot be delegated, of a combatant commander to perform those functions of command over assigned forces involving organizing and employing commands and forces; assigning tasks; designating objectives; and giving authoritative direction over all aspects of military operations, joint training, and logistics necessary to accomplish the missions assigned to the command. Also called COCOM. \glsseeformat[See also]{gov.mil.combatant_command,gov.mil.combatant_commander,gov.mil.operational_control,gov.mil.tactical_control}{}. \glsadd{gov.mil.combatant_command}\glsadd{gov.mil.combatant_commander}\glsadd{gov.mil.operational_control}\glsadd{gov.mil.tactical_control}(JP 1)}
}
\newacronym{gov.mil.cocom}{COCOM}{combatant command (command authority)}

\newglossaryentry{gov.mil.combatant_commander}{
name={combatant commander},
description={A commander of one of the unified or specified combatant commands established by the President. Also called CCDR. \glsseeformat[See also]{gov.mil.combatant_command,gov.mil.specified_combatant_command,gov.mil.unified_combatant_command}{}. \glsadd{gov.mil.combatant_command}\glsadd{gov.mil.specified_combatant_command}\glsadd{gov.mil.unified_combatant_command}(JP 3-0)}
}
\newacronym{gov.mil.ccdr}{CCDR}{combatant commander}





\newglossaryentry{gov.mil.combating_terrorism}{
name={combating terrorism},
description={Actions, including antiterrorism and counterterrorism, taken to oppose terrorism throughout the entire threat spectrum. Also called CbT. \glsseeformat[See also]{gov.mil.antiterrorism,gov.mil.counterterrorism}{}. \glsadd{gov.mil.antiterrorism}\glsadd{gov.mil.counterterrorism}(JP 3-26)}
}
\newacronym{gov.mil.cbt}{CbT}{combating terrorism}

\newglossaryentry{gov.mil.combat_search_and_rescue}{
name={combat search and rescue},
description={The tactics, techniques, and procedures performed by forces to effect the recovery of isolated personnel during combat. Also called CSAR. \glsseeformat[See also]{gov.mil.search_and_rescue}{}. \glsadd{gov.mil.search_and_rescue} (JP 3-50)}
}
\newacronym{gov.mil.csar}{CSAR}{combat search and rescue}




\newglossaryentry{gov.mil.common_use}{
name={common use},
description={Services, materiel, or facilities provided by a Department of Defense agency or a Military Department on a common basis for two or more Department of Defense agencies, elements, or other organizations as directed. (JP 4-01.5)}
}


\newglossaryentry{gov.mil.common_user_logistics}{
name={common-user logistics},
description={Materiel or service support shared with or provided by two or more Services, Department of Defense agencies, or multinational partners to another Service, Department of Defense agency, non-Department of Defense agency, and/or multinational partner in an operation. Also called CUL. \glsseeformat[See also]{gov.mil.common_use}{}\glsadd{gov.mil.common_use} (JP 4-09)}
}
\newacronym{gov.mil.cul}{CUL}{common-user logistics}

\newglossaryentry{gov.mil.component}{
name={component},
description={1. One of the subordinate organizations that constitute a joint force. (JP 1) 2. In logistics, a part or combination of parts having a specific function, which can be installed or replaced only as an entity. \glsseeformat[See also]{gov.mil.functional_component_command,gov.mil.service_component_command}{}.\glsadd{gov.mil.functional_component_command}\glsadd{gov.mil.service_component_command} (JP 4-0)}
}

\newglossaryentry{gov.mil.communications_intelligence}{
name={communications intelligence},
description={Technical information and intelligence derived from foreign communications by other than the intended recipients. Also called COMINT. (JP 2-0)}
}
\newacronym{gov.mil.comint}{COMINT}{communications intelligence}



\newglossaryentry{gov.mil.contracting_officer}{
name={contracting officer},
description={A Service member or Department of Defense civilian with the legal authority to enter into, administer, modify, and/or terminate contracts. (JP 4-10)}
}

\newglossaryentry{gov.mil.contracting_officers_representative}{
name={contracting officer’s representative},
description={An individual designated in writing by the contracting officer to perform specific technical or administrative functions. Also called COR. (JP 4-10)}
}
\newacronym{gov.mil.cor}{COR}{contracting officer’s representative}

\newglossaryentry{gov.mil.contracting_support}{
name={contracting support},
description={The planning, coordination, and execution of contracting authority to legally bind contractors in support of military operations. (JP 4-10)}
}

\newglossaryentry{gov.mil.contractor_management}{
name={contractor management},
description={The oversight and integration of contractor personnel and associated equipment in support of military operations. (JP 4-10)}
}

\newglossaryentry{gov.mil.contractor_personnel_accountability}{
name={contractor personnel accountability},
description={The process of identifying, capturing, and recording the personally identifiable information and assigned primary duty location of an individual contractor employee through the use of a designated database. (JP 4-10)}
}

\newglossaryentry{gov.mil.contractors_authorized_to_accompany_the_force}{
name={contractors authorized to accompany the force},
description={Contractor employees and all tiers of subcontractor employees who are authorized to accompany the force in applicable contingency operations outside of the United States and have afforded such status through the issuance of a letter of authorization. Also called CAAF. (JP 4-10)}
}
\newacronym{gov.mil.caaf}{CAAF}{contractors authorized to accompany the force}

\newglossaryentry{gov.mil.contract_support_integration}{
name={contract support integration},
description={The planning, coordination, and synchronization of contracted support in military operations. (JP 4-10)}
}

\newglossaryentry{gov.mil.control}{
name={control},
description={1. Authority that may be less than full command exercised by a commander over part of the activities of subordinate or other organizations. (JP 1) 2. In mapping, charting, and photogrammetry, a collective term for a system of marks or objects on the Earth or on a map or a photograph, whose positions or elevations (or both) have been or will be determined. (JP 2-03) 3. Physical or psychological pressures exerted with the intent to assure that an agent or group will respond as directed. (JP 3-0) 4. In intelligence usage, an indicator governing the distribution and use of documents, information, or material. \glsseeformat[See also]{gov.mil.administrative_control,gov.mil.operational_control,gov.mil.tactical_control}{}. \glsadd{gov.mil.administrative_control}\glsadd{gov.mil.operational_control}\glsadd{gov.mil.tactical_control}(JP 2-01)}
}



\newglossaryentry{gov.mil.course_of_action}{
name={course of action},
description={1. Any sequence of activities that an individual or unit may follow. 2. A scheme developed to accomplish a mission. Also called COA. (JP 5-0)}
}
\newacronym{gov.mil.coa}{COA}{course of action}





\newglossaryentry{gov.mil.counterterrorism}{
name={counterterrorism},
description={Activities and operations taken to neutralize terrorists and their organizations and networks in order to render them incapable of using violence to instill fear and coerce governments or societies to achieve their goals. Also called CT. \glsseeformat[See also]{gov.mil.antiterrorism,gov.mil.combating_terrorism,gov.mil.terrorism}{}. \glsadd{gov.mil.antiterrorism}\glsadd{gov.mil.combating_terrorism}\glsadd{gov.mil.terrorism}(JP 3-26)}
}
\newacronym{gov.mil.ct}{CT}{counterterrorism}







\newglossaryentry{gov.mil.critical_intelligence}{
name={critical intelligence},
description={Intelligence that is crucial and requires the immediate attention of the commander. (JP 2-0)}
}



\newglossaryentry{gov.mil.cross_servicing}{
name={cross-servicing},
description={A subset of common-user logistics in which a function is performed by one Service in support of another Service and for which reimbursement is required from the Service receiving support. \glsseeformat[See also]{gov.mil.acquisition_and_cross_servicing_agreement,gov.mil.common_user_logistics}{}\glsadd{gov.mil.acquisition_and_cross_servicing_agreement}\glsadd{gov.mil.common_user_logistics} (JP 3-16)}
}



%:D

\newglossaryentry{gov.mil.decontamination}{
name={decontamination},
description={The process of making any person, object, or area safe by destroying, neutralizing, making harmless, or absorbing and removing chemical or biological agents or by removing radioactive material clinging to or around it. (JP 3-11)}
}




\newglossaryentry{gov.mil.departure_airfield}{
name={departure airfield},
description={An airfield on which troops and/or materiel are enplaned for flight. \glsseeformat[See also]{gov.mil.airfield}{}. \glsadd{gov.mil.airfield}(JP 3-17)}
}

\newglossaryentry{gov.mil.departure_point}{
name={departure point},
description={A navigational check point used by aircraft as a marker for setting course. (JP 3-17)}
}

\newglossaryentry{gov.mil.dependents}{
name={dependents},
description={An employee’s spouse; children who are unmarried and under age 21 years or who, regardless of age, are physically or mentally incapable of self-support; dependent parents, including step and legally adoptive parents of the employee’s spouse; and dependent brothers and sisters, including step and legally adoptive brothers and sisters of the employee’s spouse who are unmarried and under 21 years of age or who, regardless of age, are physically or mentally incapable of self-support. (JP 3-68)}
}




\newglossaryentry{gov.mil.desired_point_of_impact}{
name={desired point of impact},
description={A precise point associated with a target and assigned as the impact point for a single unitary weapon to create a desired effect. Also called DPI. \glsseeformat[See also]{gov.mil.aimpoint}{}.\glsadd{gov.mil.aimpoint} (JP 3-60)}
}
\newacronym{gov.mil.dpi}{DPI}{desired point of impact}


\newglossaryentry{gov.mil.directed_energy}{
name={directed energy},
description={An umbrella term covering technologies that relate to the production of a beam of concentrated electromagnetic energy or atomic or subatomic particles. Also called DE. \glsseeformat[See also]{gov.mil.directed_energy_device,gov.mil.directed_energy_weapon}{}.\glsadd{gov.mil.directed_energy_device}\glsadd{gov.mil.directed_energy_weapon} (JP 3-13.1)}
}
\newacronym{gov.mil.de}{DE}{directed energy}

\newglossaryentry{gov.mil.directed_energy_device}{
name={directed-energy device},
description={A system using directed energy primarily for a purpose other than as a weapon. \glsseeformat[See also]{gov.mil.directed_energy,gov.mil.directed_energy_weapon}{}.\glsadd{gov.mil.directed_energy}\glsadd{gov.mil.directed_energy_weapon} (JP 3-13.1)}
}

\newglossaryentry{gov.mil.directed_energy_warfare}{
name={directed-energy warfare},
description={Military action involving the use of directed-energy weapons, devices, and countermeasures. Also called DEW. \glsseeformat[See also]{gov.mil.directed_energy,gov.mil.directed_energy_device,gov.mil.directed_energy_weapon,gov.mil.electromagnetic_spectrum,gov.mil.electronic_warfare}{}.\glsadd{gov.mil.directed_energy}\glsadd{gov.mil.directed_energy_device}\glsadd{gov.mil.directed_energy_weapon}\glsadd{gov.mil.electromagnetic_spectrum}\glsadd{gov.mil.electronic_warfare} (JP 3-13.1)}
}
\newacronym{gov.mil.dew}{DEW}{directed-energy warfare}

\newglossaryentry{gov.mil.directed_energy_weapon}{
name={directed-energy weapon},
description={A weapon or system that uses directed energy to incapacitate, damage, or destroy enemy equipment, facilities, and/or personnel. \glsseeformat[See also]{gov.mil.directed_energy,gov.mil.directed_energy_device}{}.\glsadd{gov.mil.directed_energy}\glsadd{gov.mil.directed_energy_device} (JP 3-13.1)}
}




\newglossaryentry{gov.mil.dissemination}{
name={dissemination},
description={In intelligence usage, the delivery of intelligence to users in a suitable form. \glsseeformat[See also]{gov.mil.intelligence_process}{}.\glsadd{gov.mil.intelligence_process} (JP 2-01)}
}

\newglossaryentry{gov.mil.domestic_intelligence}{
name={domestic intelligence},
description={Intelligence relating to activities or conditions within the United States that threaten internal security and that might require the employment of troops; and intelligence relating to activities of individuals or agencies potentially or actually dangerous to the security of the Department of Defense. (JP 3-08)}
}




%:E





\newglossaryentry{gov.mil.electromagnetic_spectrum}{
name={electromagnetic spectrum},
description={The range of frequencies of electromagnetic radiation from zero to infinity. It is divided into 26 alphabetically designated bands. \glsseeformat[See also]{gov.mil.electronic_warfare}{}.\glsadd{gov.mil.electronic_warfare} (JP 3-13.1)}
}


\newglossaryentry{gov.mil.electronic_attack}{
name={electronic attack},
description={Division of electronic warfare involving the use of electromagnetic energy, directed energy, or antiradiation weapons to attack personnel, facilities, or equipment with the intent of degrading, neutralizing, or destroying enemy combat capability and is considered a form of fires. Also called EA. \glsseeformat[See also]{gov.mil.electronic_protection,gov.mil.electronic_warfare,gov.mil.electronic_warfare_support}{}.\glsadd{gov.mil.electronic_protection}\glsadd{gov.mil.electronic_warfare}\glsadd{gov.mil.electronic_warfare_support} (JP 3-13.1)}
}
\newacronym{gov.mil.ea}{EA}{electronic attack}


\newglossaryentry{gov.mil.electronic_intelligence}{
name={electronic intelligence},
description={Technical and geolocation intelligence derived from foreign noncommunications electromagnetic radiations emanating from other than nuclear detonations or radioactive sources. Also called ELINT. \glsseeformat[See also]{gov.mil.electronic_warfare,gov.mil.foreign_instrumentation_signals_intelligence,gov.mil.intelligence,gov.mil.signals_intelligence}{}.\glsadd{gov.mil.electronic_warfare}\glsadd{gov.mil.foreign_instrumentation_signals_intelligence}\glsadd{gov.mil.intelligence}\glsadd{gov.mil.signals_intelligence} (JP 3-13.1)}
}

\newglossaryentry{gov.mil.electronic_masking}{
name={electronic masking},
description={The controlled radiation of electromagnetic energy on friendly frequencies in a manner to protect the emissions of friendly communications and electronic systems against enemy electronic warfare support measures/signals intelligence without significantly degrading the operation of friendly systems. (JP 3-13.1)}
}

\newglossaryentry{gov.mil.electronic_probing}{
name={electronic probing},
description={Intentional radiation designed to be introduced into the devices or systems of potential enemies for the purpose of learning the functions and operational capabilities of the devices or systems. (JP 3-13.1)}
}

\newglossaryentry{gov.mil.electronic_protection}{
name={electronic protection},
description={Division of electronic warfare involving actions taken to protect personnel, facilities, and equipment from any effects of friendly or enemy use of the electromagnetic spectrum that degrade, neutralize, or destroy friendly combat capability. Also called EP. \glsseeformat[See also]{gov.mil.electronic_attack,gov.mil.electronic_warfare,gov.mil.electronic_warfare_support}{}.\glsadd{gov.mil.electronic_attack}\glsadd{gov.mil.electronic_warfare}\glsadd{gov.mil.electronic_warfare_support} (JP 3-13.1)}
}
\newacronym{gov.mil.ep}{EP}{electronic protection}

\newglossaryentry{gov.mil.electronics_security}{
name={electronics security},
description={The protection resulting from all measures designed to deny unauthorized persons information of value that might be derived from their interception and study of noncommunications electromagnetic radiations, e.g., radar. (JP 3-13.1)}
}

\newglossaryentry{gov.mil.electronic_warfare}{
name={electronic warfare},
description={Military action involving the use of electromagnetic and directed energy to control the electromagnetic spectrum or to attack the enemy. Also called EW. \glsseeformat[See also]{gov.mil.directed_energy,gov.mil.electromagnetic_spectrum,gov.mil.electronic_attack,gov.mil.electronic_protection,gov.mil.electronic_warfare_support}{}.\glsadd{gov.mil.directed_energy}\glsadd{gov.mil.electromagnetic_spectrum}\glsadd{gov.mil.electronic_attack}\glsadd{gov.mil.electronic_protection}\glsadd{gov.mil.electronic_warfare_support} (JP 3-13.1)}
}
\newacronym{gov.mil.ew}{EW}{electronic warfare}


\newglossaryentry{gov.mil.electronic_warfare_support}{
name={electronic warfare support},
description={Division of electronic warfare involving actions tasked by, or under direct control of, an operational commander to search for, intercept, identify, and locate or localize sources of intentional and unintentional radiated electromagnetic energy for the purpose of immediate threat recognition, targeting, planning and conduct of future operations. Also called ES. \glsseeformat[See also]{gov.mil.electronic_attack,gov.mil.electronic_protection,gov.mil.electronic_warfare}{}.\glsadd{gov.mil.electronic_attack}\glsadd{gov.mil.electronic_protection}\glsadd{gov.mil.electronic_warfare} (JP 3-13.1)}
}
\newacronym{gov.mil.es}{ES}{electronic warfare support}





\newglossaryentry{gov.mil.exploitation}{
name={exploitation},
description={1. Taking full advantage of success in military operations, following up initial gains, and making permanent the temporary effects already created. 2. Taking full advantage of any information that has come to hand for tactical, operational, or strategic purposes. 3. An offensive operation that usually follows a successful attack and is designed to disorganize the enemy in depth. See also attack. (JP 2-01.3)}
}




\newglossaryentry{gov.mil.evader}{
name={evader},
description={Any person isolated in hostile or unfriendly territory who eludes capture. (JP 3-50)}
}

\newglossaryentry{gov.mil.evaluation_and_feedback}{
name={evaluation and feedback},
description={In intelligence usage, continuous assessment of intelligence operations throughout the intelligence process to ensure that the commander’s intelligence requirements are being met. \glsseeformat[See also]{gov.mil.intelligence_process}{}.\glsadd{gov.mil.intelligence_process} (JP 2-01)}
}




\newglossaryentry{gov.mil.evasion}{
name={evasion},
description={The process whereby isolated personnel avoid capture with the goal of successfully returning to areas under friendly control. (JP 3-50)}
}

\newglossaryentry{gov.mil.evasion_aid}{
name={evasion aid},
description={In personnel recovery, any piece of information or equipment designed to assist an individual in avoiding capture. \glsseeformat[See also]{gov.mil.blood_chit,gov.mil.evasion,gov.mil.evasion_chart,gov.mil.pointee_talkee,gov.mil.recovery,gov.mil.recovery_operations}{}. \glsadd{gov.mil.blood_chit}\glsadd{gov.mil.evasion}\glsadd{gov.mil.evasion_chart}\glsadd{gov.mil.pointee_talkee}\glsadd{gov.mil.recovery}\glsadd{gov.mil.recovery_operations}(JP 3-50)}
}

\newglossaryentry{gov.mil.evasion_chart}{
name={evasion chart},
description={A special map or chart designed as an evasion aid. Also called EVC. \glsseeformat[See also]{gov.mil.evasion,gov.mil.evasion_aid}{}. \glsadd{gov.mil.evasion}\glsadd{gov.mil.evasion_aid}(JP 3-50)}
}
\newacronym{gov.mil.evc}{EVC}{evasion chart}










%:F

\newglossaryentry{gov.mil.facility}{
name={facility},
description={A real property entity consisting of one or more of the following: a building, a structure, a utility system, pavement, and underlying land. (JP 3-34)}
}

\newglossaryentry{gov.mil.facility_substitutes}{
name={facility substitutes},
description={Items such as tents and prepackaged structures requisitioned through the supply system that may be used to substitute for constructed facilities. (JP 3-34)}
}

\newglossaryentry{gov.mil.family_readiness}{
name={family readiness},
description={The state of being prepared to effectively navigate the challenges of daily living experienced in the unique context of military service, to include: mobility and financial readiness, mobilization and deployment readiness, and personal and family life readiness. (DODI 1342.22)}
}














\newglossaryentry{gov.mil.feasibility}{
name={feasibility},
description={The plan review criterion for assessing whether the assigned mission can be accomplished using available resources within the time contemplated by the plan. \glsseeformat[See also]{gov.mil.acceptability,gov.mil.adequacy}{}\glsadd{gov.mil.acceptability}\glsadd{gov.mil.adequacy} (JP 5-0)}
}

\newglossaryentry{gov.mil.federal_service}{
name={federal service},
description={A term applied to National Guard members and units when called to active duty to serve the United States Government under Article I, Section 8 and Article II, Section 2 of the Constitution and Title 10, United States Code, Sections 12401 to 12408. \glsseeformat[See also]{gov.mil.active_duty,gov.mil.reserve_component}{}\glsadd{gov.mil.active_duty}\glsadd{gov.mil.reserve_component}. (JP 4-05)}
}







\newglossaryentry{gov.mil.force}{
name={force},
description={1. An aggregation of military personnel, weapon systems, equipment, and necessary support, or combination thereof. 2. A major subdivision of a fleet. (JP 1)}
}








\newglossaryentry{gov.mil.force_protection}{
name={force protection},
description={Preventive measures taken to mitigate hostile actions against Department of Defense personnel (to include family members), resources, facilities, and critical information. Also called FP. \glsseeformat[See also]{gov.mil.force,gov.mil.force_protection_condition,gov.mil.protection}{}. \glsadd{gov.mil.force}\glsadd{gov.mil.force_protection_condition}\glsadd{gov.mil.protection}(JP 3-0)}
}
\newacronym{gov.mil.fp}{FP}{force protection}

\newglossaryentry{gov.mil.force_protection_condition}{
name={force protection condition},
description={A Chairman of the Joint Chiefs of Staff-approved standard for identification of and recommended responses to terrorist threats against United States personnel and facilities. Also called FPCON. \glsseeformat[See also]{gov.mil.antiterrorism,gov.mil.force_protection}{}. \glsadd{gov.mil.antiterrorism}\glsadd{gov.mil.force_protection}(JP 3-07.2)}
}
\newacronym{gov.mil.fpcon}{FPCON}{force protection condition}













\newglossaryentry{gov.mil.foreign_instrumentation_signals_intelligence}{
name={foreign instrumentation signals intelligence},
description={A subcategory of signals intelligence consisting of technical information and intelligence derived from the intercept of foreign electromagnetic emissions associated with the testing and operational deployment of non-United States aerospace, surface, and subsurface systems. Also called FISINT. \glsseeformat[See also]{gov.mil.signals_intelligence}{}.\glsadd{gov.mil.signals_intelligence} (JP 2-01)}
}
\newacronym{gov.mil.fisint}{FISINT}{foreign instrumentation signals intelligence}


\newglossaryentry{gov.mil.foreign_intelligence}{
name={foreign intelligence},
description={Information relating to capabilities, intentions, and activities of foreign governments or elements thereof, foreign organizations, or foreign persons, or international terrorist activities. Also called FI. \glsseeformat[See also]{gov.mil.intelligence}{}\glsadd{gov.mil.intelligence}. (JP 2-0)}
}
\newacronym{gov.mil.fi}{FI}{foreign intelligence}



\newglossaryentry{gov.mil.free_drop}{
name={free drop},
description={The dropping of equipment or supplies from an aircraft without the use of parachutes. \glsseeformat[See also]{gov.mil.airdrop,gov.mil.air_movement,gov.mil.free_fall,gov.mil.high_velocity_drop,gov.mil.low_velocity_drop}{}. \glsadd{gov.mil.airdrop}\glsadd{gov.mil.air_movement}\glsadd{gov.mil.free_fall}\glsadd{gov.mil.high_velocity_drop}\glsadd{gov.mil.low_velocity_drop}(JP 3-17)}
}

\newglossaryentry{gov.mil.free_fall}{
name={free fall},
description={A parachute maneuver in which the parachute is manually activated at the discretion of the jumper or automatically at a preset altitude. \glsseeformat[See also]{gov.mil.airdrop,gov.mil.air_movement,gov.mil.free_fall,gov.mil.high_velocity_drop,gov.mil.low_velocity_drop}{}. \glsadd{gov.mil.airdrop}\glsadd{gov.mil.air_movement}\glsadd{gov.mil.free_drop}\glsadd{gov.mil.high_velocity_drop}\glsadd{gov.mil.low_velocity_drop}(JP 3-17)}
}

\newglossaryentry{gov.mil.free_fire_area }{
name={free-fire area},
description={A specific region into which any weapon system may fire without additional coordination with the establishing headquarters. Also called FFA. (JP 3-09)}
}
\newacronym{gov.mil.ffa}{FFA}{free-fire area}

\newglossaryentry{gov.mil.free_mail}{
name={free mail},
description={Correspondence of a personal nature that weighs less than 11 ounces, to include audio and video recording tapes, from a member of the Armed Forces or designated civilian, mailed postage free from a Secretary of Defense approved free mail zone. (JP 1-0)}
}




\newglossaryentry{gov.mil.functional_component_command}{
name={functional component command},
description={A command normally, but not necessarily, composed of forces of two or more Military Departments which may be established across the range of military operations to perform particular operational missions that may be of short duration or may extend over a period of time. \glsseeformat[See also]{gov.mil.component,gov.mil.service_component_command}{}.\glsadd{gov.mil.component}\glsadd{gov.mil.service_component_command} (JP 1)}
}




%:G

\newglossaryentry{gov.mil.general_military_intelligence}{
name={general military intelligence},
description={Intelligence concerning the military capabilities of foreign countries or organizations, or topics affecting potential United States or multinational military operations. Also called GMI. \glsseeformat[See also]{gov.mil.intelligence}{}.\glsadd{gov.mil.intelligence} (JP 2-0)}
}
\newacronym{gov.mil.gmi}{GMI}{general military intelligence}

\newglossaryentry{gov.mil.ground_alert}{
name={ground alert},
description={That status in which aircraft on the ground/deck are fully serviced and armed, with combat crews in readiness to take off within a specified period of time after receipt of a mission order. \glsseeformat[See also]{gov.mil.airborne_alert}{}. \glsadd{gov.mil.airborne_alert}(JP 3-01)}
}

\newglossaryentry{gov.mil.ground_based_interceptor}{
name={ground-based interceptor},
description={A fixed-based, surface-to-air missile for defense against long- range ballistic missiles using an exo-atmospheric hit-to-kill interception of the targeted reentry vehicle in the midcourse phase of flight. (JP 3-01)}
}

\newglossaryentry{gov.mil.ground_based_midcourse_defense}{
name={ground-based midcourse defense},
description={A surface-to-air ballistic missile defense system for exo-atmospheric midcourse phase interception of long-range ballistic missiles using the ground-based interceptors. Also called GMD. (JP 3-01)}
}
\newacronym{gov.mil.gmd}{GMD}{ground-based midcourse defense}

\newglossaryentry{gov.mil.group}{
name={group},
description={A long-standing functional organization that is formed to support a broad function within a headquarters. (JP 3-33)}
}

\newglossaryentry{gov.mil.guarded_frequencies}{
name={guarded frequencies},
description={A list of time-oriented, enemy frequencies that are currently being exploited for combat information and intelligence or jammed after the commander has weighed the potential operational gain against the loss of the technical information. \glsseeformat[See also]{gov.mil.electronic_warfare}{}. \glsadd{gov.mil.electronic_warfare}(JP 3-13.1)}
}

\newglossaryentry{gov.mil.guerrilla_force}{
name={guerrilla force},
description={A group of irregular, predominantly indigenous personnel organized along military lines to conduct military and paramilitary operations in enemy-held, hostile, or denied territory. (JP 3-05)}
}

\newglossaryentry{gov.mil.guided_missile}{
name={guided missile},
description={An unmanned vehicle moving above the surface of the Earth whose trajectory or flight path is capable of being altered by an external or internal mechanism. \glsseeformat[See also]{gov.mil.ballistic_missile}{}. \glsadd{gov.mil.ballistic_missile}(JP 3-01)}
}

\newglossaryentry{gov.mil.gun_target_line}{
name={gun-target line},
description={An imaginary straight line from gun to target. Also called GTL. (JP 3-09.3)}
}
\newacronym{gov.mil.gtl}{GTL}{gun-target line}




%:H

\newglossaryentry{gov.mil.high_density_airspace_control_zone}{
name={high-density airspace control zone},
description={Airspace designated in an airspace control plan or airspace control order in which there is a concentrated employment of numerous and varied weapons and airspace users. Also called HIDACZ. (JP 3-52)}
}
\newacronym{gov.mil.hidacz}{HIDACZ}{high-density airspace control zone}

\newglossaryentry{gov.mil.high_velocity_drop}{
name={high velocity drop},
description={A drop procedure in which the drop velocity is greater than 30 feet per second and lower than free drop velocity. \glsseeformat[See also]{gov.mil.airdrop}{}. \glsadd{gov.mil.airdrop}(JP 3-17)}
}

\newglossaryentry{gov.mil.homeland}{
name={homeland},
description={The physical region that includes the continental United States, Alaska, Hawaii, United States territories, and surrounding territorial waters and airspace. (JP 3-28)}
}

\newglossaryentry{gov.mil.homeland_defense}{
name={homeland defense},
description={The protection of United States sovereignty, territory, domestic population, and critical infrastructure against external threats and aggression or other threats as directed by the President. Also called HD. (JP 3-27)}
}
\newacronym{gov.mil.hd}{HD}{homeland defense}

\newglossaryentry{gov.mil.homeland_security}{
name={homeland security},
description={A concerted national effort to prevent terrorist attacks within the United States; reduce America’s vulnerability to terrorism, major disasters, and other emergencies; and minimize the damage and recover from attacks, major disasters, and other emergencies that occur. Also called HS. (JP 3-27)}
}
\newacronym{gov.mil.hs}{HS}{homeland security}

\newglossaryentry{gov.mil.home_station}{
name={home station},
description={The permanent location of active duty units and Reserve Component units. \glsseeformat[See also]{gov.mil.active_duty,gov.mil.reserve_component}{}. \glsadd{gov.mil.active_duty}\glsadd{gov.mil.reserve_component}(JP 4-05)}
}

\newglossaryentry{gov.mil.homing}{
name={homing},
description={The technique whereby a mobile station directs itself, or is directed, towards a source of primary or reflected energy, or to a specified point. (JP 3-50)}
}

\newglossaryentry{gov.mil.homing_adaptor}{
name={homing adaptor},
description={A device, when used with an aircraft radio receiver, that produces aural and/or visual signals indicating the direction of a transmitting radio station with respect to the heading of the aircraft. (JP 3-50)}
}

\newglossaryentry{gov.mil.horizontal_stowage}{
name={horizontal stowage},
description={The lateral distribution of unit equipment or categories of supplies so they can be unloaded simultaneously from two or more holds. (JP 3-02)}
}

\newglossaryentry{gov.mil.hostage_rescue}{
name={hostage rescue},
description={A personnel recovery method used to recover isolated personnel who are specifically designated as hostages. Also called HR. (JP 3-50)}
}
\newacronym{gov.mil.hr}{HR}{hostage rescue}

\newglossaryentry{gov.mil.hostile_act}{
name={hostile act},
description={An attack or other use of force against the United States, United States forces, or other designated persons or property to preclude or impede the mission and/or duties of United States forces, including the recovery of United States personnel or vital United States Government property. (JP 3-28)}
}

\newglossaryentry{gov.mil.hostile_environment}{
name={hostile environment},
description={Operational environment in which host government forces, whether opposed to or receptive to operations that a unit intends to conduct, do not have control of the territory and population in the intended operational area. (JP 3-0)}
}

\newglossaryentry{gov.mil.hostile_intent}{
name={hostile intent},
description={The threat of imminent use of force against the United States, United States forces, or other designated persons or property. (JP 3-01)}
}

\newglossaryentry{gov.mil.host_nation}{
name={host nation},
description={A nation which receives forces and/or supplies from allied nations and/or North Atlantic Treaty Organization to be located on, to operate in, or to transit through its territory. Also called HN. (JP 3-57)}
}
\newacronym{gov.mil.hn}{HN}{host nation}

\newglossaryentry{gov.mil.host_nation_support}{
name={host-nation support},
description={Civil and/or military assistance rendered by a nation to foreign forces within its territory during peacetime, crises or emergencies, or war based on agreements mutually concluded between nations. Also called HNS. \glsseeformat[See also]{gov.mil.host_nation}{}. \glsadd{gov.mil.host_nation}(JP 4-0)}
}
\newacronym{gov.mil.hns}{HNS}{host-nation support}




%:I

\newglossaryentry{gov.mil.imagery_intelligence}{
name={imagery intelligence},
description={The technical, geographic, and intelligence information derived through the interpretation or analysis of imagery and collateral materials. Also called IMINT. \glsseeformat[See also]{gov.mil.intelligence}{}.\glsadd{gov.mil.intelligence} (JP 2-03)}
}
\newacronym{gov.mil.imint}{IMINT}{imagery intelligence}


\newglossaryentry{gov.mil.inactive_duty_training}{
name={inactive duty training},
description={Authorized training performed by a member of a Reserve Component not on active duty or active duty for training and consisting of regularly scheduled unit training assemblies, additional training assemblies, periods of appropriate duty or equivalent training, and any special additional duties authorized for Reserve Component personnel by the Secretary concerned, and performed by them in connection with the prescribed activities of the organization in which they are assigned with or without pay.  \glsseeformat[See also]{gov.mil.active_duty_for_training}{}.\glsadd{gov.mil.active_duty_for_training} (JP 1)}
}

\newglossaryentry{gov.mil.intelligence}{
name={intelligence},
description={1. The product resulting from the collection, processing, integration, evaluation, analysis, and interpretation of available information concerning foreign nations, hostile or potentially hostile forces or elements, or areas of actual or potential operations. 2. The activities that result in the product. 3. The organizations engaged in such activities. \glsseeformat[See also]{gov.mil.acoustic_intelligence,gov.mil.all_source_intelligence,gov.mil.communications_intelligence,gov.mil.critical_intelligence,gov.mil.domestic_intelligence,gov.mil.domestic_intelligence,gov.mil.electronic_intelligence,gov.mil.foreign_intelligence,gov.mil.foreign_instrumentation_signals_intelligence,gov.mil.general_military_intelligence,gov.mil.imagery_intelligence,gov.mil.joint_intelligence,gov.mil.measurement_and_signature_intelligence,gov.mil.medical_intelligence,gov.mil.national_intelligence,gov.mil.open_source_intelligence,gov.mil.operational_intelligence,gov.mil.scientific_and_technical_intelligence,gov.mil.strategic_intelligence,gov.mil.tactical_intelligence,gov.mil.target_intelligence,gov.mil.technical_intelligence}{}.\glsadd{gov.mil.acoustic_intelligence}\glsadd{gov.mil.all_source_intelligence}\glsadd{gov.mil.communications_intelligence}\glsadd{gov.mil.critical_intelligence}\glsadd{gov.mil.domestic_intelligence}\glsadd{gov.mil.domestic_intelligence}\glsadd{gov.mil.electronic_intelligence}\glsadd{gov.mil.foreign_intelligence}\glsadd{gov.mil.foreign_instrumentation_signals_intelligence}\glsadd{gov.mil.general_military_intelligence}\glsadd{gov.mil.imagery_intelligence}\glsadd{gov.mil.joint_intelligence}\glsadd{gov.mil.measurement_and_signature_intelligence}\glsadd{gov.mil.medical_intelligence}\glsadd{gov.mil.national_intelligence}\glsadd{gov.mil.open_source_intelligence}\glsadd{gov.mil.operational_intelligence}\glsadd{gov.mil.scientific_and_technical_intelligence}\glsadd{gov.mil.strategic_intelligence}\glsadd{gov.mil.tactical_intelligence}\glsadd{gov.mil.target_intelligence}\glsadd{gov.mil.technical_intelligence} (JP 2-0)}
}

\newglossaryentry{gov.mil.intelligence_process}{
name={intelligence process},
description={The process by which information is converted into intelligence and made available to users, consisting of the six interrelated intelligence operations: planning and direction, collection, processing and exploitation, analysis and production, dissemination and integration, and evaluation and feedback. \glsseeformat[See also]{gov.mil.analysis_and_production,gov.mil.collection,gov.mil.dissemination,gov.mil.evaluation_and_feedback,gov.mil.intelligence,gov.mil.planning_and_direction,gov.mil.processing_and_exploitation}{}.\glsadd{gov.mil.analysis_and_production}\glsadd{gov.mil.collection}\glsadd{gov.mil.dissemination}\glsadd{gov.mil.evaluation_and_feedback}\glsadd{gov.mil.intelligence}\glsadd{gov.mil.planning_and_direction}\glsadd{gov.mil.processing_and_exploitation} (JP 2-01)}
}




\newglossaryentry{gov.mil.intertheater_airlift}{
name={intertheater airlift},
description={The common-user airlift linking theaters to the continental United States and to other theaters, as well as the airlift within the continental United States. \glsseeformat[See also]{gov.mil.intratheater_airlift}{}. \glsadd{gov.mil.intratheater_airlift}(JP 3-17)}
}




\newglossaryentry{gov.mil.intratheater_airlift}{
name={intratheater airlift},
description={Airlift conducted within a theater with assets assigned to a geographic combatant commander or attached to a subordinate joint force commander. \glsseeformat[See also]{gov.mil.intertheater_airlift}{}. \glsadd{gov.mil.intertheater_airlift}(JP 3-17)}
}







\newglossaryentry{gov.mil.isolated_personnel}{
name={isolated personnel},
description={United States military, Department of Defense civilians and contractor personnel (and others designated by the President or Secretary of Defense) who are separated from their unit (as an individual or a group) while participating in a United States sponsored military activity or mission and are, or may be, in a situation where they must survive, evade, resist, or escape. \glsseeformat[See also]{gov.mil.combat_search_and_rescue,gov.mil.search_and_rescue}{}. \glsadd{gov.mil.combat_search_and_rescue}\glsadd{gov.mil.search_and_rescue}(JP 3-50)}
}

\newglossaryentry{gov.mil.isolated_personnel_report}{
name={isolated personnel report},
description={A Department of Defense form containing information designed to facilitate the identification and authentication of an isolated person by a recovery force. Also called ISOPREP. \glsseeformat[See also]{gov.mil.authentication,gov.mil.evader}{}. \glsadd{gov.mil.authentication}\glsadd{gov.mil.evader}(JP 3-50)}
}
\newacronym{gov.mil.isoprep}{ISOPREP}{isolated personnel report}

\newglossaryentry{gov.mil.item_manager}{
name={item manager},
description={An individual within the organization of an inventory control point or other such organization assigned management responsibility for one or more specific items of materiel. (JP 4-09)}
}



%:J

\newglossaryentry{gov.mil.joint_air_operations}{
name={joint air operations},
description={Air operations performed with air capabilities/forces made available by components in support of the joint force commander’s operation or campaign objectives, or in support of other components of the joint force. (JP 3-30)}
}



\newglossaryentry{gov.mil.joint_air_operations_center}{
name={joint air operations center},
description={A jointly staffed facility established for planning, directing, and executing joint air operations in support of the joint force commander’s operation or campaign objectives. Also called JAOC. \glsseeformat[See also]{gov.mil.joint_air_operations}{}.\glsadd{gov.mil.joint_air_operations} (JP 3-30)}
}
\newacronym{gov.mil.jaoc}{JAOC}{joint air operations center}

\newglossaryentry{gov.mil.joint_intelligence}{
name={joint intelligence},
description={Intelligence produced by elements of more than one Service of the same nation. (JP 2-0)}
}


\newglossaryentry{gov.mil.joint_force}{
name={joint force},
description={A force composed of elements, assigned or attached, of two or more Military Departments operating under a single joint force commander. \glsseeformat[See also]{gov.mil.joint_force_commander}{}. \glsadd{gov.mil.joint_force_commander}(JP 3-0)}
}

\newglossaryentry{gov.mil.joint_force_air_component_commander}{
name={joint force air component commander},
description={The commander within a unified command, subordinate unified command, or joint task force responsible to the establishing commander for recommending the proper employment of assigned, attached, and/or made available for tasking air forces; planning and coordinating air operations; or accomplishing such operational missions as may be assigned. Also called JFACC. \glsseeformat[See also]{gov.mil.joint_force_commander}{}. \glsadd{gov.mil.joint_force_commander}(JP 3-0)}
}
\newacronym{gov.mil.jfacc}{JFACC}{joint force air component commander}

\newglossaryentry{gov.mil.joint_force_chaplain}{
name={joint force chaplain},
description={The military chaplain designated by the joint force commander to serve as the senior chaplain for the joint force. Also called the JFCH. (JP 3-0)}
}
\newacronym{gov.mil.jfch}{JFCH}{joint force chaplain}


\newglossaryentry{gov.mil.joint_force_commander}{
name={joint force commander},
description={A general term applied to a combatant commander, subunified commander, or joint task force commander authorized to exercise combatant command (command authority) or operational control over a joint force. Also called JFC. \glsseeformat[See also]{gov.mil.joint_force}{}. \glsadd{gov.mil.joint_force}(JP 1)}
}
\newacronym{gov.mil.jfc}{JFC}{joint force commander}

\newglossaryentry{gov.mil.joint_force_land_component_commander}{
name={joint force land component commander},
description={The commander within a unified command, subordinate unified command, or joint task force responsible to the establishing commander for recommending the proper employment of assigned, attached, and/or made available for tasking land forces; planning and coordinating land operations; or accomplishing such operational missions as may be assigned. Also called JFLCC. \glsseeformat[See also]{gov.mil.joint_force_commander}{}. \glsadd{gov.mil.joint_force_commander}(JP 3-0)}
}
\newacronym{gov.mil.jflcc}{JFLCC}{joint force land component commander}

\newglossaryentry{gov.mil.joint_force_maritime_component_commander}{
name={joint force maritime component commander},
description={The commander within a unified command, subordinate unified command, or joint task force responsible to the establishing commander for recommending the proper employment of assigned, attached, and/or made available for tasking maritime forces and assets; planning and coordinating maritime operations; or accomplishing such operational missions as may be assigned. Also called JFMCC. \glsseeformat[See also]{gov.mil.joint_force_commander}{}. \glsadd{gov.mil.joint_force_commander}(JP 3-0)}
}
\newacronym{gov.mil.jfmcc}{JFMCC}{joint force maritime component commander}

\newglossaryentry{gov.mil.joint_force_special_operations_component_commander}{
name={joint force special operations component commander},
description={The commander within a unified command, subordinate unified command, or joint task force responsible to the establishing commander for recommending the proper employment of assigned, attached, and/or made available for tasking special operations forces and assets; planning and coordinating special operations; or accomplishing such operational missions as may be assigned. Also called JFSOCC. \glsseeformat[See also]{gov.mil.joint_force_commander}{}. \glsadd{gov.mil.joint_force_commander}(JP 3-0)}
}
\newacronym{gov.mil.jfsocc}{JFSOCC}{joint force special operations component commander}



\newglossaryentry{gov.mil.joint_operations}{
name={joint operations},
description={Military actions conducted by joint forces and those Service forces employed in specified command relationships with each other, which of themselves, do not establish joint forces. (JP 3-0)}
}

\newglossaryentry{gov.mil.joint_operations_area}{
name={joint operations area},
description={An area of land, sea, and airspace, defined by a geographic combatant commander or subordinate unified commander, in which a joint force commander (normally a joint task force commander) conducts military operations to accomplish a specific mission. Also called JOA. \glsseeformat[See also]{gov.mil.area_of_responsibility,gov.mil.joint_special_operations_area}{}. \glsadd{gov.mil.area_of_responsibility}\glsadd{gov.mil.joint_special_operations_area}(JP 3-0)}
}
\newacronym{gov.mil.joa}{JOA}{joint operations area}





\newglossaryentry{gov.mil.joint_special_operations_area}{
name={joint special operations area},
description={An area of land, sea, and airspace assigned by a joint force commander to the commander of a joint special operations force to conduct special operations activities. Also called JSOA. (JP 3-0)}
}
\newacronym{gov.mil.jsoa}{JSOA}{joint special operations area}



\newglossaryentry{gov.mil.joint_personnel_recovery_center}{
name={joint personnel recovery center},
description={The primary joint force organization responsible for planning and coordinating personnel recovery for military operations within the assigned operational area. Also called JPRC. \glsseeformat[See also]{gov.mil.combat_search_and_rescue,gov.mil.search_and_rescue}{}. \glsadd{gov.mil.combat_search_and_rescue}\glsadd{gov.mil.search_and_rescue}(JP 3-50)}
}
\newacronym{gov.mil.jprc}{JPRC}{joint personnel recovery center}

\newglossaryentry{gov.mil.joint_personnel_training_and_tracking_activity}{
name={joint personnel training and tracking activity},
description={The continental United States center established to facilitate the reception, accountability, processing, training, and onward movement of individual augmentees preparing for overseas movement to support a joint military operation. Also called JPTTA. (JP 1-0)}
}
\newacronym{gov.mil.jptta}{JPTTA}{joint personnel training and tracking activity}

%:K



%:L

\newglossaryentry{gov.mil.land_domain}{
name={land domain},
description={The area of the Earth’s surface ending at the high water mark and overlapping with the maritime domain in the landward segment of the littorals. (JP 3-31)}
}

\newglossaryentry{gov.mil.land_forces}{
name={land forces},
description={Personnel, weapon systems, vehicles, and support elements operating on land to accomplish assigned missions and tasks. (JP 3-31)}
}

\newglossaryentry{gov.mil.landing_area}{
name={landing area},
description={1. That part of the operational area within which are conducted the landing operations of an amphibious force. 2. In airborne operations, the general area used for landing troops and materiel either by airdrop or air landing. 3. Any specially prepared or selected surface of land, water, or deck designated or used for takeoff and landing of aircraft. \glsseeformat[See also]{gov.mil.airfield,gov.mil.amphibious_force,gov.mil.landing_beach,gov.mil.landing_force}{}. \glsadd{gov.mil.airfield}\glsadd{gov.mil.amphibious_force}\glsadd{gov.mil.landing_beach}\glsadd{gov.mil.landing_force}(JP 3-02)}
}

\newglossaryentry{gov.mil.landing_area_diagram}{
name={landing area diagram},
description={A graphic means of showing the beach designations, boat lanes, organization of the line of departure, scheduled waves, landing ship area, transport areas, and the fire support areas in the immediate vicinity of the boat lanes. (JP 3-02)}
}

\newglossaryentry{gov.mil.landing_beach}{
name={landing beach},
description={That portion of a shoreline required for the landing of an amphibious force. (JP 3-02)}
}

\newglossaryentry{gov.mil.landing_craft}{
name={landing craft},
description={A craft employed in amphibious operations specifically designed for carrying troops and their equipment and for beaching, unloading, retracting, and resupply operations. (JP 3-02)}
}

\newglossaryentry{gov.mil.landing_craft_and_amphibious_vehicle_assignment_table}{
name={landing craft and amphibious vehicle assignment table},
description={A table showing the assignment of personnel and materiel to each landing craft and amphibious vehicle and the assignment of the landing craft and amphibious vehicles to waves for the ship-to- shore movement. (JP 3-02)}
}

\newglossaryentry{gov.mil.landing_craft_availability_table}{
name={landing craft availability table},
description={A tabulation of the type and number of landing craft that will be available from each ship of the transport group. (JP 3-02)}
}

\newglossaryentry{gov.mil.landing_diagram}{
name={landing diagram},
description={A graphic means of illustrating the plan for the ship-to-shore movement. (JP 3-02)}
}

\newglossaryentry{gov.mil.landing_force}{
name={landing force},
description={A Marine Corps or Army task organization, which is part of the amphibious force, formed to conduct amphibious operations. Also called LF. \glsseeformat[See also]{gov.mil.amphibious_force,gov.mil.amphibious_operation,gov.mil.amphibious_task_force,gov.mil.task_organization}{}. \glsadd{gov.mil.amphibious_force}\glsadd{gov.mil.amphibious_operation}\glsadd{gov.mil.amphibious_task_force}\glsadd{gov.mil.task_organization}(JP 3-02)}
}
\newacronym{gov.mil.lf}{LF}{landing force}

\newglossaryentry{gov.mil.landing_force_operational_reserve_material}{
name={landing force operational reserve material},
description={Package of contingency supplies pre- positioned and maintained onboard selected amphibious warfare ships to enhance reaction time and provide support for the embarked landing force in contingencies. Also called LFORM. (JP 3-02)}
}
\newacronym{gov.mil.lform}{LFORM}{landing force operational reserve material}






\newglossaryentry{gov.mil.landing_group}{
name={landing group},
description={In amphibious operations, a subordinate task organization of the landing force capable of conducting landing operations, under a single tactical command, against a position or group of positions. (JP 3-02)}
}

\newglossaryentry{gov.mil.landing_plan}{
name={landing plan},
description={In amphibious operations, a collective term referring to all individually prepared amphibious task force and landing force documents that, taken together, present, in detail, all instructions for execution of the ship-to-shore movement. (JP 3-02)}
}

\newglossaryentry{gov.mil.landing_sequence_table}{
name={landing sequence table},
description={A document that incorporates the detailed plans for ship-to-shore movement of nonscheduled units. (JP 3-02)}
}

\newglossaryentry{gov.mil.landing_site}{
name={landing site},
description={1. A site within a landing zone containing one or more landing points. See also airfield. 2. In amphibious operations, a continuous segment of coastline over which troops, equipment, and supplies can be landed by surface means. (JP 3-02)}
}

\newglossaryentry{gov.mil.landing_zone}{
name={landing zone},
description={Any specified zone used for the landing of aircraft. Also called LZ. \glsseeformat[See also]{gov.mil.airfield}{}. \glsadd{gov.mil.airfield}(JP 3-17)}
}
\newacronym{gov.mil.lz}{LZ}{landing zone}

\newglossaryentry{gov.mil.laser_guided_weapon}{
name={laser-guided weapon},
description={A weapon that uses a seeker to detect laser energy reflected from a laser-marked/designated target and provides guidance commands to a control system that guides the weapon to the target. Also called LGW. (JP 3-09)}
}
\newacronym{gov.mil.lgw}{LGW}{laser-guided weapon}

\newglossaryentry{gov.mil.laser_rangefinder}{
name={laser rangefinder},
description={A device that uses laser energy for determining the distance from the device to a place or object. (JP 3-09)}
}

\newglossaryentry{gov.mil.laser_seeker}{
name={laser seeker},
description={A device based on a direction-sensitive receiver that detects the energy reflected from a laser-designated target and defines the direction of the target relative to the receiver. \glsseeformat[See also]{gov.mil.laser_guided_weapon}{}. \glsadd{gov.mil.laser_guided_weapon}(JP 3-09.3)}
}



\newglossaryentry{gov.mil.limiting_factor}{
name={limiting factor},
description={A factor or condition that, either temporarily or permanently, impedes mission accomplishment. (JP 5-0)}
}

\newglossaryentry{gov.mil.line_of_communications}{
name={line of communications},
description={A route, either land, water, and/or air, that connects an operating military force with a base of operations and along which supplies and military forces move. Also called LOC. (JP 2-01.3)}
}
\newacronym{gov.mil.loc}{LOC}{line of communications}

\newglossaryentry{gov.mil.line_of_demarcation}{
name={line of demarcation},
description={A line defining the boundary of a buffer zone used to establish the forward limits of disputing or belligerent forces after each phase of disengagement or withdrawal has been completed. \glsseeformat[See also]{gov.mil.buffer_zone,gov.mil.peace_operations}{}. \glsadd{gov.mil.buffer_zone}\glsadd{gov.mil.peace_operations}(JP 3-07.3)}
}






\newglossaryentry{gov.mil.low_level_transit_route}{
name={low-level transit route},
description={A temporary corridor of defined dimensions established in the forward area to minimize the risk to friendly aircraft from friendly air defenses or surface forces. Also called LLTR. (JP 3-52)}
}
\newacronym{gov.mil.lltr}{LLTR}{low-level transit route}

\newglossaryentry{gov.mil.low_velocity_drop}{
name={low velocity drop},
description={A drop procedure in which the drop velocity does not exceed 30 feet per second. (JP 3-17)}
}

\newglossaryentry{gov.mil.low_visibility_operations}{
name={low-visibility operations},
description={Sensitive operations wherein the diplomatic-military restrictions inherent in covert and clandestine operations are either not necessary or not feasible; actions are taken as required to limit exposure of those involved and/or their activities and with the knowledge that the action and/or sponsorship of the operation may preclude plausible denial by the initiating power. (JP 3-05)}
}





%:M


\newglossaryentry{gov.mil.maritime_pre_positioning_ships}{
name={maritime pre-positioning ships},
description={Civilian-crewed, Military Sealift Command-chartered ships that are usually forward-deployed and loaded with pre-positioned equipment and up to 30 days of supplies to support Marine expeditionary brigades. Also called MPSs. \glsseeformat[See also]{gov.mil.navy_cargo_handling_battalion}{}.\glsadd{gov.mil.navy_cargo_handling_battalion} (JP 3-02)}
}
\newacronym{gov.mil.mpss}{MPSs}{maritime pre-positioning ships}

\newglossaryentry{gov.mil.measurement_and_signature_intelligence}{
name={measurement and signature intelligence},
description={Information produced by quantitative and qualitative analysis of physical attributes of targets and events to characterize, locate, and identify targets and events, and derived from specialized, technically derived measurements of physical phenomenon intrinsic to an object or event. Also called MASINT. \glsseeformat[See also]{gov.mil.intelligence,gov.mil.scientific_and_technical_intelligence}{}.\glsadd{gov.mil.intelligence}\glsadd{gov.mil.scientific_and_technical_intelligence} (JP 2-0)}
}
\newacronym{gov.mil.masint}{MASINT}{measurement and signature intelligence}

\newglossaryentry{gov.mil.medical_intelligence}{
name={medical intelligence},
description={That category of intelligence resulting from collection, evaluation, analysis, and interpretation of foreign medical, bio-scientific, and environmental information that is of interest to strategic planning and to military medical planning and operations for the conservation of the fighting strength of friendly forces and the formation of assessments of foreign medical capabilities in both military and civilian sectors. Also called MEDINT. \glsseeformat[See also]{gov.mil.intelligence}{}.\glsadd{gov.mil.intelligence} (JP 2-01)}
}
\newacronym{gov.mil.medint}{MEDINT}{medical intelligence}




\newglossaryentry{gov.mil.midcourse_phase}{
name={midcourse phase},
description={That portion of the flight of a ballistic missile between the boost phase and the terminal phase. \glsseeformat[See also]{gov.mil.boost_phase,gov.mil.terminal_phase}{}. \glsadd{gov.mil.boost_phase}\glsadd{gov.mil.terminal_phase}(JP 3-01)}
}




\newglossaryentry{gov.mil.military_source_operations}{
name={military source operations},
description={The collection, from, by and/or via humans, of foreign and military and military-related intelligence. (JP 2-01.2)}
}

\newglossaryentry{gov.mil.military_standard_requisitioning_and_issue_procedure}{
name={military standard requisitioning and issue procedure},
description={A uniform procedure established by the Department of Defense for use within the Department of Defense to govern requisition and issue of materiel within standardized priorities. Also called MILSTRIP. (JP 4-01)}
}
\newacronym{gov.mil.milstrip}{MILSTRIP}{military standard requisitioning and issue procedure}

\newglossaryentry{gov.mil.military_standard_transportation_and_movement_procedures}{
name={military standard transportation and movement procedures},
description={Uniform and standard transportation data, documentation, and control procedures applicable to all cargo movements in the Department of Defense transportation system. Also called MILSTAMP. (JP 4-01.5)}
}
\newacronym{gov.mil.milstamp}{MILSTAMP}{military standard transportation and movement procedures}

\newglossaryentry{gov.mil.military_technician}{
name={military technician},
description={A Federal civilian employee providing full-time support to a National Guard, Reserve, or Active Component organization for administration, training, and maintenance of the Selected Reserve. Also called MILTECH. (CJCSM 3150.13)}
}
\newacronym{gov.mil.miltech}{MILTECH}{military technician}


\newglossaryentry{gov.mil.mine}{
name={mine},
description={1.In land mine warfare, a munition placed under, on or near the ground or other surface area and designed to be exploded by the presence, proximity or contact of a person or vehicle. 2. In naval mine warfare, an explosive device laid in the water with the intention of damaging or sinking ships or of deterring shipping from entering an area. \glsseeformat[See also]{gov.mil.mine_warfare}{}. \glsadd{gov.mil.mine_warfare}(JP 3-15)}
}

\newglossaryentry{gov.mil.mine_countermeasures}{
name={mine countermeasures},
description={All methods for preventing or reducing damage or danger from mines. Also called MCM. (JP 3-15)}
}
\newacronym{gov.mil.mcm}{MCM}{mine countermeasures}

\newglossaryentry{gov.mil.minefield}{
name={minefield},
description={1. In land warfare, an area of ground containing mines emplaced with or without a pattern. 2. In naval warfare, an area of water containing mines emplaced with or without a pattern. \glsseeformat[See also]{gov.mil.mine,gov.mil.mine_warfare}{}. \glsadd{gov.mil.mine}\glsadd{gov.mil.mine_warfare}(JP 3-15)}
}

\newglossaryentry{gov.mil.minefield_record}{
name={minefield record},
description={A complete written record of all pertinent information concerning a minefield, submitted on a standard form by the officer in charge of the emplacement operations. (JP 3-15)}
}

\newglossaryentry{gov.mil.minefield_report}{
name={minefield report},
description={An oral, electronic, or written communication concerning mining activities (friendly or enemy) submitted in a standard format by the fastest secure means available. (JP 3-15)}
}




\newglossaryentry{gov.mil.mine_warfare}{
name={mine warfare},
description={The strategic, operational, and tactical use of mines and mine countermeasures either by emplacing mines to degrade the enemy’s capabilities to wage land, air, and maritime warfare or by countering of enemy-emplaced mines to permit friendly maneuver or use of selected land or sea areas. Also called MIW. (JP 3-15)}
}
\newacronym{gov.mil.miw}{MIW}{mine warfare}




\newglossaryentry{gov.mil.mission}{
name={mission},
description={1. The task, together with the purpose, that clearly indicates the action to be taken and the reason therefore. (JP 3-0) 2. In common usage, especially when applied to lower military units, a duty assigned to an individual or unit; a task. (JP 3-0) 3. The dispatching of one or more aircraft to accomplish one particular task. (JP 3-30)}
}


\newglossaryentry{gov.mil.mission_oriented_protective_posture}{
name={mission-oriented protective posture},
description={A flexible system of protection against chemical, biological, radiological, and nuclear contamination in which personnel are required to wear only that protective clothing and equipment appropriate to the threat level, work rate imposed by the mission, temperature, and humidity. Also called MOPP. \glsseeformat[See also]{gov.mil.mission_oriented_protective_posture_gear}{}. \glsadd{gov.mil.mission_oriented_protective_posture_gear}(JP 3-11)}
}
\newacronym{gov.mil.mopp}{MOPP}{mission-oriented protective posture}

\newglossaryentry{gov.mil.mission_oriented_protective_posture_gear}{
name={mission-oriented protective posture gear},
description={Military term for individual protective equipment, including suit, boots, gloves, mask with hood, first aid treatments, and decontamination kits, issued to authorized personnel. Also called MOPP gear. \glsseeformat[See also]{gov.mil.decontamination,gov.mil.mission_oriented_protective_posture}{}. \glsadd{gov.mil.decontamination}\glsadd{gov.mil.mission_oriented_protective_posture}(JP 3-11)}
}
\newacronym{gov.mil.mopp_gear}{MOPP gear}{mission-oriented protective posture gear}

\newglossaryentry{gov.mil.multinational}{
name={multinational},
description={Between two or more forces or agencies of two or more nations or coalition
partners. \glsseeformat[See also]{gov.mil.alliance}{}. \glsadd{gov.mil.alliance}(JP 5-0)}
}




\newglossaryentry{gov.mil.multi_service_publication}{
name={multi-Service publication},
description={A publication containing principles, terms, tactics, techniques, and procedures used and approved by the forces of two or more Services to perform a common military function consistent with approved joint doctrine. (CJCSM 5120.01)}
}

\newglossaryentry{gov.mil.munition}{
name={munition},
description={A complete device charged with explosives; propellants; pyrotechnics; initiating composition; or chemical, biological, radiological, or nuclear material for use in operations including demolitions. (JP 3-42)}
}

\newglossaryentry{gov.mil.munitions_effectiveness_assessment}{
name={munitions effectiveness assessment},
description={The assessment of the military force applied in terms of the weapon system and munitions effectiveness to determine and recommend any required changes to the methodology, tactics, weapon system, munitions, fusing, and/or weapon delivery parameters to increase force effectiveness. Also called MEA. \glsseeformat[See also]{gov.mil.assessment,gov.mil.battle_damage_assessment}{}. \glsadd{gov.mil.assessment}\glsadd{gov.mil.battle_damage_assessment}(JP 2-01)}
}
\newacronym{gov.mil.mea}{MEA}{munitions effectiveness assessment}




%:N

\newglossaryentry{gov.mil.national_intelligence}{
name={national intelligence},
description={All intelligence that pertains to more than one agency and involves threats to the United States, its people, property, or interests; the development, proliferation, or use of weapons of mass destruction; or any other matter bearing on United States national or homeland security. (JP 2-01)}
}

\newglossaryentry{gov.mil.national_security}{
name={national security},
description={A collective term encompassing both national defense and foreign relations of the United States with the purpose of gaining: a. A military or defense advantage over any foreign nation or group of nations; b. A favorable foreign relations position; or c. A defense posture capable of successfully resisting hostile or destructive action from within or without, overt or covert. \glsseeformat[See also]{gov.mil.security}{}. \glsadd{gov.mil.security}(JP 1)}
}



\newglossaryentry{gov.mil.national_stock_number}{
name={national stock number (NSN)},
description={The 13-digit stock number replacing the 11-digit federal stock number. It consists of the 4-digit federal supply classification code and the 9-digit national item identification number. The national item identification number consists of a 2-digit National Codification Bureau number designating the central cataloging office (whether North Atlantic Treaty Organization or other friendly country) that assigned the number and a 7-digit (xxx-xxxx) nonsignificant number. The number shall be arranged as follows: 9999-00-999-9999. Also called NSN (JP 4-09)}
}
\newacronym{gov.mil.nsn}{NSN}{national stock number}


\newglossaryentry{gov.mil.naval_beach_group}{
name={naval beach group},
description={A permanently organized naval command within an amphibious force, composed of a commander and staff, a beachmaster unit, an amphibious construction battalion, and assault craft units, designed to provide an administrative group from which required naval tactical components may be made available to the amphibious task force commander and to the amphibious landing force commander. Also called NBG. \glsseeformat[See also]{gov.mil.shore_party}{}. \glsadd{gov.mil.shore_party}(JP 3-02)}
}
\newacronym{gov.mil.nbg}{NBG}{naval beach group}





\newglossaryentry{gov.mil.navy_cargo_handling_battalion}{
name={Navy cargo-handling battalion},
description={A mobile logistic support unit that is organized, trained, and equipped to: a. load and off-load Navy and Marine Corps cargo carried in maritime pre-positioning ships and merchant breakbulk or container ships in all environments, b. operate an associated temporary ocean cargo terminal, c. load and off-load Navy and Marine Corps cargo carried in military-controlled aircraft, and d. operate an associated expeditionary air cargo terminal. Also called NCHB. \glsseeformat[See also]{gov.mil.maritime_pre_positioning_ships}{}.\glsadd{gov.mil.maritime_pre_positioning_ships} (JP 3-02)}
}
\newacronym{gov.mil.nchb}{NCHB}{Navy cargo-handling battalion}




\newglossaryentry{gov.mil.navy_support_element}{
name={Navy support element},
description={The maritime pre-positioning force element that is tasked to conduct the off-load and ship-to-shore movement of maritime pre-positioned equipment and/or supplies. Also called NSE. (JP 3-02)}
}
\newacronym{gov.mil.nse}{NSE}{Navy support element}

\newglossaryentry{gov.mil.navy_tactical_air_control_center}{
name={Navy tactical air control center},
description={The principal air operations installation (ship-based) from which all aircraft and air warning functions of tactical air operations are controlled. Also called Navy TACC. (JP 3-09.3)}
}
\newacronym{gov.mil.navy_tacc}{Navy TACC}{Navy tactical air control center}

\newglossaryentry{gov.mil.navy_unique_fleet_essential_aircraft}{
name={Navy-unique fleet essential aircraft},
description={Combatant commander-controlled airlift assets deemed essential for providing air transportation in support of naval operations’ transportation requirements. Also called NUFEA. (JP 3-17)}
}
\newacronym{gov.mil.nufea}{NUFEA}{Navy-unique fleet essential aircraft}

\newglossaryentry{gov.mil.need_to_know}{
name={need to know},
description={A criterion used in security procedures that requires the custodians of classified information to establish, prior to disclosure, that the intended recipient must have access to the information to perform his or her official duties. (JP 2-01.2)}
}




%:O

\newglossaryentry{gov.mil.objective_area}{
name={objective area},
description={A geographical area, defined by competent authority, within which is located an objective to be captured or reached by the military forces. Also called OA. (JP 3-06)}
}
\newacronym{gov.mil.oa}{OA}{objective area}



\newglossaryentry{gov.mil.open_source_intelligence}{
name={open-source intelligence},
description={Relevant information derived from the systematic collection, processing, and analysis of publicly available information in response to known or anticipated intelligence requirements. Also called OSINT. \glsseeformat[See also]{gov.mil.intelligence}{}.\glsadd{gov.mil.intelligence} (JP 2-0)}
}
\newacronym{gov.mil.osint}{OSINT}{open-source intelligence}


\newglossaryentry{gov.mil.operation}{
name={operation},
description={1. A sequence of tactical actions with a common purpose or unifying theme. (JP 1) 2. A military action or the carrying out of a strategic, operational, tactical, service, training, or administrative military mission. (JP 3-0)}
}

\newglossaryentry{gov.mil.operational_control}{
name={operational control},
description={The authority to perform those functions of command over subordinate forces involving organizing and employing commands and forces, assigning tasks, designating objectives, and giving authoritative direction necessary to accomplish the mission. Also called OPCON. \glsseeformat[See also]{gov.mil.combatant_command,gov.mil.combatant_command_command_authority,gov.mil.tactical_control}{}. \glsadd{gov.mil.combatant_command}\glsadd{gov.mil.combatant_command_command_authority}\glsadd{gov.mil.tactical_control}(JP 1)}
}
\newacronym{gov.mil.opcon}{OPCON}{operational control}

\newglossaryentry{gov.mil.operational_intelligence}{
name={operational intelligence},
description={Intelligence that is required for planning and conducting campaigns and major operations to accomplish strategic objectives within theaters or operational areas. \glsseeformat[See also]{gov.mil.intelligence,gov.mil.strategic_intelligence,gov.mil.tactical_intelligence}{}.\glsadd{gov.mil.intelligence}\glsadd{gov.mil.strategic_intelligence}\glsadd{gov.mil.tactical_intelligence} (JP 2-0)}
}




%:P




\newglossaryentry{gov.mil.passive_defense}{
name={passive defense},
description={Measures taken to reduce the probability of and to minimize the effects of damage caused by hostile action without the intention of taking the initiative. \glsseeformat[See also]{gov.mil.active_defense}{}.\glsadd{gov.mil.active_defense} (JP 3-60)}
}


\newglossaryentry{gov.mil.peace_building}{
name={peace building},
description={Stability actions that strengthen and rebuild a society’s institutions, infrastructure, and civic life to avoid a relapse into conflict. Also called PB. \glsseeformat[See also]{gov.mil.peace_enforcement,gov.mil.peacekeeping,gov.mil.peacemaking,gov.mil.peace_operations}{}. \glsadd{gov.mil.peace_enforcement}\glsadd{gov.mil.peacekeeping}\glsadd{gov.mil.peacemaking}\glsadd{gov.mil.peace_operations}(JP 3-07.3)}
}
\newacronym{gov.mil.pb}{PB}{peace building}

\newglossaryentry{gov.mil.peace_enforcement}{
name={peace enforcement},
description={Application of military force, or the threat of its use, normally pursuant to international authorization, to compel compliance with resolutions or sanctions designed to maintain or restore peace and order. \glsseeformat[See also]{gov.mil.peace_building,gov.mil.peacekeeping,gov.mil.peacemaking,gov.mil.peace_operations}{}. \glsadd{gov.mil.peace_building}\glsadd{gov.mil.peacekeeping}\glsadd{gov.mil.peacemaking}\glsadd{gov.mil.peace_operations}(JP 3-07.3)}
}

\newglossaryentry{gov.mil.peacekeeping}{
name={peacekeeping},
description={Military operations undertaken, with the consent of all major parties to a dispute, designed to monitor and facilitate implementation of an agreement (cease fire, truce, or other such agreement) and support diplomatic efforts to reach a long-term political settlement. \glsseeformat[See also]{gov.mil.peace_building,gov.mil.peace_enforcement,gov.mil.peacemaking,gov.mil.peace_operations}{}. \glsadd{gov.mil.peace_building}\glsadd{gov.mil.peace_enforcement}\glsadd{gov.mil.peacemaking}\glsadd{gov.mil.peace_operations}(JP 3-07.3)}
}

\newglossaryentry{gov.mil.peacemaking}{
name={peacemaking},
description={The process of diplomacy, mediation, negotiation, or other forms of peaceful settlements that arranges an end to a dispute and resolves issues that led to it. Also called PM. \glsseeformat[See also]{gov.mil.peace_building,gov.mil.peace_enforcement,gov.mil.peacekeeping,gov.mil.peace_operations}{}. \glsadd{gov.mil.peace_building}\glsadd{gov.mil.peace_enforcement}\glsadd{gov.mil.peacekeeping}\glsadd{gov.mil.peace_operations}(JP 3-07.3)}
}
\newacronym{gov.mil.pm}{PM}{peacemaking}





\newglossaryentry{gov.mil.peace_operations}{
name={peace operations},
description={Multiagency and multinational crisis response and limited contingency operations involving all instruments of national power with military missions to contain conflict, redress the peace, and shape the environment to support reconciliation and rebuilding and facilitate the transition to legitimate governance. Also called PO. \glsseeformat[See also]{gov.mil.peace_building,gov.mil.peace_enforcement,gov.mil.peacekeeping,gov.mil.peacemaking}{}. \glsadd{gov.mil.peace_building}\glsadd{gov.mil.peace_enforcement}\glsadd{gov.mil.peacekeeping}\glsadd{gov.mil.peacemaking}(JP 3-07.3)}
}
\newacronym{gov.mil.po}{PO}{peace operations}




\newglossaryentry{gov.mil.personnel_recovery_coordination_cell}{
name={personnel recovery coordination cell},
description={The primary joint force component organization responsible for coordinating and controlling component personnel recovery missions. Also called PRCC. (JP 3-50)}
}
\newacronym{gov.mil.prcc}{PRCC}{personnel recovery coordination cell}

\newglossaryentry{gov.mil.personnel_recovery_reference_product}{
name={personnel recovery reference product},
description={A reference document for personnel recovery containing specific information on a particular country or region of interest. Also called PRRP. (JP 3-50)}
}
\newacronym{gov.mil.prrp}{PRRP}{personnel recovery reference product}

\newglossaryentry{gov.mil.personnel_services_support}{
name={personnel services support},
description={Service-provided sustainment activities that support a Service member during both exercises and operations. Also called PSS. (JP 1-0)}
}
\newacronym{gov.mil.pss}{PSS}{personnel services support}

\newglossaryentry{gov.mil.petroleum_oils_and_lubricants}{
name={petroleum, oils, and lubricants},
description={A broad term that includes all petroleum and associated products used by the Armed Forces. Also called POL. (JP 4-01.6)}
}
\newacronym{gov.mil.pol}{POL}{petroleum, oils, and lubricants}


\newglossaryentry{gov.mil.phase}{
name={phase},
description={In planning, a definitive stage of a campaign or operation during which a large portion of the forces and capabilities are involved in similar or mutually supporting activities for a common purpose. (JP 5-0)}
}

\newglossaryentry{gov.mil.phase_line}{
name={phase line},
description={An easily identified feature in the operational area utilized for control and coordination of military operations. Also called PL. (JP 3-09)}
}
\newacronym{gov.mil.pl}{PL}{phase line}


\newglossaryentry{gov.mil.planning_and_direction}{
name={planning and direction},
description={In intelligence usage, the determination of intelligence requirements, development of appropriate intelligence architecture, preparation of a collection plan, and issuance of orders and requests to information collection agencies. \glsseeformat[See also]{gov.mil.intelligence_process}{}.\glsadd{gov.mil.intelligence_process} (JP 2-01)}
}


\newglossaryentry{gov.mil.pointee_talkee}{
name={pointee-talkee},
description={A language aid containing selected phrases in English opposite a translation in a foreign language used by pointing to appropriate phrases. \glsseeformat[See also]{gov.mil.evasion_aid}{}. \glsadd{gov.mil.evasion_aid}(JP 3-50)}
}



\newglossaryentry{gov.mil.port_of_debarkation}{
name={port of debarkation},
description={The geographic point at which cargo or personnel are discharged. Also called POD. \glsseeformat[See also]{gov.mil.port_of_embarkation}{}.\glsadd{gov.mil.port_of_embarkation} (JP 4-0)}
}
\newacronym{gov.mil.pod}{POD}{port of debarkation}

\newglossaryentry{gov.mil.port_of_embarkation}{
name={port of embarkation},
description={The geographic point in a routing scheme from which cargo or personnel depart. Also called POE. \glsseeformat[See also]{gov.mil.port_of_embarkation}{}.\glsadd{gov.mil.port_of_debarkation} (JP 4-01.2)}
}
\newacronym{gov.mil.poe}{POE}{port of embarkation}





\newglossaryentry{gov.mil.procedural_identification}{
name={procedural identification},
description={An identification based on observation and analysis of target behaviors including location and trajectory, as well as compliance with airspace control measures. (JP 3-01)}
}

\newglossaryentry{gov.mil.procedure_word}{
name={procedure word},
description={A word or phrase limited to radio telephone procedure used to facilitate communication by conveying information in a condensed standard form. Also called proword. (JP 3-09.3)}
}
\newacronym{gov.mil.proword}{proword}{procedure word}

\newglossaryentry{gov.mil.processing}{
name={processing},
description={A system of operations designed to convert raw data into useful information. (JP 2-0)}
}

\newglossaryentry{gov.mil.processing_and_exploitation}{
name={processing and exploitation},
description={In intelligence usage, the conversion of collected information into forms suitable to the production of intelligence. \glsseeformat[See also]{gov.mil.intelligence_process}{}.\glsadd{gov.mil.intelligence_process} (JP 2-01)}
}



\newglossaryentry{gov.mil.process_owner}{
name={process owner},
description={The head of a Department of Defense component assigned a responsibility by the Secretary of Defense when process improvement involves more than one Service or Department of Defense component. (JP 4-0)}
}

\newglossaryentry{gov.mil.procurement_lead_time}{
name={procurement lead time},
description={The interval in time between the initiation of procurement action and receipt of the products or services purchased as the result of such actions. (JP 4-10)}
}

\newglossaryentry{gov.mil.procuring_contracting_officer}{
name={procuring contracting officer},
description={A contracting officer who initiates and signs the contract. Also called PCO. \glsseeformat[See also]{gov.mil.administrative_contracting_officer,gov.mil.contracting_officer}{}.\glsadd{gov.mil.administrative_contracting_officer}\glsadd{gov.mil.contracting_officer} (JP 4-10)}
}
\newacronym{gov.mil.pco}{PCO}{procuring contracting officer}

\newglossaryentry{gov.mil.protection}{
name={protection},
description={Preservation of the effectiveness and survivability of mission-related military and nonmilitary personnel, equipment, facilities, information, and infrastructure deployed or located within or outside the boundaries of a given operational area. \glsseeformat[See also]{gov.mil.mission_oriented_protective_posture}{}. \glsadd{gov.mil.mission_oriented_protective_posture}(JP 3-0}
}





%:R



\newglossaryentry{gov.mil.realistic_military_training}{
name={Realistic Military Training},
description={Department of Defense training conducted off federal property utilizing private or non-federal public property and infrastructure. (DODI 1322.28)}
}

\newglossaryentry{gov.mil.real_property}{
name={real property},
description={Lands, buildings, structures, utilities systems, improvements, and appurtenances, thereto that includes equipment attached to and made part of buildings and structures, but not movable equipment. (JP 3-34)}
}

\newglossaryentry{gov.mil.reattack_recommendation}{
name={reattack recommendation},
description={An assessment, derived from the results of battle damage assessment and munitions effectiveness assessment, providing the commander systematic advice on reattack of a target. Also called RR. \glsseeformat[See also]{gov.mil.assessment,gov.mil.battle_damage_assessment,gov.mil.munitions_effectiveness_assessment,gov.mil.target}{}. \glsadd{gov.mil.assessment}\glsadd{gov.mil.battle_damage_assessment}\glsadd{gov.mil.munitions_effectiveness_assessment}(JP 3-60)}
}
\newacronym{gov.mil.rr}{RR}{reattack recommendation}





\newglossaryentry{gov.mil.recovery}{
name={recovery},
description={1. In air (aviation) operations, that phase of a mission that involves the return of an aircraft to a land base or platform afloat. (JP 3-52) 2. The retrieval of a mine from the location where emplaced. (JP 3-15) 3. In personnel recovery, actions taken to physically gain custody of isolated personnel and return them to friendly control. (JP 3-50) 4. Actions taken to extricate damaged or disabled equipment for return to friendly control or repair at another location. \glsseeformat[See also]{gov.mil.evader,gov.mil.evasion}{}.\glsadd{gov.mil.evader}\glsadd{gov.mil.evasion} (JP 3-34)}
}

\newglossaryentry{gov.mil.recovery_operations}{
name={recovery operations},
description={ Operations conducted to search for, locate, identify, recover, and return isolated personnel, human remains, sensitive equipment, or items critical to national security. (JP 3-50)}
}


\newglossaryentry{gov.mil.rescue_combat_air_patrol}{
name={rescue combat air patrol},
description={An aircraft patrol provided over that portion of an objective area in which recovery operations are being conducted for the purpose of intercepting and destroying hostile aircraft. Also called RESCAP. \glsseeformat[See also]{gov.mil.combat_air_patrol}{}. \glsadd{gov.mil.combat_air_patrol}(JP 3-50)}
}
\newacronym{gov.mil.rescap}{RESCAP}{rescue combat air patrol}

\newglossaryentry{gov.mil.rescue_coordination_center}{
name={rescue coordination center},
description={A unit, recognized by International Civil Aviation Organization, International Maritime Organization, or other cognizant international body, responsible for promoting efficient organization of search and rescue services and coordinating the conduct of search and rescue operations within a search and rescue region. Also called RCC. (JP 3-50)}
}
\newacronym{gov.mil.rcc}{RCC}{rescue coordination center}

\newglossaryentry{gov.mil.reserve}{
name={reserve},
description={1. Portion of a body of troops that is kept to the rear or withheld from action at the beginning of an engagement to be available for a decisive movement. 2. Members of the uniformed Services who are not in active service but who are subject to call to active duty. 3. Portion of an appropriation or contract authorization held or set aside for future operations or contingencies and, in respect to which, administrative authorization to incur commitments or obligations has been withheld. (JP 4-05)}
}

\newglossaryentry{gov.mil.reserve_component}{
name={Reserve Component},
description={The Armed Forces of the United States Reserve Component consists of the Army National Guard of the United States, the Army Reserve, the Navy Reserve, the Marine Corps Reserve, the Air National Guard of the United States, the Air Force Reserve, and the Coast Guard Reserve. Also called RC. \glsseeformat[See also]{gov.mil.component,gov.mil.reserve}{}. (JP 4-05)}
}
\newacronym{gov.mil.rc}{RC}{Reserve Component}



%:S

\newglossaryentry{gov.mil.scientific_and_technical_intelligence}{
name={scientific and technical intelligence},
description={The product resulting from the collection, evaluation, analysis, and interpretation of foreign scientific and technical information that covers: a. foreign developments in basic and applied research and in applied engineering techniques; and b. scientific and technical characteristics, capabilities, and limitations of all foreign military systems, weapons, weapon systems, and materiel; the research and development related thereto; and the production methods employed for their manufacture. Also called S\&TI. \glsseeformat[See also]{gov.mil.intelligence,gov.mil.technical_intelligence}{}.\glsadd{gov.mil.intelligence}\glsadd{gov.mil.technical_intelligence} (JP 2-01)}
}
\newacronym{gov.mil.SandTI}{S\&TI}{scientific and technical intelligence}

\newglossaryentry{gov.mil.search}{
name={search},
description={A systematic reconnaissance of a defined area, so that all parts of the area have passed within visibility. (JP 3-50)}
}

\newglossaryentry{gov.mil.search_and_rescue}{
name={search and rescue},
description={The use of aircraft, surface craft, submarines, and specialized rescue teams and equipment to search for and rescue distressed persons on land or at sea in a permissive environment. Also called SAR. \glsseeformat[See also]{gov.mil.combat_search_and_rescue,gov.mil.isolated_personnel,gov.mil.joint_personnel_recovery_center,gov.mil.personnel_recovery_coordination_cell}{}. \glsadd{gov.mil.combat_search_and_rescue}\glsadd{gov.mil.isolated_personnel}\glsadd{gov.mil.joint_personnel_recovery_center}\glsadd{gov.mil.personnel_recovery_coordination_cell}(JP 3-50)}
}
\newacronym{gov.mil.sar}{SAR}{search and rescue}

\newglossaryentry{gov.mil.search_and_rescue_numerical_encryption_grid}{
name={search and rescue numerical encryption grid},
description={A predesignated ten-letter word without repeated letters used exclusively by recovery forces or isolated personnel to encrypt numerical data such as position, time, and/or headings in a covert manner. (JP 3-50)}
}

\newglossaryentry{gov.mil.search_and_rescue_point}{
name={search and rescue point},
description={A predesignated specific location, relative to which isolated personnel provide their position to recovery forces. Also called SARDOT. (JP 3-50)}
}
\newacronym{gov.mil.sardot}{SARDOT}{search and rescue point}

\newglossaryentry{gov.mil.search_and_rescue_region}{
name={search and rescue region},
description={An area of defined dimensions, recognized by the International Civil Aviation Organization, International Maritime Organization, or other cognizant international body, and associated with a rescue coordination center within which search and rescue services are provided. (JP 3-50)}
}

\newglossaryentry{gov.mil.sea_state}{
name={sea state},
description={A scale that categorizes the force of progressively higher seas by wave height. (JP 4-01.6)}
}

\newglossaryentry{gov.mil.secondary_loads}{
name={secondary loads},
description={Unit equipment, supplies, and major end items that are transported in the beds of organic vehicles. (JP 3-02)}
}



\newglossaryentry{gov.mil.security}{
name={security},
description={1. Measures taken by a military unit, activity, or installation to protect itself against all acts designed to, or which may, impair its effectiveness. (JP 3-10) 2. A condition that results from the establishment and maintenance of protective measures that ensure a state of inviolability from hostile acts or influences. (JP 3-10) 3. With respect to classified matter, the condition that prevents unauthorized persons from having access to official information that is safeguarded in the interests of national security. \glsseeformat[See also]{gov.mil.national_security}{}. \glsadd{gov.mil.national_security}(JP 2-0}
}




\newglossaryentry{gov.mil.sensitive_site}{
name={sensitive site},
description={A geographically limited area that contains, but is not limited to, adversary information systems, war crimes sites, critical government facilities, and areas suspected of containing high value targets. (JP 3-31)}
}

\newglossaryentry{gov.mil.sequel}{
name={sequel},
description={The subsequent operation or phase based on the possible outcomes of the current operation or phase. \glsseeformat[See also]{gov.mil.branch}{}. \glsadd{gov.mil.branch}(JP 5-0)}
}







\newglossaryentry{gov.mil.service_component_command}{
name={Service component command},
description={A command consisting of the Service component commander and all those Service forces, such as individuals, units, detachments, organizations, and installations under that command, including the support forces that have been assigned to a combatant command or further assigned to a subordinate unified command or joint task force. \glsseeformat[See also]{gov.mil.component,gov.mil.functional_component_command}{}.\glsadd{gov.mil.component}\glsadd{gov.mil.functional_component_command} (JP 1)}
}


\newglossaryentry{gov.mil.sexual_assault_forensic_examination_kit}{
name={sexual assault forensic examination kit},
description={The medical and forensic examination kit used to ensure controlled procedures and safekeeping of any bodily specimens in a sexual assault case. Also called SAFE kit. (JP 1-0)}
}
\newacronym{gov.mil.safe}{SAFE}{sexual assault forensic examination kit}


\newglossaryentry{gov.mil.sexual_assault_prevention_and_response_program}{
name={Sexual Assault Prevention and Response Program},
description={A Department of Defense program for the Military Departments and Department of Defense components that establishes sexual assault prevention and response policies to be implemented worldwide. Also called SAPR program. (JP 1-0)}
}
\newacronym{gov.mil.sapr}{SAPR}{Sexual Assault Prevention and Response Program}

\newglossaryentry{gov.mil.sexual_assault_response_coordinator}{
name={sexual assault response coordinator},
description={The single point of contact at an installation or within a geographic area who overseas sexual assault awareness, prevention, and response. Also called SARC. (JP 1-0)}
}
\newacronym{gov.mil.sarc}{SARC}{sexual assault response coordinator}

\newglossaryentry{gov.mil.shelter}{
name={shelter},
description={An International Organization for Standardization container outfitted with live- or work-in capability. (JP 4-09)}
}

\newglossaryentry{gov.mil.shielding}{
name={shielding},
description={1. Material of suitable thickness and physical characteristics used to protect personnel from radiation during the manufacture, handling, and transportation of fissionable and radioactive materials. 2. Obstructions that tend to protect personnel or materials from the effects of a nuclear explosion. (JP 3-11)}
}

\newglossaryentry{gov.mil.ship_to_shore_movement}{
name={ship-to-shore movement},
description={That portion of the action phase of an amphibious operation that includes the deployment of the landing force from ships to designated landing areas. (JP 3-02)}
}

\newglossaryentry{gov.mil.shoot_look_shoot}{
name={shoot-look-shoot},
description={A firing doctrine in which the result of the first intercept attempt is assessed prior to the launch of a subsequent interceptor. Also called SLS. (JP 3-01)}
}
\newacronym{gov.mil.sls}{SLS}{shoot-look-shoot}

\newglossaryentry{gov.mil.shore_fire_control_party}{
name={shore fire control party},
description={A specially trained unit that controls naval gunfire in support of troops ashore. Also called SFCP. (JP 3-09)}
}
\newacronym{gov.mil.sfcp}{SFCP}{shore fire control party}

\newglossaryentry{gov.mil.shore_party}{
name={shore party},
description={A task organization of the landing force, formed for the purpose of facilitating the landing and movement off the beaches of troops, equipment, and supplies; for the evacuation from the beaches of casualties and enemy prisoners of war; and for facilitating the beaching, retraction, and salvaging of landing ships and craft. Also called beach group. \glsseeformat[See also]{gov.mil.beachmaster_unit,gov.mil.beach_party,gov.mil.naval_beach_group}{}. \glsadd{gov.mil.beachmaster_unit}\glsadd{gov.mil.beach_party}\glsadd{gov.mil.naval_beach_group}(JP 3-02)}
}


\newglossaryentry{gov.mil.shortfall}{
name={shortfall},
description={The lack of forces, equipment, personnel, materiel, or capability, reflected as the difference between the resources identified as a plan requirement and those quantities identified as apportioned for planning that would adversely affect the command’s ability to accomplish its mission. (JP 5-0)}
}








\newglossaryentry{gov.mil.signals_intelligence}{
name={signals intelligence},
description={1. A category of intelligence comprising either individually or in combination all communications intelligence, electronic intelligence, and foreign instrumentation signals intelligence, however transmitted. 2. Intelligence derived from communications, electronic, and foreign instrumentation signals. Also called SIGINT. \glsseeformat[See also]{gov.mil.communications_intelligence,gov.mil.electronic_intelligence,gov.mil.foreign_instrumentation_signals_intelligence,gov.mil.intelligence}{}.\glsadd{gov.mil.communications_intelligence}\glsadd{gov.mil.electronic_intelligence}\glsadd{gov.mil.foreign_instrumentation_signals_intelligence}\glsadd{gov.mil.intelligence} (JP 2-0)}
}
\newacronym{gov.mil.sigint}{SIGINT}{signals intelligence}

%\newglossaryentry{gov.mil.space_defense}{
%name={space defense},
%description={}
%}


\newglossaryentry{gov.mil.specified_combatant_command}{
name={specified combatant command},
description={A command, normally composed of forces from a single Military Department, that has a broad, continuing mission, normally functional, and is established and so designated by the President through the Secretary of Defense with the advice and assistance of the Chairman of the Joint Chiefs of Staff. (JP 1)}
}



\newglossaryentry{gov.mil.source}{
name={source},
description={1. A person, thing, or activity from which information is obtained. 2. In clandestine activities, a person (agent), normally a foreign national, in the employ of an intelligence activity for intelligence purposes. 3. In interrogation activities, any person who furnishes information, either with or without the knowledge that the information is being used for intelligence purposes. \glsseeformat[See also]{gov.mil.agent,gov.mil.collection_agency}{}.\glsadd{gov.mil.agent}\glsadd{gov.mil.collection_agency} (JP 2-01)}
}


\newglossaryentry{gov.mil.strategic_intelligence}{
name={strategic intelligence},
description={Intelligence required for the formation of policy and military plans at national and international levels. \glsseeformat[See also]{gov.mil.intelligence,gov.mil.operational_intelligence,gov.mil.tactical_intelligence}{}.\glsadd{gov.mil.intelligence}\glsadd{gov.mil.operational_intelligence}\glsadd{gov.mil.tactical_intelligence} (JP 2-01.2)}
}






\newglossaryentry{gov.mil.submarine_operating_authority}{
name={submarine operating authority},
description={The naval commander exercising operational control of submarines. Also called SUBOPAUTH. (JP 3-32)}
}
\newacronym{gov.mil.subopauth}{SUBOPAUTH}{submarine operating authority}

\newglossaryentry{gov.mil.subordinate_campaign_plan}{
name={subordinate campaign plan},
description={A combatant command prepared plan that satisfies the requirements under a Department of Defense campaign plan, which, depending upon the circumstances, transitions to a supported or supporting plan in execution. (JP 5-0)}
}

\newglossaryentry{gov.mil.subordinate_command}{
name={subordinate command},
description={A command consisting of the commander and all those individuals, units, detachments, organizations, or installations that have been placed under the command by the authority establishing the subordinate command. (JP 1)}
}

\newglossaryentry{gov.mil.subordinate_unified_command}{
name={subordinate unified command},
description={A command established by commanders of unified commands, when so authorized by the Secretary of Defense through the Chairman of the Joint Chiefs of Staff, to conduct operations on a continuing basis in accordance with the criteria set forth for unified commands. \glsseeformat[See also]{gov.mil.functional_component_command,gov.mil.operational_control,gov.mil.subordinate_command,gov.mil.unified_command}{}. \glsadd{gov.mil.functional_component_command}\glsadd{gov.mil.operational_control}\glsadd{gov.mil.subordinate_command}\glsadd{gov.mil.unified_command}(JP 1)}
}

\newglossaryentry{gov.mil.subsidiary_landing}{
name={subsidiary landing},
description={In an amphibious operation, a landing usually made outside the designated landing area. (JP 3-02)}
}









%:T

\newglossaryentry{gov.mil.table_of_allowance}{
name={table of allowance},
description={An equipment allowance document that prescribes basic allowances of organizational equipment and provides the control to develop, revise, or change equipment authorization inventory data. Also called TOA. (JP 4-09)}
}
\newacronym{gov.mil.toa}{TOA}{table of allowance}

\newglossaryentry{gov.mil.taboo_frequencies}{
name={TABOO frequencies},
description={Any friendly frequency of such importance that it must never be deliberately jammed or interfered with by friendly forces including international distress, safety, and controller frequencies. \glsseeformat[See also]{gov.mil.electronic_warfare}{}. \glsadd{gov.mil.electronic_warfare}(JP 3-13.1)}
}

\newglossaryentry{gov.mil.tactical_air_control_party}{
name={tactical air control party},
description={A subordinate operational component of a tactical air control system designed to provide air liaison to land forces and for the control of aircraft. Also called TACP. (JP 3-09.3)}
}
\newacronym{gov.mil.tacp}{TACP}{tactical air control party}



\newglossaryentry{gov.mil.tactical_control}{
name={tactical control},
description={The authority over forces that is limited to the detailed direction and control of movements or maneuvers within the operational area necessary to accomplish missions or tasks assigned. Also called TACON. \glsseeformat[See also]{gov.mil.combatant_command,gov.mil.combatant_command_command_authority,gov.mil.operational_control}{}. \glsadd{gov.mil.combatant_command}\glsadd{gov.mil.combatant_command_command_authority}\glsadd{gov.mil.operational_control}(JP 1)}
}
\newacronym{gov.mil.tacon}{TACON}{tactical control}







\newglossaryentry{gov.mil.tactical_intelligence}{
name={tactical intelligence},
description={Intelligence required for the planning and conduct of tactical operations. \glsseeformat[See also]{gov.mil.intelligence}{}.\glsadd{gov.mil.intelligence} (JP 2-01.2)}
}

\newglossaryentry{gov.mil.target_intelligence}{
name={target intelligence},
description={Intelligence that portrays and locates the components of a target or target complex and indicates its vulnerability and relative importance. \glsseeformat[See also]{gov.mil.target}{}.\glsadd{gov.mil.target} (JP 3-60)}
}


\newglossaryentry{gov.mil.target}{
name={target},
description={An entity or object that performs a function for the threat considered for possible engagement or other action. \glsseeformat[See also]{gov.mil.objective_area}{}.\glsadd{gov.mil.objective_area} (JP 3-60)}
}






\newglossaryentry{gov.mil.task}{
name={task},
description={A clearly defined action or activity specifically assigned to an individual or organization that must be done as it is imposed by an appropriate authority. (JP 1)}
}

\newglossaryentry{gov.mil.task_element}{
name={task element},
description={A component of a naval task unit organized by the commander of a task unit or higher authority. (JP 3-32)}
}

\newglossaryentry{gov.mil.task_force}{
name={task force},
description={A component of a fleet organized by the commander of a task fleet or higher authority for the accomplishment of a specific task or tasks. Also called TF. (JP 3-32)}
}
\newacronym{gov.mil.tf}{TF}{task force}



\newglossaryentry{gov.mil.task_organization}{
name={task organization},
description={An organization that assigns to responsible commanders the means with which to accomplish their assigned tasks in any planned action. (JP 3-33)}
}

\newglossaryentry{gov.mil.technical_intelligence}{
name={technical intelligence},
description={Intelligence derived from the collection, processing, analysis, and exploitation of data and information pertaining to foreign equipment and materiel for the purposes of preventing technological surprise, assessing foreign scientific and technical capabilities, and developing countermeasures designed to neutralize an adversary’s technological advantages. Also called TECHINT. \glsseeformat[See also]{gov.mil.exploitation,gov.mil.intelligence}{}.\glsadd{gov.mil.exploitation}\glsadd{gov.mil.intelligence} (JP 2-0)}
}
\newacronym{gov.mil.techint}{TECHINT}{technical intelligence}




\newglossaryentry{gov.mil.terminal}{
name={terminal},
description={A facility designed to transfer cargo from one means of conveyance to another. \glsseeformat[See also]{gov.mil.facility}{}. \glsadd{gov.mil.facility}(JP 4-01.6)}
}



\newglossaryentry{gov.mil.terminal_phase}{
name={terminal phase},
description={That portion of the flight of a ballistic missile that begins when the warhead or payload reenters the atmosphere and ends when the warhead or payload detonates, releases its submunitions, or impacts. \glsseeformat[See also]{gov.mil.boost_phase,gov.mil.midcourse_phase}{}. \glsadd{gov.mil.boost_phase}\glsadd{gov.mil.midcourse_phase}(JP 3-01)}
}







\newglossaryentry{gov.mil.terrorism}{
name={terrorism},
description={The unlawful use of violence or threat of violence, often motivated by religious, political, or other ideological beliefs, to instill fear and coerce governments or societies in pursuit of goals that are usually political. \glsseeformat[See also]{gov.mil.antiterrorism,gov.mil.combating_terrorism,gov.mil.counterterrorism,gov.mil.force_protection_condition}{}. \glsadd{gov.mil.antiterrorism}\glsadd{gov.mil.combating_terrorism}\glsadd{gov.mil.counterterrorism}\glsadd{gov.mil.force_protection_condition}(JP 3-07.2)}
}


\newglossaryentry{gov.mil.transit_zone}{
name={transit zone},
description={In illicit trafficking, the path taken by smugglers between the source and the arrival zones, and does not include distribution. \glsseeformat[See also]{gov.mil.arrival_zone}{}. \glsadd{gov.mil.arrival_zone}(JP 3-07.4)}
}




%:U





\newglossaryentry{gov.mil.unified_action}{
name={unified action},
description={The synchronization, coordination, and/or integration of the activities of governmental and nongovernmental entities with military operations to achieve unity of effort. (JP 1)}
}

\newglossaryentry{gov.mil.unified_combatant_command}{
name={unified combatant command},
description={\glsseeformat[See]{gov.mil.unified_command}{}. \glsadd{gov.mil.unified_command}(JP 1)}
}

\newglossaryentry{gov.mil.unified_command}{
name={unified command},
description={A command with a broad continuing mission under a single commander and composed of significant assigned components of two or more Military Departments that is established and so designated by the President, through the Secretary of Defense with the advice and assistance of the Chairman of the Joint Chiefs of Staff. Also called unified combatant command. \glsseeformat[See also]{gov.mil.combatant_command,gov.mil.subordinate_unified_command}{}. \glsadd{gov.mil.combatant_command}\glsadd{gov.mil.subordinate_unified_command}(JP 1)}
}



%:V

\newglossaryentry{gov.mil.vesicant_agent}{
name={vesicant agent},
description={\glsseeformat[See]{gov.mil.blister_agent}{}. \glsadd{gov.mil.blister_agent}(JP 3-11)}
}

%:W

\newglossaryentry{gov.mil.weapon_engagement_zone}{
name={weapon engagement zone},
description={ In air and missile defense, airspace of defined dimensions within which the responsibility for engagement of air threats normally rests with a particular weapon system. Also called WEZ. (JP 3-01)}
}
\newacronym{gov.mil.wez}{WEZ}{weapon engagement zone}


%:X

%:Y

%:Z



