% !TEX encoding = UTF-8 Unicode

%Taken from Joint Publication 1-02, DoD Dictionary of Military and Associated Terms

%\newglossaryentry{gov.achievedAvailability}{name=achieved availability ($\text{A}_{\text{A}}$),
%text={achieved availability},
%description={Availability of a system with respect to operating time and both corrective and preventive maintenance. It ignores \glsname{gov.meanLogisticsDelayTime} and may be calculated as \glsname{gov.meanTimeBetweenMaintenance} divided by the sum of \acrshort{gov.mtbm} and \glsname{gov.meanMaintenanceTime}, that is, $\text{\acrshort{gov.aa}} = \text{\acrshort{gov.mtbm}}/(\text{\acrshort{gov.mtbm}} + \text{\acrshort{gov.mmt}})$. See \glsname{gov.meanTimeBetweenMaintenance}, \glsname{gov.meanLogisticsDelayTime}, and \glsname{gov.meanMaintenanceTime}.
%}}


% A

\newglossaryentry{gov.mil.acceptability}{name=acceptability,
description={The joint operation plan review criterion for assessing whether the contemplated course of action is proportional, worth the cost, consistent with the law of war; and is militarily and politically supportable. See also \glsname{gov.adequacy}; \glsname{gov.feasibility}. \protect \maybeCite{DODJP1-02-2010}
}}

\newglossaryentry{gov.mil.access}{name=access,
description={In counterintelligence and intelligence use, a. a way or means of approach to identify a target; or b. exploitable proximity to or ability to approach an individual, facility, or information that enables target to carry out the intended mission. \protect \maybeCite{DODJP1-02-2010}
}}

\newglossaryentry{gov.mil.accessToClassifiedInformation}{name=access to classified information,
description={The ability and opportunity to obtain knowledge of classified information by persons with the proper security clearance and a need to know of specified classified information. \protect \maybeCite{DODJP1-02-2010}
}}

\newglossaryentry{gov.mil.accompanyingSupplies}{name=accompanying supplies,
description={Unit supplies that deploy with forces. \protect \maybeCite{DODJP1-02-2010}
}}

\newglossaryentry{gov.mil.accountability}{name=accountability,
description={The obligation imposed by law or lawful order or regulation on an officer or other person for keeping accurate record of property, documents, or funds. See also \glsname{gov.responsibility}. \protect \maybeCite{DODJP1-02-2010}
}}

\newglossaryentry{gov.mil.acousticIntelligence}{name=acoustic intelligence (ACINT),
text={acoustic intelligence},
description={Intelligence derived from the collection and processing of acoustic phenomena. \protect \maybeCite{DODJP1-02-2010}
}}

\newglossaryentry{gov.mil.acquisitionAndCrossServicingAgreement}{name=acquisition and cross-servicing agreement (ACSA),
text={acquisition and cross-servicing agreement},
description={Agreements negotiated on a bilateral basis with US allies or coalition partners that allow US forces to exchange most common types of support, including food, fuel, transportation, ammunition, and equipment. Authority to negotiate these agreements is usually delegated to the combatant commander by the Secretary of Defense. Authority to execute these agreements lies with the Secretary of Defense, and may or may not be delegated. Governed by legal guidelines, these agreements are used for contingencies, peacekeeping operations, unforeseen emergencies, or exercises to correct logistic deficiencies that cannot be adequately corrected by national means. The support received or given is reimbursed under the conditions of the acquisition and cross-servicing agreement. See also \glsname{gov.crossServicing}; \glsname{gov.servicing}. \protect \maybeCite{DODJP1-02-2010}
}}

\newglossaryentry{gov.mil.actionableIntelligence}{name=actionable intelligence,
description={Intelligence information that is directly useful to customers for immediate exploitation without having to go through the full intelligence production process. \protect \maybeCite{DODJP1-02-2010}
}}

\newglossaryentry{gov.mil.actionPhase}{name=action phase,
description={In amphibious operations, the period of time between the arrival of the landing forces of the amphibious force in the operational area and the accomplishment of their mission. See also \glsname{gov.amphibiousForce}; \glsname{gov.amphibiousOperation}; \glsname{gov.landingForce}; \glsname:{gov.mission}. \protect \maybeCite{DODJP1-02-2010}
}}



%% C

\newglossaryentry{gov.mil.centerOfGravity}{name=center of gravity (COG),
text={center of gravity},
description={The source of power that provides moral or physical strength, freedom of action, or will to act. See also \glsname{gov.decisivePoint}. \protect \maybeCite{DODJP1-02-2010}
}}


%% D

\newglossaryentry{gov.mil.decisivePoint}{name=decisive point,
description={A geographic place, specific key event, critical factor, or function that, when acted upon, allows commanders to gain a marked advantage over an adversary or contribute materially to achieving success. See also \glsname{gov.centerOfGravity}. \protect \maybeCite{DODJP1-02-2010}
}}



%% I

\newglossaryentry{gov.mil.individualProtectiveEquipment}{name=individual protective equipment (IPE),
text={individual protective equipment},
description={In chemical, biological, radiological, or nuclear operations, the personal clothing and equipment required to protect an individual from chemical, biological, and radiological hazards and some nuclear hazards. \protect \maybeCite{DODJP1-02-2010}
}}



%% P

\newglossaryentry{gov.mil.personalProtectiveEquipment}{name=personal protective equipment (PPE),
text={personal protective equipment},
description={The equipment provided to shield or isolate a person from the chemical, physical, and thermal hazards that can be encountered at a hazardous materials incident. Personal protective equipment includes both personal protective clothing and respiratory protection. See also \glsname{gov.mil.individualProtectiveEquipment}. \protect \maybeCite{DODJP1-02-2010}
}}
